### 2017-06-21 latex/paper.tex
complete paper,and format the folder structure

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-21 16:00:23
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou}
 \altaffiliation[Also at ]{Physics Department, Fudan University.}%Lines break automatically or can be forced with \\
\author{Xin-Gao Gong}%
 \email{xggong@fudan.edu.cn}
\affiliation{%
 Authors' institution and/or address\\
 This line break forced with \textbackslash\textbackslash
}%
\begin{abstract}
By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as$ 1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
\begin{description}
\item[Keywords]
Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
\end{description}
\end{abstract}

\maketitle

\section{INTRODUCTION}

With the development of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials. The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size. For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li2014}. Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}. Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}. However, materials prepared in the practical application is often multilayer structure to a few nanometers. Previous studies have focused on the weak Van der Waals interaction (vdW), and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicon material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicon, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.

Silicon nano is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon. The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.

At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}. Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications. However, the study on the properties of multilayer silicon thermal transport is still very rare, To this end, based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.

\section{COMPUTATIONAL DETAILS}

In this paper, based on the large scale parallel and efficient LAMMPS molecular dynamics software package, we study the thermal conductivity of multilayer silicon structure by using the non-equilibrium temperature gradient method. Because of the abundant silicon structure model, the phase reconstruction has attracted much attention. In order to well simulate the structures of different phase by MD, the latest Mod potential is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition. Firstly, we use conjugate gradient method to optimize these structures. All structures are shown in FIG.1.

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/structures}
\caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicon. Within which (a) to (e) are top view and side view of bilayer structures. (f) to (g) are side view of trilayer structures and (h) is that of four-layers. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The blacks represent those that are inside the structure. The top view of the cells is shown in the last.}
\end{figure}

 For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc. ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag). TABLE.1 lists the structure name, the minimum repeat cell periodicity, the binding energies, the first principle binding energies and the structural properties of the multilayer silicon. The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants. It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA). However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants. For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

\begin{table*}
\caption{\label{tab:table1}
Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 Name
 &Minimal period
 &Symmetry
 &$E_c$ in Guo
 &$E_c$ in MD
 &Buckling Feature\\
\hline
2l1 & $1 \times 1$ & Cmme & 5.000 &4.145 &Smooth \\
2l2 & $\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\
2l2 &$\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\

\end{tabular}
\end{ruledtabular}
\end{table*}

From TABLE.1, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure. The simulation is doing by velocity Verlet integral algorithm with the timestep to be $1 fs$. The length of the system in the x direction is $10~100nm$, the transverse direction y is in periodic boundary condition with its simulated width to be 5 nm, and free boundary condition is applied in z direction. At the same time the outermost two ends of the x direction are fixed, close to witch a 3nm with Nose-Hoover bath is applied. The left and right ends of the temperature control at $310K$ and$ 290K$. The simulation is carried out by NVT for $0.4ns$, then control the temperature gradient for $10 ns$, and finally we statistics the data of the last $10ns$. By Fourier's law, the relationship between thermal conductivity and heat flux is

\begin{equation}
\kappa = \frac{ J_x}{ \nabla T \cdot S} \label{eq_nemd}
\end{equation}

where $\kappa$ stands for thermal conductivity, $J_x$ , $\nabla T=(T_L-T_R)/L_x$ is the average heat flux and temperature gradient along x direction respectively. $T_L$, $T_R$ and $L_x$ means the temperature of the two ends and the sample length between the heat baths. $S=W \cdot nd$ is the total cross area, where W,n,d is the size in the y direction, the layer number and the thickness of each layer. According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

\section{RESULTS AND DISCCUSION}

We firstly investigate the effect of surface reconstruction on thermal conductivity. 5 kinds of silicon structures of armchair and zigzag were selected to study. The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.2. the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh. In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic. In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials. And the edges of the two directions are similar in shape, leading to small difference of heat transport.

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/2l_length}
\caption{\label{fig:2l_length} (color online) The thermal conductivity dependence on length for five types of bilayer silicon. The scatters are the results of MD simulations while the lines are fitted with Eq.~\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

When the length of the silicon is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious. When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious. The empirical formula of the John A. Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials. Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicon
\begin{equation}
\kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}})
\end{equation}

where $\kappa_\infty$ is the fitted full scattering thermal conductance. $L_c$ is the transition length from the ballistic transportation to the scattering transportation. The value $ \chi=|\kappa_{z,\infty}-\kappa_{a,\infty} |/max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) \times 100 \%$ is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions.

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/pr_total}
\caption{\label{fig:pr_total} (color online) The participation ratio .}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/pr_direction}
\caption{\label{fig:pr_direction} (color online) The participation ratio .}
\end{figure}

The total scattering thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.2. It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure). In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%. The smallest is 2l2 and 2lh (20\%). The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

\begin{table*}
\caption{\label{tab:table2}
The thermal conductivity and anisotropic ratio of different multi-layer silicene.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}

 &$\kappa_{z,\infty}$
 &$\kappa_{a,\infty}$
 &$\chi$
 &
 &$\kappa_{z,\infty}$
 &$\kappa_{a,\infty}$
 &$\chi$\\
\hline
2l1 & 11.6 & 6.5 & 43.9\% & 2l2 & 1.5 & 1.2 & 20.0\%\\
2l3 & 5.0 & 9.7 & 48.5\% & 2lr3 & 8.2 & 3.5 & 57.3\%\\
2lh & 2.0 & 2.5 & 20.0\% & 3l1 & 11.5 & 2.9 & 74.8\%\\
3l2 & 10.2 & 5.2 & 49.0\% & 4l1 & 10.2 & 3.4 & 66.7\%\\
5l1 & 11.7 & 5.7 & 51.3\% & 6l1 & 10.3 & 7.8 & 24.3\%\\
8l1 & 13.2 & 14.9 & 11.4\% & 10l1 & 13.3 & 13.5 & 1.5\%\\
Si111 & 33.6 & 34.7 & 3.2\% & Silicene & 11.4 & 11.6 & 1.7\%\\

\end{tabular}
\end{ruledtabular}
\end{table*}

The influence of thickness change on the thermal transport properties was then investigated. Here we study mainly on multilayer silicon structure with 3-10 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction. In order to compare, we also calculated the thermal conductivity of Si on its (111) surface and the thermal conductivity of the monolayer. The magnitude of the anisotropy is also shown in TABLE.2. From the FIG.3(a), in the case of the medium thickness of the 3~6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair. And with the increase of the number of layers, the anisotropy decreases gradually. The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.1). Compared with the bulk silicon structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicon surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicon. In order to predict the relationship between the thermal conductivity and the thickness, we calculated the thermal conductivity of the 8-10 layers silicene with the $2 \times 1$ surface reconstruction. In order to compare, the thermal conductivity of the bulk Si (111) surface with no surface reconstruction (9 layers) and the thermal conductivity of the monolayer were calculated. As shown in TABLE.2, with the increase of thickness, the anisotropy decreases gradually. When the thickness is up to 10 layers, the anisotropy of the thermal transport of multilayer silicon can be neglected (only about 1.5\%), which is consistent with the results of bulk silicon and single silicon. On the other hand, as shown in FIG.3(b), at the same thickness, in the case of shorter length (10~50nm), the anisotropy is obvious. When the length is about 100nm, the anisotropy difference becomes very small, and the size effect of the thermal conductivity anisotropy is obvious. This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicon structures along different directions. However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/trans_x}
\includegraphics[width=0.48\textwidth]{images/trans_y}
\caption{\label{fig:transmission} (color online)The transmission function.}
\end{figure}

In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we use molecular dynamics to measure the phonon spectra of several typical structures. The $10 \times  10  \times  1$ multilayer structure is chosen. The selected high symmetry points are $K(0.5,0.5,0.0),\Gamma(0.0,0.0,0.0),X(0.5,0.0,0.0),  Y(0.0,0.5,0.0)$, Take points along $ K \rightarrow \Gamma \rightarrow X\rightarrow Y$ as shown in FIG.4.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction. According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport. There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction. FIG.4(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2. The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy. Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction. Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease. At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length. The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair. With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged. On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number. Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/gv}
\caption{\label{fig:gv} (color online)Group Velocity.}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/tau}
\caption{\label{fig:tau} (color online)Lifetime.}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/gruneisen}
\caption{\label{fig:gruneisen} (color online)Gruneisen parameters.}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/vl_length}
\caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/bands}
\caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points. (a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
\end{figure}

\section{CONCLUSIONS}

By means of non-equilibrium molecular dynamics simulation, we found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure), and can be as low as 1.2 W/mK (2l2 structure) and the anisotropy can be as high as 57.3\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicon has good thermoelectric properties. In the 3-6 layer multilayer silicon with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased. The thermal conductivity anisotropy of the multilayer silicon with 10 layers is very small, which is consistent with the bulk Si and monolayer silicene. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.

\quad \\
\section{ACKNOWLEGEMENTS}
This paper was partially supported by the National Natural Science Foundation of China, the Special Funds for Major State Basic Research, the Foundation for the Author of National Excellent Doctoral Dissertation of China, the Program for Professor of Special Appointment at Shanghai Institutions of Higher Learning, and the Research Program of Shanghai Municipality and the Ministry of Education.

\bibliography{ref}
\end{document}

### 2017-06-21 latex/run.py

@@ -1,0 +1,18 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-21 01:41:49
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 17:03:42
+import os
+if not os.path.exists("bin/"):
+    os.mkdir("bin")
+os.chdir("bin")
+if not os.path.exists("images/"):
+    os.mkdir("images")
+os.system("cp ../ref.bib .")
+os.system("cp ../../src/*.eps images/")
+os.system('latex ../paper.tex')
+os.system('bibtex paper')
+os.system('latex ../paper.tex')
+os.system('latex ../paper.tex')
+os.system("dvipdft paper")

### 2017-06-21 src/2l_length.py

@@ -1,0 +1,53 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-14 22:16:16
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 17:08:29
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+markers = ['s', '8', '^', 'D', '>']
+colors = "k,r,g,b,purple".split(',')
+vs = '2l1,2l2,2l3,2lr3,2lh'.split(',')
+
+
+def ff(p, x):
+    return p[0] * (1.0 - np.exp(-x / p[1]))
+    # return 1.0/(p[1]/x+1/p[0])-p[2]
+    # return p[0]*p[1]**x
+
+
+with fig('2l_length.eps'):
+    for s in ['z', 'a']:
+        for i, v in enumerate(vs):
+
+            file = "multi_si/tc/%s.txt" % (v + s)
+            m = markers[i]
+            c = colors[i]
+            if s == 'z':
+                opts = dict(
+                    markeredgecolor='w',
+                    marker=m,
+                    color=c,
+                    markersize=8 + 2,
+                    ls='.')
+                o1 = "-"
+            else:
+                opts = dict(
+                    markeredgecolor=c,
+                    marker=m,
+                    color='w',
+                    markersize=8,
+                    ls='.')
+                o1 = "--"
+            y = np.loadtxt(file, skiprows=2)[:, [1, 5]]
+            print y
+            label = v + s
+            pl.plot(y[:, 0], y[:, 1], label=label, **opts)
+            p = fit(y[:, 0], y[:, 1], [1, 1, 1], ff)
+            xx = np.linspace(10, 100, 1000)
+            pl.plot(xx, ff(p, xx), color=c, ls=o1)
+            pl.xlabel("Length(nm)")
+            pl.ylim([0, 14])
+            pl.ylabel("Thermal Conductivity(W/mK)")
+    setLegend(pl, ncol=2, fontsize=10)

### 2017-06-21 src/bands.py

@@ -1,0 +1,65 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-15 16:27:39
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 16:06:51
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+vs = np.array('2l1,2l2,3l1,4l1,6l1,10l1'.split(',')).reshape([2, 3])
+ch = 'abcdef'
+text_style = dict(
+    horizontalalignment='left',
+    verticalalignment='center',
+    fontsize=14,
+    fontdict={'family': 'serif'})
+import matplotlib
+matplotlib.rcParams['xtick.major.width'] = 0
+with fig('bands.eps'):
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 7))
+    for i in range(2):
+        for j in range(3):
+            label = ch[i * 3 + j] + ")"
+            v = vs[i, j]
+            file = "multisi_phonon/" + v
+            y = np.loadtxt(file, skiprows=2)
+            k = y[:, 3]
+            fq = y[:, 4:]
+            m = fq.shape[1]
+            # for mi in range(m):
+            G1 = 0.707107
+            X = 1.20711
+            Y = 1.91421
+            G2 = 2.41421
+            LX = X - G1
+            LY = G2 - Y
+            L = LX + LY
+            fil = (k > G1 - 0.02) * (k < X + 0.02)  # G->X
+            axes[i, j].plot(
+                X - k[fil][::-1], fq[fil][::-1], color='k', alpha=0.9)
+            fil = (k > Y - 0.02) * (k < G2 + 0.02)  # Y->G
+            axes[i, j].plot(
+                G2 - k[fil][::-1] + LX, fq[fil][::-1], color='k', alpha=0.9)
+            axes[i, j].text(
+                .05, .95, label, transform=axes[i, j].transAxes, **text_style)
+            axes[i, j].set_xticks([])
+            # axes[i,j].set_xlim([0,2.41421])
+            # axes[i,j].set_xlim([0,L])
+            axes[i, j].set_ylim([0, 19])
+            # t=(0+0.1,0.707107,1.20711,1.91421,2.41421-0.1);
+            # labels=("K",r"$\Gamma$","X","Y",r"$\Gamma$")
[…]

### 2017-06-21 src/drawband.py

@@ -1,56 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-15 16:27:39
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-16 14:10:26
-from aces.tools import *
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np
-
-vs=np.array('2l1,2l2,3l1,4l1,6l1,10l1'.split(',')).reshape([2,3])
-ch='abcdef'
-text_style = dict(horizontalalignment='left', verticalalignment='center',
-              fontsize=14, fontdict={'family': 'serif'})
-import matplotlib
-matplotlib.rcParams['xtick.major.width'] = 0
-with fig('bands.png'):
-	fi,axes=pl.subplots(2,3,sharex=True,sharey=True,figsize=(10,7))
-	for i in range(2):
-		for j in range(3):
-			label=ch[i*3+j]+")"
-			v=vs[i,j]
-			file="multisi_phonon/"+v
-			y=np.loadtxt(file,skiprows=2)
-			k=y[:,3]
-			fq=y[:,4:]
-			m=fq.shape[1]
-			#for mi in range(m):	
-			G1=0.707107
-			X=1.20711
-			Y=1.91421
-			G2=2.41421
-			LX=X-G1
-			LY=G2-Y
-			L=LX+LY
-			fil=(k>G1-0.02)*(k<X+0.02) # G->X
-			axes[i,j].plot(X-k[fil][::-1],fq[fil][::-1],color='k',alpha=0.9)
-			fil=(k>Y-0.02)*(k<G2+0.02) # Y->G
-			axes[i,j].plot(G2-k[fil][::-1]+LX,fq[fil][::-1],color='k',alpha=0.9)
-			axes[i,j].text(.05,.95,label,transform=axes[i,j].transAxes,**text_style)
-			axes[i,j].set_xticks([])
-			#axes[i,j].set_xlim([0,2.41421])
-			#axes[i,j].set_xlim([0,L])
-			axes[i,j].set_ylim([0,19])
-			#t=(0+0.1,0.707107,1.20711,1.91421,2.41421-0.1);
-			#labels=("K",r"$\Gamma$","X","Y",r"$\Gamma$")
-			t=(0+0.1,LX,L-0.1);
-			labels=("X",r"$\Gamma$","Y")
-			if j==0:
-				axes[i,j].set_ylabel("Frequency (THz)")
-			if i==0:
[…]

### 2017-06-21 src/drawpr.py

@@ -1,44 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   1970-01-01 08:00:00
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-15 20:44:44
-from aces.tools import *
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np
-
-vs='2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
-p=[]
-error=[]
-with fig('pr2s.png'):
-	for v in vs:
-		if v=="2lh":
-			v="2lhex"
-		if v=="2lr":
-			v="2lrt3"
-		file=v+"/0/secondorder/pr.txt"
-		y=np.loadtxt(file)
-		print y
-		u=y[:,1].mean()
-		p.append(u)
-		e=y[:,1].std()
-		error.append(e)
-	fig, ax = pl.subplots()
-	pos = []
-	b=0.0
-	for i in range(5):
-		b=b+0.5
-		pos.append(b)
-	b+=0.5
-	for i in range(2):
-		b=b+0.5
-		pos.append(b)
-	for i in range(5):
-		b=b+1
-		pos.append(b)
-	ax.bar(pos, p, yerr=error, align='center',
-        color='g', ecolor='black',width=0.3,error_kw=dict(elinewidth=2,ecolor='black'))
-	ax.set_xticks(pos)
-	ax.set_xticklabels(vs)
-	ax.set_xlabel('Structure')
-	ax.set_ylabel("Average Phonon Participation Ratio")

### 2017-06-21 src/drawprq.py

@@ -1,60 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-16 16:26:09
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-17 14:15:28
-from aces.tools import *
-from ase import io
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np
-text_style = dict(horizontalalignment='left', verticalalignment='center',
-              fontsize=12, fontdict={'family': 'serif'})
-vs='2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-import matplotlib
-matplotlib.rcParams['axes.linewidth'] = 0
-with fig('prq.png'):
-
-	fi,axes=pl.subplots(3,4,figsize=(10,7), subplot_kw=dict(projection='polar'))
-	print vs
-	for i,v in enumerate(vs):
-		ax=axes[i//4,i%4]
-		if v=="2lh":
-			v="2lhex"
-		if v=="2lr3":
-			v="2lrt3"
-		#shell_exec("cd %s/0/secondorder/; ae drawpr"%v)
-		file=v+"/0/secondorder/prq.txt"
-		y=np.loadtxt(file)
-		"""
-		poscar=v+"/0/POSCAR"
-		atoms=io.read(poscar)
-		rcell=atoms.get_reciprocal_cell()
-		yy=[]
-		for x in y:
-			xx=x[:3].dot(rcell)
-			yy.append(xx)
-		yy=np.array(yy)
-		"""
-		N=30
-		dth=2*np.pi/N
-		ths=np.arange(0,N)*dth
-		prs=[]
-		thi=np.arctan2(y[:,1],y[:,0])#*180/np.pi
-		thi[thi < 0] += 2*np.pi
-		for th in ths:
-			fil=(thi>th-.5*dth)*(thi<=th+.5*dth)
-			if fil.sum()>0:
-				xx=y[fil,4].mean()
-			else:
-				xx=None
-			prs.append(xx)
-		ax.plot(ths,prs,lw=2,color='r')
-		# for periodic
-		ax.plot(np.array(ths)[[-1,0]],np.array(prs)[[-1,0]],lw=2,color='r')
-		ax.set_rlim([0,1.2])
-		ax.set_rticks([])
-
-		ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
-		if i>0:
[…]

### 2017-06-21 src/grunei.py

@@ -1,41 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-16 18:34:55
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-16 19:38:54
-
-
-
-from aces.tools import *
-from ase import io
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np
-markers=['^','s',"8"]
-colors="k,r,b,g,purple".split(',')
-import matplotlib
-matplotlib.rcParams['ytick.minor.width'] = 1.5
-matplotlib.rcParams['ytick.minor.size'] = 3
-with fig('gru.png'):
-	fi,axes=pl.subplots(1,3,sharex=True,sharey=True,figsize=(10,7))
-	for j in range(3):
-		if j==0:
-			vs="2l1,2l2,2lhex".split(',')
-		if j==1:
-			vs="3l1,3l2,4l1".split(',')
-		if j==2:
-			vs="5l1,6l1,Silicene".split(',')
-		for i,v in enumerate(vs):
-			ax=axes[j]
-			file="%s/0/SHENG/T300K/gruneisen_freq.txt"%v
-			if v=="2l1":
-				file="2l1/0/sheng.1/T300K/gruneisen_freq.txt"
-			if not exists(file):
-				shell_exec("cd %s/0/SHENG/;ae postnew"%v)
-			y=np.genfromtxt(file,delimiter='\t',skip_header=1)
-			hist,bin_edges=np.histogram(y[:,1],bins=60,range=[-2,5],density=True)
-			ax.plot(bin_edges[1:],hist,color=colors[i],label=v,lw=2)
-			ax.set_xlim([-2,4.9])
-			setLegend(ax,fontsize=10)
-	fi.text(0.5, 0.04, 'Gruneisen Parameter', ha='center')
-	fi.text(0.05, 0.5, 'Probability', va='center', rotation='vertical')
-	fi.subplots_adjust(left = None, bottom = None, right  = None, top = None, wspace = 0, hspace = 0 )

### 2017-06-21 src/gruneisen.py

@@ -1,0 +1,47 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-16 18:34:55
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 16:21:02
+
+
+from aces.tools import *
+from ase import io
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+markers = ['^', 's', "8"]
+colors = "k,r,b,g,purple".split(',')
+import matplotlib
+matplotlib.rcParams['ytick.minor.width'] = 1.5
+matplotlib.rcParams['ytick.minor.size'] = 3
+with fig('gruneisen.eps'):
+    fi, axes = pl.subplots(1, 3, sharex=True, sharey=True, figsize=(10, 7))
+    for j in range(3):
+        if j == 0:
+            vs = "2l1,2l2,2lhex".split(',')
+        if j == 1:
+            vs = "3l1,3l2,4l1".split(',')
+        if j == 2:
+            vs = "5l1,6l1,Silicene".split(',')
+        for i, v in enumerate(vs):
+            ax = axes[j]
+            file = "%s/0/SHENG/T300K/gruneisen_freq.txt" % v
+            if v == "2l1":
+                file = "2l1/0/sheng.1/T300K/gruneisen_freq.txt"
+            if not exists(file):
+                shell_exec("cd %s/0/SHENG/;ae postnew" % v)
+            y = np.genfromtxt(file, delimiter='\t', skip_header=1)
+            hist, bin_edges = np.histogram(
+                y[:, 1], bins=60, range=[-2, 5], density=True)
+            ax.plot(bin_edges[1:], hist, color=colors[i], label=v, lw=2)
+            ax.set_xlim([-2, 4.9])
+            setLegend(ax, fontsize=10)
+    fi.text(0.5, 0.04, 'Gruneisen Parameter', ha='center')
+    fi.text(0.05, 0.5, 'Probability', va='center', rotation='vertical')
+    fi.subplots_adjust(
+        left=None,
+        bottom=None,
+        right=None,
+        top=None,
+        wspace=0,
+        hspace=0)

### 2017-06-21 src/gv.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-19 18:32:58
+# @Last Modified time: 2017-06-21 16:28:27
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -12,7 +12,7 @@ text_style = dict(
     fontsize=12,
     fontdict={'family': 'serif'})
 vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
-with fig('gv.png'):
+with fig('gv.eps'):
     fi, axes = pl.subplots(2, 6, sharex=True, sharey=True, figsize=(10, 7))
     for i, v in enumerate(vs):
         print v
@@ -43,7 +43,7 @@ with fig('gv.png'):
             fil = (freqs > i * df) * (freqs < (i + 1) * df)
             ff.append(i * df)
             if fil.sum() == 0:
-                gg.append(0)
+                gg.append(np.array([0, 0, 0]))
             else:
                 gg.append(gvs[fil].mean(axis=0))
         gg = np.array(gg)

### 2017-06-21 src/multi_si/draw2l.py

@@ -1,42 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-14 22:16:16
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-15 15:06:29
-from aces.tools import *
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np 
-files=ls("tc/*.txt")
-markers=['s','8','^','D','>']
-colors="k,r,g,b,purple".split(',')
-vs='2l1,2l2,2l3,2lr3,2lh'.split(',')
-def ff(p,x):
-	return p[0]*(1.0-np.exp(-x/p[1]))
-	#return 1.0/(p[1]/x+1/p[0])-p[2]
-	#return p[0]*p[1]**x
-
-
-with fig('2l.png'):
-	for s in ['z','a']:
-		for i,v in enumerate(vs):
-		
-			file="tc/%s.txt"%(v+s)
-			m=markers[i]
-			c=colors[i]
-			if s=='z':
-				opts=dict(markeredgecolor='w',marker=m,color=c,markersize=8+2,ls='.')
-				o1="-"
-			else:
-				opts=dict(markeredgecolor=c,marker=m,color='w',markersize=8,ls='.')
-				o1="--"
-			y=np.loadtxt(file,skiprows=2)[:,[1,5]]
-			print y
-			label=file.replace("tc/","").replace(".txt","")
-			pl.plot(y[:,0],y[:,1],label=label,**opts)
-			p=fit(y[:,0],y[:,1],[1,1,1],ff)
-			xx=np.linspace(10,100,1000)
-			pl.plot(xx,ff(p,xx),color=c,ls=o1)
-			pl.xlabel("Length(nm)")
-			pl.ylim([0,14])
-			pl.ylabel("Thermal Conductivity(W/mK)")
-	setLegend(pl,ncol=2,fontsize=10)

### 2017-06-21 src/multi_si/drawvl.py

@@ -1,75 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-14 22:16:16
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-15 15:05:11
-from aces.tools import *
-from aces.graph import fig,setLegend,pl,fit
-import numpy as np
-
-def ff(p,x):
-	return p[0]*(1.0-np.exp(-x/p[1]))
-	#return 1.0/(p[1]/x+1/p[0])-p[2]
-	#return p[0]*p[1]**x
-
-
-with fig('vla.png',figsize=(7,8)):
-	markers=['s','8','^','D','>']
-	colors="k,r,b,purple,g".split(',')
-	vs='3l1,3l2,4l1,5l1'.split(',')
-	text_style = dict(horizontalalignment='left', verticalalignment='center',
-                  fontsize=14, fontdict={'family': 'serif'})
-	fi,axes=pl.subplots(2,1,sharex=True,figsize=(7,8))
-	ax1=axes[0]
-	for s in ['z','a']:
-		for i,v in enumerate(vs):
-		
-			file="tc/%s.txt"%(v+s)
-			m=markers[i]
-			c=colors[i]
-			if s=='z':
-				opts=dict(markeredgecolor='w',marker=m,color=c,markersize=8+2,ls='.')
-				o1="-"
-			else:
-				opts=dict(markeredgecolor=c,marker=m,color='w',markersize=8,ls='.')
-				o1="--"
-			y=np.loadtxt(file,skiprows=2)[:,[1,5]]
-			print y
-			label=file.replace("tc/","").replace(".txt","")
-			ax1.plot(y[:,0],y[:,1],label=label,**opts)
-			p=fit(y[:,0],y[:,1],[1,1,1],ff)
-			xx=np.linspace(10,100,1000)
-			ax1.plot(xx,ff(p,xx),color=c,ls=o1)
-			ax1.set_ylabel("Thermal Conductivity(W/mK)")
-			#ax1.set_xticks([])
-			ax1.set_ylim([0,14])
-			ax1.text(-.15,1,'a)',transform=ax1.transAxes,**text_style)
-	setLegend(ax1,ncol=2,loc=0,fontsize=8)
-	ax1=axes[1]
-	vs='8l1,10l1,si111,6l1'.split(',')
-	for s in ['z','a']:
-		for i,v in enumerate(vs):
-		
[…]

### 2017-06-21 src/negf/drawtrans.py

@@ -1,38 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   1970-01-01 08:00:00
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-16 15:37:32
-from aces.tools import *
-from ase import io
-from aces.graph import fig,setLegend,pl,fit
-import matplotlib
-matplotlib.rcParams['xtick.major.width'] =1
-matplotlib.rcParams['ytick.major.width'] = 1
-import numpy as np
-text_style = dict(horizontalalignment='left', verticalalignment='center',
-              fontsize=12, fontdict={'family': 'serif'})
-vs='2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-with fig('trans.png'):
-	fi,axes=pl.subplots(6,2,sharex=True,sharey=True,figsize=(10,7))
-	for i,v in enumerate(vs):
-		ax=axes[i//2,i%2]
-		file=v+"/transmission.txt"
-		f=np.loadtxt(file,skiprows=1)
-		freq=f[:,0]
-		trans=f[:,3]
-		atoms=io.read(v+"/center/SPOSCAR")
-		cross=np.linalg.norm(atoms.cell[1])*(atoms.positions[:,2].max()-atoms.positions[:,2].min())
-		ax.plot(freq,trans/cross,color="k")
-		ax.fill_between(freq,0,trans/cross,color='r',alpha=0.5)
-		ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
-		ax.set_yticks([0.1,0.5,0.9])
-		ax.set_yticklabels([0.1,0.5,0.9])
-		#ax.set_ylabel("Phonon Transmission")
-		#ax.set_xlabel("Frequency (THz)")
-		ax.set_xlim([0,22])
-		#setLegend(pl,fontsize=9)
-	#ax.set_xlabel("Frequency (THz)")
-	fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
-	fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
-	fi.subplots_adjust(left = None, bottom = None, right  = None, top = None, wspace = 0, hspace = 0 )

### 2017-06-21 src/negfa/drawtrans.py

@@ -1,38 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   1970-01-01 08:00:00
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-16 15:37:32
-from aces.tools import *
-from ase import io
-from aces.graph import fig,setLegend,pl,fit
-import matplotlib
-matplotlib.rcParams['xtick.major.width'] =1
-matplotlib.rcParams['ytick.major.width'] = 1
-import numpy as np
-text_style = dict(horizontalalignment='left', verticalalignment='center',
-              fontsize=12, fontdict={'family': 'serif'})
-vs='2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-with fig('trans.png'):
-	fi,axes=pl.subplots(6,2,sharex=True,sharey=True,figsize=(10,7))
-	for i,v in enumerate(vs):
-		ax=axes[i//2,i%2]
-		file=v+"/transmission.txt"
-		f=np.loadtxt(file,skiprows=1)
-		freq=f[:,0]
-		trans=f[:,3]
-		atoms=io.read(v+"/center/SPOSCAR")
-		cross=np.linalg.norm(atoms.cell[0])*(atoms.positions[:,2].max()-atoms.positions[:,2].min())
-		ax.plot(freq,trans/cross,color="k")
-		ax.fill_between(freq,0,trans/cross,color='r',alpha=0.5)
-		ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
-		ax.set_yticks([0.1,0.5,0.9])
-		ax.set_yticklabels([0.1,0.5,0.9])
-		#ax.set_ylabel("Phonon Transmission")
-		#ax.set_xlabel("Frequency (THz)")
-		ax.set_xlim([0,22])
-		#setLegend(pl,fontsize=9)
-	#ax.set_xlabel("Frequency (THz)")
-	fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
-	fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
-	fi.subplots_adjust(left = None, bottom = None, right  = None, top = None, wspace = 0, hspace = 0 )

### 2017-06-21 src/pr_direction.py

@@ -1,0 +1,70 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-16 16:26:09
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 17:02:00
+from aces.tools import *
+from ase import io
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+text_style = dict(horizontalalignment='left', verticalalignment='center',
+                  fontsize=12, fontdict={'family': 'serif'})
+vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+import matplotlib
+matplotlib.rcParams['axes.linewidth'] = 0
+with fig('pr_direction.png'):
+
+    fi, axes = pl.subplots(
+        3, 4, figsize=(
+            10, 7), subplot_kw=dict(
+            projection='polar'))
+    print vs
+    for i, v in enumerate(vs):
+        ax = axes[i // 4, i % 4]
+        if v == "2lh":
+            v = "2lhex"
+        if v == "2lr3":
+            v = "2lrt3"
+        #shell_exec("cd %s/0/secondorder/; ae drawpr"%v)
+        file = v + "/0/secondorder/prq.txt"
+        y = np.loadtxt(file)
+        """
+		poscar=v+"/0/POSCAR"
+		atoms=io.read(poscar)
+		rcell=atoms.get_reciprocal_cell()
+		yy=[]
+		for x in y:
+			xx=x[:3].dot(rcell)
+			yy.append(xx)
+		yy=np.array(yy)
+		"""
+        N = 30
+        dth = 2 * np.pi / N
+        ths = np.arange(0, N) * dth
+        prs = []
+        thi = np.arctan2(y[:, 1], y[:, 0])  # *180/np.pi
+        thi[thi < 0] += 2 * np.pi
+        for th in ths:
+            fil = (thi > th - .5 * dth) * (thi <= th + .5 * dth)
+            if fil.sum() > 0:
+                xx = y[fil, 4].mean()
+            else:
+                xx = None
+            prs.append(xx)
+        ax.plot(ths, prs, lw=2, color='r')
+        # for periodic
+        ax.plot(np.array(ths)[[-1, 0]], np.array(prs)
+                [[-1, 0]], lw=2, color='r')
+        ax.set_rlim([0, 1.2])
+        ax.set_rticks([])
+
[…]

### 2017-06-21 src/pr_total.py

@@ -1,0 +1,53 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   1970-01-01 08:00:00
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 16:30:08
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
+p = []
+error = []
+with fig('pr_total.eps'):
+    for v in vs:
+        if v == "2lh":
+            v = "2lhex"
+        if v == "2lr":
+            v = "2lrt3"
+        file = v + "/0/secondorder/pr.txt"
+        y = np.loadtxt(file)
+        print y
+        u = y[:, 1].mean()
+        p.append(u)
+        e = y[:, 1].std()
+        error.append(e)
+    fig, ax = pl.subplots()
+    pos = []
+    b = 0.0
+    for i in range(5):
+        b = b + 0.5
+        pos.append(b)
+    b += 0.5
+    for i in range(2):
+        b = b + 0.5
+        pos.append(b)
+    for i in range(5):
+        b = b + 1
+        pos.append(b)
+    ax.bar(
+        pos,
+        p,
+        yerr=error,
+        align='center',
+        color='g',
+        ecolor='black',
+        width=0.3,
+        error_kw=dict(
+            elinewidth=2,
+            ecolor='black'))
+    ax.set_xticks(pos)
+    ax.set_xticklabels(vs)
+    ax.set_xlabel('Structure')
+    ax.set_ylabel("Average Phonon Participation Ratio")

### 2017-06-21 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-19 17:05:44
+# @Last Modified time: 2017-06-21 16:22:13
 
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
@@ -12,7 +12,7 @@ colors = "k,r,b,g,purple".split(',')
 import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
-with fig('tao2l.png'):
+with fig('tau.eps'):
     fi, axes = pl.subplots(1, 3, sharex=True, sharey=True, figsize=(10, 7))
     for j in range(3):
         if j == 0:

### 2017-06-21 src/trans_x.py

@@ -1,0 +1,45 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   1970-01-01 08:00:00
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 16:33:25
+from aces.tools import *
+from ase import io
+from aces.graph import fig, setLegend, pl, fit
+import matplotlib
+matplotlib.rcParams['xtick.major.width'] = 1
+matplotlib.rcParams['ytick.major.width'] = 1
+import numpy as np
+text_style = dict(horizontalalignment='left', verticalalignment='center',
+                  fontsize=12, fontdict={'family': 'serif'})
+vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+with fig('trans_x.eps'):
+    fi, axes = pl.subplots(6, 2, sharex=True, sharey=True, figsize=(10, 7))
+    for i, v in enumerate(vs):
+        ax = axes[i // 2, i % 2]
+        file = "negf/" + v + "/transmission.txt"
+        f = np.loadtxt(file, skiprows=1)
+        freq = f[:, 0]
+        trans = f[:, 3]
+        atoms = io.read("negf/" + v + "/center/SPOSCAR")
+        cross = np.linalg.norm(
+            atoms.cell[1]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
+        ax.plot(freq, trans / cross, color="k")
+        ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
+        ax.text(.02, .8, "(" + v + ")", transform=ax.transAxes, **text_style)
+        ax.set_yticks([0.1, 0.5, 0.9])
+        ax.set_yticklabels([0.1, 0.5, 0.9])
+        #ax.set_ylabel("Phonon Transmission")
+        #ax.set_xlabel("Frequency (THz)")
+        ax.set_xlim([0, 22])
+        # setLegend(pl,fontsize=9)
+    #ax.set_xlabel("Frequency (THz)")
+    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
+    fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
+    fi.subplots_adjust(
+        left=None,
+        bottom=None,
+        right=None,
+        top=None,
+        wspace=0,
+        hspace=0)

### 2017-06-21 src/trans_y.py

@@ -1,0 +1,45 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   1970-01-01 08:00:00
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 16:33:11
+from aces.tools import *
+from ase import io
+from aces.graph import fig, setLegend, pl, fit
+import matplotlib
+matplotlib.rcParams['xtick.major.width'] = 1
+matplotlib.rcParams['ytick.major.width'] = 1
+import numpy as np
+text_style = dict(horizontalalignment='left', verticalalignment='center',
+                  fontsize=12, fontdict={'family': 'serif'})
+vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+with fig('trans_y.eps'):
+    fi, axes = pl.subplots(6, 2, sharex=True, sharey=True, figsize=(10, 7))
+    for i, v in enumerate(vs):
+        ax = axes[i // 2, i % 2]
+        file = "negfa/" + v + "/transmission.txt"
+        f = np.loadtxt(file, skiprows=1)
+        freq = f[:, 0]
+        trans = f[:, 3]
+        atoms = io.read("negfa/" + v + "/center/SPOSCAR")
+        cross = np.linalg.norm(
+            atoms.cell[0]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
+        ax.plot(freq, trans / cross, color="k")
+        ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
+        ax.text(.02, .8, "(" + v + ")", transform=ax.transAxes, **text_style)
+        ax.set_yticks([0.1, 0.5, 0.9])
+        ax.set_yticklabels([0.1, 0.5, 0.9])
+        #ax.set_ylabel("Phonon Transmission")
+        #ax.set_xlabel("Frequency (THz)")
+        ax.set_xlim([0, 22])
+        # setLegend(pl,fontsize=9)
+    #ax.set_xlabel("Frequency (THz)")
+    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
+    fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
+    fi.subplots_adjust(
+        left=None,
+        bottom=None,
+        right=None,
+        top=None,
+        wspace=0,
+        hspace=0)

### 2017-06-21 src/vl_length.py

@@ -1,0 +1,102 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-14 22:16:16
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-21 17:08:15
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+
+def ff(p, x):
+    return p[0] * (1.0 - np.exp(-x / p[1]))
+    # return 1.0/(p[1]/x+1/p[0])-p[2]
+    # return p[0]*p[1]**x
+
+
+with fig('vl_length.eps', figsize=(7, 8)):
+    markers = ['s', '8', '^', 'D', '>']
+    colors = "k,r,b,purple,g".split(',')
+    vs = '3l1,3l2,4l1,5l1'.split(',')
+    text_style = dict(horizontalalignment='left', verticalalignment='center',
+                      fontsize=14, fontdict={'family': 'serif'})
+    fi, axes = pl.subplots(2, 1, sharex=True, figsize=(7, 8))
+    ax1 = axes[0]
+    for s in ['z', 'a']:
+        for i, v in enumerate(vs):
+
+            file = "multi_si/tc/%s.txt" % (v + s)
+            m = markers[i]
+            c = colors[i]
+            if s == 'z':
+                opts = dict(
+                    markeredgecolor='w',
+                    marker=m,
+                    color=c,
+                    markersize=8 + 2,
+                    ls='.')
+                o1 = "-"
+            else:
+                opts = dict(
+                    markeredgecolor=c,
+                    marker=m,
+                    color='w',
+                    markersize=8,
+                    ls='.')
+                o1 = "--"
+            y = np.loadtxt(file, skiprows=2)[:, [1, 5]]
+            print y
+            label = v + s
+            ax1.plot(y[:, 0], y[:, 1], label=label, **opts)
+            p = fit(y[:, 0], y[:, 1], [1, 1, 1], ff)
+            xx = np.linspace(10, 100, 1000)
+            ax1.plot(xx, ff(p, xx), color=c, ls=o1)
+            ax1.set_ylabel("Thermal Conductivity(W/mK)")
+            # ax1.set_xticks([])
+            ax1.set_ylim([0, 14])
+            ax1.text(-.15, 1, 'a)', transform=ax1.transAxes, **text_style)
[…]

### 2017-06-21 src/trans_x.py
mv trans_x and trans_y to transmission

@@ -1,45 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   1970-01-01 08:00:00
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:33:25
-from aces.tools import *
-from ase import io
-from aces.graph import fig, setLegend, pl, fit
-import matplotlib
-matplotlib.rcParams['xtick.major.width'] = 1
-matplotlib.rcParams['ytick.major.width'] = 1
-import numpy as np
-text_style = dict(horizontalalignment='left', verticalalignment='center',
-                  fontsize=12, fontdict={'family': 'serif'})
-vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-with fig('trans_x.eps'):
-    fi, axes = pl.subplots(6, 2, sharex=True, sharey=True, figsize=(10, 7))
-    for i, v in enumerate(vs):
-        ax = axes[i // 2, i % 2]
-        file = "negf/" + v + "/transmission.txt"
-        f = np.loadtxt(file, skiprows=1)
-        freq = f[:, 0]
-        trans = f[:, 3]
-        atoms = io.read("negf/" + v + "/center/SPOSCAR")
-        cross = np.linalg.norm(
-            atoms.cell[1]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
-        ax.plot(freq, trans / cross, color="k")
-        ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
-        ax.text(.02, .8, "(" + v + ")", transform=ax.transAxes, **text_style)
-        ax.set_yticks([0.1, 0.5, 0.9])
-        ax.set_yticklabels([0.1, 0.5, 0.9])
-        #ax.set_ylabel("Phonon Transmission")
-        #ax.set_xlabel("Frequency (THz)")
-        ax.set_xlim([0, 22])
-        # setLegend(pl,fontsize=9)
-    #ax.set_xlabel("Frequency (THz)")
-    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
-    fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
-    fi.subplots_adjust(
-        left=None,
-        bottom=None,
-        right=None,
-        top=None,
-        wspace=0,
-        hspace=0)

### 2017-06-21 src/transmission.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   1970-01-01 08:00:00
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:33:11
+# @Last Modified time: 2017-06-21 22:19:29
 from aces.tools import *
 from ase import io
 from aces.graph import fig, setLegend, pl, fit
@@ -13,10 +13,21 @@ import numpy as np
 text_style = dict(horizontalalignment='left', verticalalignment='center',
                   fontsize=12, fontdict={'family': 'serif'})
 vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-with fig('trans_y.eps'):
-    fi, axes = pl.subplots(6, 2, sharex=True, sharey=True, figsize=(10, 7))
+with fig('transmission.eps'):
+    fi, axes = pl.subplots(6, 2, sharex=True, sharey=False, figsize=(10, 7))
     for i, v in enumerate(vs):
         ax = axes[i // 2, i % 2]
+        file = "negf/" + v + "/transmission.txt"
+        f = np.loadtxt(file, skiprows=1)
+        freq = f[:, 0]
+        trans = f[:, 3]
+        atoms = io.read("negf/" + v + "/center/SPOSCAR")
+        cross = np.linalg.norm(
+            atoms.cell[1]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
+
+        ax.plot(freq, trans / cross, color="k", label=v + "z")
+        # ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
+        ax.text(.02, .8, "(" + v + ")", transform=ax.transAxes, **text_style)
         file = "negfa/" + v + "/transmission.txt"
         f = np.loadtxt(file, skiprows=1)
         freq = f[:, 0]
@@ -24,15 +35,15 @@ with fig('trans_y.eps'):
         atoms = io.read("negfa/" + v + "/center/SPOSCAR")
         cross = np.linalg.norm(
             atoms.cell[0]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
-        ax.plot(freq, trans / cross, color="k")
+
+        # ax.plot(freq, trans / cross, color="k", ls="--", label=v + "")
[…]

### 2017-06-21 latex/paper.tex
mv trans_x and trans_y to transmission
transmission fills to lines

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-21 16:00:23
+% @Last Modified time: 2017-06-21 22:36:35
 \documentclass[%
@@
 \begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/trans_x}
-\includegraphics[width=0.48\textwidth]{images/trans_y}
-\caption{\label{fig:transmission} (color online)The transmission function.}
+\includegraphics[width=0.48\textwidth]{images/transmission}
+\caption{\label{fig:transmission} (color online)The anisotropic transmission function of the structures.
+The structure identifiers are labeled at top-left of each subplot.
+the transmission along zigzag direction is ploted as black curve while that of armchair direction is filled.
+The y range of each subplot is normalized to the max value within the graph.}
 \end{figure}

### 2017-06-21 src/transmission.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   1970-01-01 08:00:00
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 22:19:29
+# @Last Modified time: 2017-06-21 22:33:29
 from aces.tools import *
 from ase import io
 from aces.graph import fig, setLegend, pl, fit
@@ -36,8 +36,8 @@ with fig('transmission.eps'):
         cross = np.linalg.norm(
             atoms.cell[0]) * (atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
 
-        # ax.plot(freq, trans / cross, color="k", ls="--", label=v + "")
-        ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
+        ax.plot(freq, trans / cross, color="r", label=v + "")
+        #ax.fill_between(freq, 0, trans / cross, color='r', alpha=0.5)
         ax.set_yticks([])
         ax.set_yticklabels([])
         # ax.set_ylabel("Phonon Transmission")

### 2017-06-22 latex/paper.tex
update author and ref

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-21 22:36:35
+% @Last Modified time: 2017-06-22 14:52:23
 \documentclass[%
@@
 \title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
-\author{Yang Zhou}
- \altaffiliation[Also at ]{Physics Department, Fudan University.}%Lines break automatically or can be forced with \\
-\author{Xin-Gao Gong}%
+\author{Yang Zhou${}^{1,2}$}
+\author{Zhi-Xin Guo${}^{3}$}
+\author{Shi-you Chen}
+\author{Hongjun Xiang}
+\author{Xin-Gao Gong${}^{1,2}$}
 \email{xggong@fudan.edu.cn}
-\affiliation{%
- Authors' institution and/or address\\
- This line break forced with \textbackslash\textbackslash
-}%
+\affiliation{
+${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
+${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
+${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
+}
 \begin{abstract}

### 2017-06-23 latex/paper.tex
fix some error in tex and remove docx file

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-22 14:52:23
+% @Last Modified time: 2017-06-23 13:06:47
 \documentclass[%
@@
 It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction.
-Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as$ 1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.
+Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.
 This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
@@
 
-In this paper, based on the large scale parallel and efficient LAMMPS molecular dynamics software package, we study the thermal conductivity of multilayer silicon structure by using the non-equilibrium temperature gradient method.
+In this paper, based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007}, we study the thermal conductivity of multilayer silicon structure by using the non-equilibrium temperature gradient method.
 Because of the abundant silicon structure model, the phase reconstruction has attracted much attention.
@@
 Firstly, we use conjugate gradient method to optimize these structures.
-All structures are shown in FIG.1.
+All structures are shown in FIG.\ref{fig:structures}.
 
@@
 ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
-TABLE.1 lists the structure name, the minimum repeat cell periodicity, the binding energies, the first principle binding energies and the structural properties of the multilayer silicon.
+TABLE.\ref{tab:table1} lists the structure name, the minimum repeat cell periodicity, the binding energies, the first principle binding energies and the structural properties of the multilayer silicon.
 The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
@@
 
-From TABLE.1, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure.
+From TABLE.\ref{tab:table1}, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure.
 The simulation is doing by velocity Verlet integral algorithm with the timestep to be $1 fs$.
-The length of the system in the x direction is $10~100nm$, the transverse direction y is in periodic boundary condition with its simulated width to be 5 nm, and free boundary condition is applied in z direction.
+The length of the system in the x direction is $10 - 100nm$, the transverse direction y is in periodic boundary condition with its simulated width to be 5 nm, and free boundary condition is applied in z direction.
 At the same time the outermost two ends of the x direction are fixed, close to witch a 3nm with Nose-Hoover bath is applied.
-The left and right ends of the temperature control at $310K$ and$ 290K$.
+The left and right ends of the temperature control at $310K$ and $290K$.
 The simulation is carried out by NVT for $0.4ns$, then control the temperature gradient for $10 ns$, and finally we statistics the data of the last $10ns$.
@@
 5 kinds of silicon structures of armchair and zigzag were selected to study.
-The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.2.
+The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:2l_length}.
 the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh.
@@
 \caption{\label{fig:2l_length} (color online) The thermal conductivity dependence on length for five types of bilayer silicon.
-The scatters are the results of MD simulations while the lines are fitted with Eq.~\ref{eq_nemd}.
+The scatters are the results of MD simulations while the lines are fitted with Eq.\ref{eq_nemd}.
 The letter z/a in the legend mean the transport direction is zigzag/armchair.}
@@
 
-The total scattering thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.2.
+The total scattering thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}.
 It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure).
@@
 In order to compare, we also calculated the thermal conductivity of Si on its (111) surface and the thermal conductivity of the monolayer.
-The magnitude of the anisotropy is also shown in TABLE.2.
-From the FIG.3(a), in the case of the medium thickness of the 3~6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair.
+The magnitude of the anisotropy is also shown in TABLE.\ref{tab:table2}.
+From the FIG.\ref{fig:vl_length}(a), in the case of the medium thickness of the 3 - 6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair.
 And with the increase of the number of layers, the anisotropy decreases gradually.
-The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.1).
+The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}).
 Compared with the bulk silicon structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow.
@@
 In order to compare, the thermal conductivity of the bulk Si (111) surface with no surface reconstruction (9 layers) and the thermal conductivity of the monolayer were calculated.
-As shown in TABLE.2, with the increase of thickness, the anisotropy decreases gradually.
+As shown in TABLE.\ref{tab:table2}, with the increase of thickness, the anisotropy decreases gradually.
 When the thickness is up to 10 layers, the anisotropy of the thermal transport of multilayer silicon can be neglected (only about 1.5\%), which is consistent with the results of bulk silicon and single silicon.
-On the other hand, as shown in FIG.3(b), at the same thickness, in the case of shorter length (10~50nm), the anisotropy is obvious.
+On the other hand, as shown in FIG.\ref{fig:vl_length}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious.
 When the length is about 100nm, the anisotropy difference becomes very small, and the size effect of the thermal conductivity anisotropy is obvious.
@@
 The $10 \times  10  \times  1$ multilayer structure is chosen.
-The selected high symmetry points are $K(0.5,0.5,0.0),\Gamma(0.0,0.0,0.0),X(0.5,0.0,0.0),  Y(0.0,0.5,0.0)$, Take points along $ K \rightarrow \Gamma \rightarrow X\rightarrow Y$ as shown in FIG.4.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
+The selected high symmetry points are $K(0.5, 0.5, 0.0) , \Gamma(0.0, 0.0, 0.0), X(0.5, 0.0, 0.0),  Y(0.0, 0.5, 0.0)$, Take points along $ K \rightarrow \Gamma \rightarrow X\rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
 According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport.
 There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction.
-FIG.4(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2.
+FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2.
 The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy.

### 2017-06-23 latex/paper.tex
extract io.shengbte and draw tao~direction

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-23 13:06:47
+% @Last Modified time: 2017-06-23 15:56:59
 \documentclass[%
@@
 
+\begin{figure}[b]
+\includegraphics[width=0.48\textwidth]{images/bands}
+\caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points.
+(a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
+\end{figure}
 In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we use molecular dynamics to measure the phonon spectra of several typical structures.
@@
 
+The anisotropy of phonon velocity has little contribution for the anisotropy of the thermal conductivity.
+FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures.
+The group velocity  along the two directions of  2 layers silicene ( include silicene) are exactly the same except for that of 2lr3 structure whose low frequency group velocities are highly anisotropic.
+Group velocity for the others are all highly anisotropic and it's obvious that the group velocity of armchair direction are all large than that of zigzag.
+The relation between the group velocity of both direction are contrast with that of the thermal conductivity, which indicate that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects.
+
+The
+
 \begin{figure}[b]
@@
 \caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
-\end{figure}
-
-\begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/bands}
-\caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points.
-(a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
 \end{figure}

### 2017-06-23 src/pr_direction.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 16:26:09
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 17:02:00
+# @Last Modified time: 2017-06-23 15:08:36
 from aces.tools import *
 from ase import io
 from aces.graph import fig, setLegend, pl, fit
@@ -18,7 +18,7 @@ with fig('pr_direction.png'):
         3, 4, figsize=(
             10, 7), subplot_kw=dict(
             projection='polar'))
-    print vs
+    print(vs)
     for i, v in enumerate(vs):
         ax = axes[i // 4, i % 4]
         if v == "2lh":

### 2017-06-23 src/tau.py

@@ -2,18 +2,20 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:22:13
+# @Last Modified time: 2017-06-23 19:26:23
 
-import aces.tools as tl
+
 from aces.graph import fig, setLegend, pl
 import numpy as np
+from aces.algorithm.kpoints import filter_along_direction as fad
+from aces.io.shengbte import get_qpoints_full as gqf, get_tau, get_omega
 markers = ['^', 's', "8"]
 colors = "k,r,b,g,purple".split(',')
 import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('tau.eps'):
-    fi, axes = pl.subplots(1, 3, sharex=True, sharey=True, figsize=(10, 7))
+    fi, axes = pl.subplots(3, 3, sharex=True, sharey=True, figsize=(10, 10))
     for j in range(3):
         if j == 0:
             vs = "2l1,2l2,2lhex".split(',')
@@ -22,29 +24,52 @@ with fig('tau.eps'):
         if j == 2:
             vs = "5l1,6l1,Silicene".split(',')
         for i, v in enumerate(vs):
-            ax = axes[j]
-            file = "%s/0/SHENG/T300K/q_tao.txt" % v
-            if v == "2l1":
-                file = "2l1/0/sheng.1/T300K/q_tao.txt"
-            if not tl.exists(file):
-                tl.shell_exec("cd %s/0/SHENG/;ae post" % v)
-            y = np.genfromtxt(file, delimiter='\t', skip_header=1)
-            c = ['w', 'k'][colors[i] == 'k']
-            th = np.arctan2(y[:, 1], y[:, 0])
-            dth = 2.0 * np.pi / 30
-            fil = (th < dth) * (th > -dth)
-            ax.semilogy(
-                y[fil, 3],
-                y[fil, 4],
-                ls='.',
-                marker=markers[i],
-                markersize=6,
-                markeredgecolor=colors[i],
-                color=c,
-                label=v)
-            ax.set_xlim([0, 4.9])
-            ax.set_ylim([0, 1e4])
-            setLegend(ax, fontsize=10)
+            for s in ['z', 'a']:
+                ax = axes[j, i]
+                dir = "%s/0/SHENG" % v
[…]

### 2017-06-23 src/gruneisen.py
direction effects of gruneisen and tau

@@ -2,20 +2,23 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:21:02
+# @Last Modified time: 2017-06-23 21:21:33
 
 
-from aces.tools import *
-from ase import io
-from aces.graph import fig, setLegend, pl, fit
+from aces.tools import exists, shell_exec
+
+from aces.graph import fig, setLegend, pl
 import numpy as np
+from aces.algorithm.kpoints import filter_along_direction as fad
+from aces.io.shengbte import get_qpoints_full as gqf, get_gruneisen, get_omega
+from aces.f import binmeanx
 markers = ['^', 's', "8"]
 colors = "k,r,b,g,purple".split(',')
 import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('gruneisen.eps'):
-    fi, axes = pl.subplots(1, 3, sharex=True, sharey=True, figsize=(10, 7))
+    fi, axes = pl.subplots(3, 3, sharex=True, sharey=True, figsize=(10, 10))
     for j in range(3):
         if j == 0:
             vs = "2l1,2l2,2lhex".split(',')
@@ -24,20 +27,42 @@ with fig('gruneisen.eps'):
         if j == 2:
             vs = "5l1,6l1,Silicene".split(',')
         for i, v in enumerate(vs):
-            ax = axes[j]
-            file = "%s/0/SHENG/T300K/gruneisen_freq.txt" % v
-            if v == "2l1":
-                file = "2l1/0/sheng.1/T300K/gruneisen_freq.txt"
-            if not exists(file):
-                shell_exec("cd %s/0/SHENG/;ae postnew" % v)
-            y = np.genfromtxt(file, delimiter='\t', skip_header=1)
-            hist, bin_edges = np.histogram(
-                y[:, 1], bins=60, range=[-2, 5], density=True)
-            ax.plot(bin_edges[1:], hist, color=colors[i], label=v, lw=2)
-            ax.set_xlim([-2, 4.9])
-            setLegend(ax, fontsize=10)
-    fi.text(0.5, 0.04, 'Gruneisen Parameter', ha='center')
-    fi.text(0.05, 0.5, 'Probability', va='center', rotation='vertical')
+            for s in ['z', 'a']:
+
[…]

### 2017-06-23 src/tau.py

@@ -2,13 +2,14 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 19:26:23
+# @Last Modified time: 2017-06-23 21:24:07
 
 
 from aces.graph import fig, setLegend, pl
 import numpy as np
 from aces.algorithm.kpoints import filter_along_direction as fad
 from aces.io.shengbte import get_qpoints_full as gqf, get_tau, get_omega
+from aces.f import binmeanx
 markers = ['^', 's', "8"]
 colors = "k,r,b,g,purple".split(',')
 import matplotlib
@@ -46,20 +47,12 @@ with fig('tau.eps'):
                     tau_full[fil].flatten()]
                 q = np.nan_to_num(q)
 
-                xx = []
-                dp = 0.4
-                for p in np.arange(0.0, 5.0, dp):
-                    f1 = (q[:, 0] <= (p + dp)) * (q[:, 0] > p)
-                    if f1.any():
-                        xx.append([p + dp * .5, q[f1, 1].mean()])
-                xx = np.array(xx)
+                x, y = binmeanx(q, [0.0, 5.0], dx=0.5)
                 mfc = [colors[i], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
-                if len(xx) == 0:
-                    break
                 ax.semilogy(
-                    xx[:, 0],
-                    xx[:, 1],
+                    x,
+                    y,
                     ls=ls,
                     marker=markers[i],
                     markersize=9,
@@ -70,7 +63,7 @@ with fig('tau.eps'):
                 ax.set_xlim([0, 4.55])
                 ax.set_ylim([1e-0, 1e3])
                 setLegend(ax, fontsize=10)
-    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
+    fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
     fi.text(
         0.05, 0.5, 'Relaxation Time (ps)', va='center', rotation='vertical')
     fi.subplots_adjust(

### 2017-06-23 src/transmission.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   1970-01-01 08:00:00
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 22:33:29
+# @Last Modified time: 2017-06-23 21:23:56
 from aces.tools import *
 from ase import io
 from aces.graph import fig, setLegend, pl, fit
@@ -45,7 +45,7 @@ with fig('transmission.eps'):
         ax.set_xlim([0, 22])
         # setLegend(ax, fontsize=9)
     #ax.set_xlabel("Frequency (THz)")
-    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
+    fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
     fi.text(0.07, 0.5, 'Phonon Transmission', va='center', rotation='vertical')
     fi.subplots_adjust(
         left=None,

### 2017-06-23 src/vl_length.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 17:08:15
+# @Last Modified time: 2017-06-23 20:15:34
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -57,7 +57,7 @@ with fig('vl_length.eps', figsize=(7, 8)):
             ax1.text(-.15, 1, 'a)', transform=ax1.transAxes, **text_style)
     setLegend(ax1, ncol=2, loc=0, fontsize=8)
     ax1 = axes[1]
-    vs = '8l1,10l1,si111,6l1'.split(',')
+    vs = '8l1,10l1,6l1,Silicene'.split(',')
     for s in ['z', 'a']:
         for i, v in enumerate(vs):
 
@@ -88,7 +88,7 @@ with fig('vl_length.eps', figsize=(7, 8)):
             xx = np.linspace(10, 100, 1000)
             ax1.plot(xx, ff(p, xx), color=c, ls=o1)
             ax1.set_xlabel("Length(nm)")
-            ax1.set_ylim([0, 37])
+            ax1.set_ylim([0, 18])
             ax1.set_ylabel("Thermal Conductivity(W/mK)")
             ax1.text(-.15, 1, 'b)', transform=ax1.transAxes, **text_style)
     setLegend(ax1, ncol=2, loc=0, fontsize=8)

### 2017-06-24 latex/paper.tex
重新画了一些图，并写了相关文字

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-23 15:56:59
+% @Last Modified time: 2017-06-24 17:55:39
 \documentclass[%
@@
 
-Silicon nano is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
+Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
 And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon.
@@
 
+\begin{figure}[b]
+\includegraphics[width=0.48\textwidth]{images/vl_length}
+\caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
+\end{figure}
+
 When the length of the silicon is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious.
@@
 
-\begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/pr_total}
-\caption{\label{fig:pr_total} (color online) The participation ratio .}
-\end{figure}
-
-\begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/pr_direction}
-\caption{\label{fig:pr_direction} (color online) The participation ratio .}
-\end{figure}
-
-The total scattering thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}.
+The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}.
 It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure).
@@
 \begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/transmission}
-\caption{\label{fig:transmission} (color online)The anisotropic transmission function of the structures.
-The structure identifiers are labeled at top-left of each subplot.
-the transmission along zigzag direction is ploted as black curve while that of armchair direction is filled.
-The y range of each subplot is normalized to the max value within the graph.}
-\end{figure}
-
-\begin{figure}[b]
 \includegraphics[width=0.48\textwidth]{images/bands}
@@
 \end{figure}
-In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we use molecular dynamics to measure the phonon spectra of several typical structures.
+
+In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures.
 The $10 \times  10  \times  1$ multilayer structure is chosen.
-The selected high symmetry points are $K(0.5, 0.5, 0.0) , \Gamma(0.0, 0.0, 0.0), X(0.5, 0.0, 0.0),  Y(0.0, 0.5, 0.0)$, Take points along $ K \rightarrow \Gamma \rightarrow X\rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
+The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
 According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport.
@@
 
-The
+\begin{figure}[b]
+\includegraphics[width=0.48\textwidth]{images/pr_direction}
+\caption{\label{fig:pr_direction} (color online) The participation ratio.}
+\end{figure}
+
+The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures.
+In previous work we have proven that  phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}.
+The participation ratio of all the structures as shown in FIG.\ref{fig:pr_direction}.PR of both Silicene and 2l1 structures are exactly the same , suggesting that every phonon has been participated by all the atoms ,which means there's no localization.
+The others all present localization but that of 2l2 is isotropic while  PR is larger for armchair of 2l3 than that of zigag which is consist with their thermal conductivity.
+
+\begin{figure}[b]
+\includegraphics[width=0.48\textwidth]{images/transmission}
+\caption{\label{fig:transmission} (color online)The anisotropic transmission function of the structures.
+The structure identifiers are labeled at top-left of each subplot.
+the transmission along zigzag direction is ploted as black curve while that of armchair direction is filled.
+The y range of each subplot is normalized to the max value within the graph.}
+\end{figure}
+
+The localization means number of transport channels is reduced by some atoms.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
+Similar to the situation of participation ratio, transmission of Silicene,2l1 are close.
+Especially that of 2l2 areexactly the same, which is due to the structure symmetry of it.
+The anistropy of the transmission are clearly seen in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair.
+The localization  contributes a lot to ther anisotropy becuase these trends are silimar to their thermal conductivity.
 
@@
 
+The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering.
+Considering three- phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.
+The result is also consist with the trends of thermal conductivity.
+
 \begin{figure}[b]
@@
 
-\begin{figure}[b]
-\includegraphics[width=0.48\textwidth]{images/vl_length}
-\caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
-\end{figure}
+The anisotroy of phonon lifetime is due to the anisotropy of anharmonic effect. The Gruneisen parameters which represent the degree of anharmonic effect is also shown in FIG.\ref{fig:gruneisen}.
+The larger the anharmonic effect the smaller the scattering lifetime of the phonons.
 

### 2017-06-24 src/pr_direction.py

@@ -2,65 +2,60 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 16:26:09
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 15:08:36
-from aces.tools import *
-from ase import io
-from aces.graph import fig, setLegend, pl, fit
+# @Last Modified time: 2017-06-23 21:59:58
+
+from aces.graph import fig, setLegend, pl
+from aces.algorithm.kpoints import filter_along_direction as fad
 import numpy as np
+from aces.f import binmeanx
 text_style = dict(horizontalalignment='left', verticalalignment='center',
                   fontsize=12, fontdict={'family': 'serif'})
 vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
-import matplotlib
-matplotlib.rcParams['axes.linewidth'] = 0
-with fig('pr_direction.png'):
+markers = ['^', 's', "8"]
+colors = "k,r,b,g,purple".split(',')
+with fig('pr_direction.eps'):
 
     fi, axes = pl.subplots(
-        3, 4, figsize=(
-            10, 7), subplot_kw=dict(
-            projection='polar'))
+        3, 4, sharex=True, sharey=True, figsize=(10, 10))
     print(vs)
-    for i, v in enumerate(vs):
-        ax = axes[i // 4, i % 4]
-        if v == "2lh":
-            v = "2lhex"
-        if v == "2lr3":
-            v = "2lrt3"
-        #shell_exec("cd %s/0/secondorder/; ae drawpr"%v)
-        file = v + "/0/secondorder/prq.txt"
-        y = np.loadtxt(file)
-        """
-		poscar=v+"/0/POSCAR"
-		atoms=io.read(poscar)
-		rcell=atoms.get_reciprocal_cell()
-		yy=[]
-		for x in y:
-			xx=x[:3].dot(rcell)
-			yy.append(xx)
-		yy=np.array(yy)
-		"""
-        N = 30
-        dth = 2 * np.pi / N
-        ths = np.arange(0, N) * dth
-        prs = []
-        thi = np.arctan2(y[:, 1], y[:, 0])  # *180/np.pi
-        thi[thi < 0] += 2 * np.pi
-        for th in ths:
-            fil = (thi > th - .5 * dth) * (thi <= th + .5 * dth)
-            if fil.sum() > 0:
-                xx = y[fil, 4].mean()
[…]

### 2017-06-24 src/pr_total.py

@@ -1,53 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   1970-01-01 08:00:00
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:30:08
-from aces.tools import *
-from aces.graph import fig, setLegend, pl, fit
-import numpy as np
-
-vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
-p = []
-error = []
-with fig('pr_total.eps'):
-    for v in vs:
-        if v == "2lh":
-            v = "2lhex"
-        if v == "2lr":
-            v = "2lrt3"
-        file = v + "/0/secondorder/pr.txt"
-        y = np.loadtxt(file)
-        print y
-        u = y[:, 1].mean()
-        p.append(u)
-        e = y[:, 1].std()
-        error.append(e)
-    fig, ax = pl.subplots()
-    pos = []
-    b = 0.0
-    for i in range(5):
-        b = b + 0.5
-        pos.append(b)
-    b += 0.5
-    for i in range(2):
-        b = b + 0.5
-        pos.append(b)
-    for i in range(5):
-        b = b + 1
-        pos.append(b)
-    ax.bar(
-        pos,
-        p,
-        yerr=error,
-        align='center',
-        color='g',
-        ecolor='black',
-        width=0.3,
-        error_kw=dict(
-            elinewidth=2,
-            ecolor='black'))
-    ax.set_xticks(pos)
-    ax.set_xticklabels(vs)
-    ax.set_xlabel('Structure')
-    ax.set_ylabel("Average Phonon Participation Ratio")

### 2017-06-25 pre/run.py
add pre. and use latexindent

@@ -1,0 +1,20 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-21 01:41:49
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-25 22:59:03
+import os
+if not os.path.exists("bin/"):
+    os.mkdir("bin")
+os.chdir("bin")
+if not os.path.exists("images/"):
+    os.mkdir("images")
+os.system("cp ../fudan_logo_vector.eps .")
+os.system("cp ../../latex/ref.bib .")
+os.system("cp ../../src/*.eps images/")
+os.system('xelatex ../presentation.tex')
+os.system('xelatex ../presentation.tex')
+#os.system('bibtex presentation')
+#os.system('latex ../presentation.tex')
+#os.system('latex ../presentation.tex')
+#os.system("dvipdft presentation")

### 2017-06-26 latex/paper.tex
add pre logo

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-24 17:55:39
+% @Last Modified time: 2017-06-26 15:07:24
 \documentclass[%
@@
 \preprint{APS/123-QED}
-\usepackage{graphicx}% Include figure files
+\usepackage{graphicx}% Include figure filesxx
 \usepackage{bm}% bold math
@@
 \author{Yang Zhou${}^{1,2}$}
+\author{Chao-Yu Chen${}^{3}$}
 \author{Zhi-Xin Guo${}^{3}$}
-\author{Shi-you Chen}
-\author{Hongjun Xiang}
+\email{zxguo08@hotmail.com}
+\author{Shi-You Chen}
+\author{Hong-Jun Xiang}
 \author{Xin-Gao Gong${}^{1,2}$}
@@
       Name
- &Minimal period
- &Symmetry
- &$E_c$ in Guo
- &$E_c$ in MD
- &Buckling Feature\\
+           & Minimal period
+           & Symmetry
+           & $E_c$ in Guo
+           & $E_c$ in MD
+           & Buckling Feature                                                                       \\
       \hline
-2l1 & $1 \times 1$ & Cmme & 5.000 &4.145 &Smooth \\
-2l2 & $\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
-2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
-2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
-2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
-3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
-3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
-4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\
-2l2 &$\sqrt{2}\times\sqrt{2}$ & C12/m1 & 4.991 & 4.204 & Large buckling and symmetric\\
-2l3 & $2 \times 2$ & C12/m1 & 5.063 & 4.257 & Large buckling and tilt symmetric\\
-2lh & $2 \times 2$ & P1 & 5.073 & 4.216 & Large buckling\\
-2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1 & - & 4.225 & Small buckling and symmetric\\
-3l1 & $2 \times 1$ & P121/m1 & 5.138 & 4.337 & -\\
-3l2 & $2 \times 1$ & P1 & 5.135 & 4.298 & -\\
-4l1 & $2 \times 1$ & P1 & 5.225 & 4.368 & -\\
-
+      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
+      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
+      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
+      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
+      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
+      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
+      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
+      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
+      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
+      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
+      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
+      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
+      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
+      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
+      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
     \end{tabular}
@@
 
- &$\kappa_{z,\infty}$
- &$\kappa_{a,\infty}$
- &$\chi$
+            & $\kappa_{z,\infty}$
+            & $\kappa_{a,\infty}$
+            & $\chi$
             &
- &$\kappa_{z,\infty}$
- &$\kappa_{a,\infty}$
- &$\chi$\\
+            & $\kappa_{z,\infty}$
+            & $\kappa_{a,\infty}$
+            & $\chi$                                                                \\
       \hline
-2l1 & 11.6 & 6.5 & 43.9\% & 2l2 & 1.5 & 1.2 & 20.0\%\\
-2l3 & 5.0 & 9.7 & 48.5\% & 2lr3 & 8.2 & 3.5 & 57.3\%\\
-2lh & 2.0 & 2.5 & 20.0\% & 3l1 & 11.5 & 2.9 & 74.8\%\\
-3l2 & 10.2 & 5.2 & 49.0\% & 4l1 & 10.2 & 3.4 & 66.7\%\\
-5l1 & 11.7 & 5.7 & 51.3\% & 6l1 & 10.3 & 7.8 & 24.3\%\\
-8l1 & 13.2 & 14.9 & 11.4\% & 10l1 & 13.3 & 13.5 & 1.5\%\\
-Si111 & 33.6 & 34.7 & 3.2\% & Silicene & 11.4 & 11.6 & 1.7\%\\
-
+      2l1   & 11.6                & 6.5  & 43.9\% & 2l2      & 1.5  & 1.2  & 20.0\% \\
+      2l3   & 5.0                 & 9.7  & 48.5\% & 2lr3     & 8.2  & 3.5  & 57.3\% \\
+      2lh   & 2.0                 & 2.5  & 20.0\% & 3l1      & 11.5 & 2.9  & 74.8\% \\
+      3l2   & 10.2                & 5.2  & 49.0\% & 4l1      & 10.2 & 3.4  & 66.7\% \\
+      5l1   & 11.7                & 5.7  & 51.3\% & 6l1      & 10.3 & 7.8  & 24.3\% \\
+      8l1   & 13.2                & 14.9 & 11.4\% & 10l1     & 13.3 & 13.5 & 1.5\%  \\
+      Si111 & 33.6                & 34.7 & 3.2\%  & Silicene & 11.4 & 11.6 & 1.7\%  \\
     \end{tabular}

### 2017-06-26 latex/run.py
reformat pre

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-21 01:41:49
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 17:03:42
+# @Last Modified time: 2017-06-26 18:34:07
 import os
 if not os.path.exists("bin/"):
     os.mkdir("bin")
@@ -10,9 +10,10 @@ os.chdir("bin")
 if not os.path.exists("images/"):
     os.mkdir("images")
 os.system("cp ../ref.bib .")
+os.system("cp ../*.tex .")
 os.system("cp ../../src/*.eps images/")
-os.system('latex ../paper.tex')
+os.system('latex paper.tex')
 os.system('bibtex paper')
-os.system('latex ../paper.tex')
-os.system('latex ../paper.tex')
+os.system('latex paper.tex')
+os.system('latex paper.tex')
 os.system("dvipdft paper")

### 2017-06-26 pre/run.py

@@ -1,20 +1,0 @@
-# -*- coding: utf-8 -*-
-# @Author: YangZhou
-# @Date:   2017-06-21 01:41:49
-# @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-25 22:59:03
-import os
-if not os.path.exists("bin/"):
-    os.mkdir("bin")
-os.chdir("bin")
-if not os.path.exists("images/"):
-    os.mkdir("images")
-os.system("cp ../fudan_logo_vector.eps .")
-os.system("cp ../../latex/ref.bib .")
-os.system("cp ../../src/*.eps images/")
-os.system('xelatex ../presentation.tex')
-os.system('xelatex ../presentation.tex')
-#os.system('bibtex presentation')
-#os.system('latex ../presentation.tex')
-#os.system('latex ../presentation.tex')
-#os.system("dvipdft presentation")

### 2017-06-26 latex/paper.tex
reformat pre
add group velocity

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-26 15:07:24
+% @Last Modified time: 2017-06-26 23:08:02
 \documentclass[%
@@
   \end{ruledtabular}
+
 \end{table*}
@@
     \begin{tabular}{cccccccc}
-
             & $\kappa_{z,\infty}$
@@
 
+The thermal conductivity tensor could be calculated with
+
+\begin{equation}
+  \kappa^{\alpha\beta} = \sum_{k \sigma}{c_{k \sigma}v^{\alpha}_{k \sigma}v^{\beta}_{k \sigma}\tau_{k \sigma}} \label{eq:kappasum}
+\end{equation}
+
+Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $tau_{k \sigma}$ is phonon lifetime.
+The anisotropy could derive from these factors and it's worth finding the most important ones.
+
+Heat capacity has no contribution to anisotropy. The average heat capacity is shown in Fig.\ref{fig:cv} and it's obviously that there's no difference in the value of the two directions.
+
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/gv}
+  \includegraphics[width=0.48\textwidth]{images/cv}
+  \caption{\label{fig:cv} (color online)Average Phonon heat capacity. The red bar present for the value of zigzag direction and yellow represent for that of armchiar direction. }
+\end{figure}
+
+\begin{figure}[b]
+  \includegraphics[width=0.48\textwidth]{images/gv}{}
   \caption{\label{fig:gv} (color online)Group Velocity.}
@@
 
+The anisotroy of group velocity derived from the localization of phonons along that directoin.
 The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures.
@@
 The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering.
-Considering three- phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+Considering three-phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
 The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.

### 2017-06-26 src/cv.py

@@ -1,0 +1,74 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-16 14:39:58
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-26 22:48:19
+import aces.tools as tl
+from aces.graph import fig, pl
+import numpy as np
+from aces.f import capacity
+from aces.algorithm.kpoints import filter_along_direction as fad
+from ase import io
+text_style = dict(
+    horizontalalignment='left',
+    verticalalignment='center',
+    fontsize=12,
+    fontdict={'family': 'serif'})
+vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
+with fig('cv.eps'):
+    fi, axes = pl.subplots(figsize=(10, 7))
+    N = len(vs)
+    ind = np.arange(N)  # the x locations for the groups
+    width = 0.35       # the width of the bars
+
+    cv1 = []
+    cv2 = []
+    for i, v in enumerate(vs):
+        print(v)
+        ax = axes
+        if v == "2lh":
+            v = "2lhex"
+        if v == "2lr":
+            v = "2lrt3"
+        file = v + "/0/secondorder/groupv/mesh.yaml"
+        data = tl.parseyaml(file)
+        freqs = []
+        qpoints = []
+        for phonon in data['phonon']:
+            qp = phonon['q-position']
+            for band in phonon['band']:
+                frequency = band['frequency']
+                gv = np.array(band['group_velocity'])
+                freqs.append(frequency)
+                qpoints.append(qp)
+        freqs = np.array(freqs)
+        qpoints = np.array(qpoints)
+        dth = np.pi / 10
+        phi = 0.0
+        fil = fad(qpoints, phi, dth)
+        atoms = io.read(v + "/0/secondorder/POSCAR")
+        V = np.linalg.norm(atoms.cell[0]) * np.linalg.norm(atoms.cell[1]) * (
+            atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
+        cv = capacity(freqs[fil], 300, V).mean()
+        print("cv1", cv)
+        cv1.append(cv)
+
+        phi = np.pi / 2.0
+        fil = fad(qpoints, phi, dth)
+        cv = capacity(freqs[fil], 300, V).mean()
[…]

### 2017-06-26 src/gruneisen.py

@@ -2,10 +2,8 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 21:21:33
+# @Last Modified time: 2017-06-26 21:53:59
 
-
-from aces.tools import exists, shell_exec
 
 from aces.graph import fig, setLegend, pl
 import numpy as np

### 2017-06-26 src/gv.py

@@ -2,10 +2,11 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-21 16:28:27
-from aces.tools import *
-from aces.graph import fig, setLegend, pl, fit
+# @Last Modified time: 2017-06-26 21:44:53
+import aces.tools as tl
+from aces.graph import fig, setLegend, pl
 import numpy as np
+from aces.f import binmeanx
 text_style = dict(
     horizontalalignment='left',
     verticalalignment='center',
@@ -15,14 +16,14 @@ vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
 with fig('gv.eps'):
     fi, axes = pl.subplots(2, 6, sharex=True, sharey=True, figsize=(10, 7))
     for i, v in enumerate(vs):
-        print v
+        print(v)
         ax = axes[i // 6, i % 6]
         if v == "2lh":
             v = "2lhex"
         if v == "2lr":
             v = "2lrt3"
         file = v + "/0/secondorder/groupv/mesh.yaml"
-        data = parseyaml(file)
+        data = tl.parseyaml(file)
         freqs = []
         gvs = []
         for phonon in data['phonon']:
@@ -35,20 +36,12 @@ with fig('gv.eps'):
         freqs = np.array(freqs)
         gvs = np.array(gvs)
         gvs = np.abs(gvs)
-        ff = []
-        gg = []
         N = 40
         df = 20.0 / N
-        for i in range(N):
-            fil = (freqs > i * df) * (freqs < (i + 1) * df)
-            ff.append(i * df)
-            if fil.sum() == 0:
-                gg.append(np.array([0, 0, 0]))
-            else:
-                gg.append(gvs[fil].mean(axis=0))
-        gg = np.array(gg)
-        ax.plot(ff, gg[:, 0], color="k", lw=3, label=v + "z")
-        ax.plot(ff, gg[:, 1], color="r", ls="--", lw=3, label=v + "a")
+        x, y = binmeanx(np.c_[freqs, gvs[:, 0]], [0, 20], df)
+        ax.plot(x, y, color="k", lw=3, label=v + "z")
+        x, y = binmeanx(np.c_[freqs, gvs[:, 1]], [0, 20], df)
[…]

### 2017-06-27 src/pr_atoms.py
pr atoms

@@ -1,0 +1,63 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-27 14:58:52
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-06-27 22:50:00
+
+import aces.tools as tl
+from aces.graph import fig, pl
+from aces.algorithm.kpoints import filter_along_direction as fad
+import numpy as np
+from ase import io
+from aces.io.phonopy.meshyaml import get_eigs, get_pr, meshyaml
+text_style = dict(horizontalalignment='left', verticalalignment='center',
+                  fontsize=12, fontdict={'family': 'serif'})
+vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+markers = ['^', 's', "8"]
+colors = "k,r,b,g,purple".split(',')
+
+
+def write_dump(poscar, color, file):
+    atoms = io.read(poscar)
+    cell = atoms.get_cell()
+    natom = len(atoms)
+    s = """ITEM: TIMESTEP
+0
+ITEM: NUMBER OF ATOMS
+%d
+ITEM: BOX BOUNDS pp pp pp
+0 %.6f
+0 %.6f
+0 %.6f
+""" % (natom, cell[0, 0], cell[1, 1], cell[2, 2])
+    s += "ITEM: ATOMS id xs ys zs color\n"
+    ss = atoms.get_scaled_positions()
+    for i in range(natom):
+        s += str(i + 1) + ' ' + tl.toString(ss[i]) + " " + str(color[i]) + "\n"
+    tl.write(s, file)
+
+for j in range(3):
+    vv = np.array(vs).reshape([3, 4])[j]
+    for i, v in enumerate(vv):
+        for s in ['z', 'a']:
+            if v == "2lh":
+                v = "2lhex"
+            if v == "2lr3":
+                v = "2lrt3"
+            file = v + "/0/secondorder/mesh.npz"
+            poscar = v + "/0/secondorder/POSCAR"
+
+            qpoints, freqs, eigs = get_eigs(file)
+            dth = np.pi / 10
+            if s == "z":
+                phi = 0.0
+            else:
+                phi = np.pi / 2.0
+            fil = fad(qpoints, phi, dth)
+
+            # shape=(natom). the average amplitude of each atom
+            c = np.linalg.norm(eigs, axis=-1)[fil]
+
[…]

### 2017-06-28 latex/paper.tex
2017-06-28

--- 2017-06-26 latex/paper.tex
@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-26 15:07:24
+% @Last Modified time: 2017-06-28 17:35:13
 \documentclass[%
@@
 The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size.
-For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li2014}.
+For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li,Yu2014}.
 Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}.
@@
   \caption{\label{tab:table2}
-    The thermal conductivity and anisotropic ratio of different multi-layer silicene.}
+    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
   \begin{ruledtabular}
-    \begin{tabular}{cccccccc}
-
+    \begin{tabular}{cccccccccccc}
             & $\kappa_{z,\infty}$
@@
             & $\chi$
+            & $Cv_{z}$
+            & $Cv_{a}$
             &
@@
             & $\kappa_{a,\infty}$
-            & $\chi$                                                                \\
+            & $\chi$
+            & $Cv_{z}$
+            & $Cv_{a}$                                                                                              \\
       \hline
-      2l1   & 11.6                & 6.5  & 43.9\% & 2l2      & 1.5  & 1.2  & 20.0\% \\
-      2l3   & 5.0                 & 9.7  & 48.5\% & 2lr3     & 8.2  & 3.5  & 57.3\% \\
-      2lh   & 2.0                 & 2.5  & 20.0\% & 3l1      & 11.5 & 2.9  & 74.8\% \\
-      3l2   & 10.2                & 5.2  & 49.0\% & 4l1      & 10.2 & 3.4  & 66.7\% \\
-      5l1   & 11.7                & 5.7  & 51.3\% & 6l1      & 10.3 & 7.8  & 24.3\% \\
-      8l1   & 13.2                & 14.9 & 11.4\% & 10l1     & 13.3 & 13.5 & 1.5\%  \\
-      Si111 & 33.6                & 34.7 & 3.2\%  & Silicene & 11.4 & 11.6 & 1.7\%  \\
+      2l1   & 11.6                & 6.5  & 43.9\% & 165.8 & 166.7 & 2l2      & 1.5  & 1.2  & 20.0\% & 38.44 & 38.44 \\
+      2l3   & 5.0                 & 9.7  & 48.5\% & 23.38 & 23.38 & 2lr3     & 8.2  & 3.5  & 57.3\% & 10.15 & 10.15 \\
+      2lh   & 2.0                 & 2.5  & 20.0\% & 22.42 & 22.42 & 3l1      & 11.5 & 2.9  & 74.8\% & 52.22 & 52.46 \\
+      3l2   & 10.2                & 5.2  & 49.0\% & 55.56 & 55.84 & 4l1      & 10.2 & 3.4  & 66.7\% & 37.71 & 37.89 \\
+      5l1   & 11.7                & 5.7  & 51.3\% & 29.17 & 29.32 & 6l1      & 10.3 & 7.8  & 24.3\% & 23.73 & 23.86 \\
+      8l1   & 13.2                & 14.9 & 11.4\% & 17.26 & 17.36 & 10l1     & 13.3 & 13.5 & 1.5\%  & -     & -     \\
+      Si111 & 33.6                & 34.7 & 3.2\%  & -     & -     & Silicene & 11.4 & 11.6 & 1.7\%  & 606.4 & 613.4 \\
     \end{tabular}
@@
 
+The thermal conductivity tensor could be calculated with
+
+\begin{equation}
+  \kappa^{\alpha\beta} = \sum_{k \sigma}{c_{k \sigma}v^{\alpha}_{k \sigma}v^{\beta}_{k \sigma}\tau_{k \sigma}} \label{eq:kappasum}
+\end{equation}
+
+Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime.
+The anisotropy could derive from these factors and it's worth finding the most important ones.
+
+Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ , calculate each of their heat capacity with
+
+\begin{equation}
+  c_{k \sigma}=\frac{\hbar \omega_{k \sigma} }{V} \frac{\partial f(\omega_{k \sigma},T)}{\partial T}
+\end{equation}
+
+Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
+The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$.
+The average heat capacity of the structures are shown in Table.\ref{tab:table2} .
+Large difference could be found between the $Cv$ of the structures.
+The lowest value is $10.15 kJ/m^3/K$ of 2lr while the highest value of Silicene could reach $606.4 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.
+There's no obvious trends when the layer increases but Silicene and 2l1 have pretty large value than the others and this has some relation to their low thickness.
+Almost no difference could be found in the value along zigzag direction and armchair direction, even if $\omega_{k \sigma}$ has large deviation between the direction as shown in Fig.\ref{fig:bands}.
+This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high.
+That means when considering only acoustic phonons the heat capacity is close to constant.
+
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/gv}
+  \includegraphics[width=0.48\textwidth]{images/gv}{}
   \caption{\label{fig:gv} (color online)Group Velocity.}
@@
 
-The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures.
+The different localization situation  along each direction determines the anisotroy of group velocity  along that direction.
+To qualitatively measure the physical mechanism of phonon localization we carried out a vibrational eigenmode analysis.
+Mode localization can be quantitatively characterized by the phonon participation ratio $P_{k\sigma}$  \cite{Allen1999}for each eigen-mode $k\sigma$ as
+
+\begin{equation}
+  P_{k\sigma}= \frac{1}{N \sum_{i}
+    {(\sum_\alpha{\epsilon^{i\alpha}_{k\sigma}
+        \epsilon^{*i\alpha}_{k\sigma}})^2}}
+\end{equation}
+
+where N is the atom number and $\epsilon^{i\alpha}_{k\sigma}$ is the eigenvector component of mode $k\sigma$ for the i-th atom and $\alpha$ direction.
+The value of participation ratio is between 0 and 1 which measures the fraction of atoms participating a given phonon mode.
+If the mode is localized then its trends with N is O(1/N) while delocalized modes with O(1).
+
+The anisotropy of phonon participation ratio has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures.
 In previous work we have proven that phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}.
-The participation ratio of all the structures as shown in FIG.\ref{fig:pr_direction}.PR of both Silicene and 2l1 structures are exactly the same , suggesting that every phonon has been participated by all the atoms ,which means there's no localization.
-The others all present localization but that of 2l2 is isotropic while  PR is larger for armchair of 2l3 than that of zigag which is consist with their thermal conductivity.
+Fig.\ref{fig:pr_direction} shows average phonon participation ratio for each eigenmode $k\sigma$ in various structures.
+The participation ratio of similar frequency has large difference and we select the phonons along zigzag direction and  average their participation ratio to obtain the solid black curve in Fig.\ref{fig:pr_direction} while the same is done to obtain the dash red curve for armchair direction.
+All the phonons of Silicene , 2l1 and some low frequency phonons of 2l2 exibit delocalized nature,suggesting that every phonon has been participated by all the atoms, which is due to the perfect bonding of them without dangling bonds.
+Different surface situation affects the localization a a lot.
+2l3 and 2lr3 exhibit large localization and anisotropy even for very low phonons, this is due to their unique surface where the buckling atoms form parallel lines, between them existing large distance,see Fig.\ref{fig:structures}.
+With the increasement of thickness, low frequency region remain delocalized while the participation ratio of intermediate frequency  decreases.
+For 6l1 the average participation ratio could drop down to around 0.4, and that of 8l1 even to 0.3.
+But the absolute number of atoms that participate in the mode $P_{k\sigma} \cdot N$ does not decrease and the number of transmission chanels in fact increase so thermal conductivity increase.
 
@@
 
-The localization means number of transport channels is reduced by some atoms.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
-Similar to the situation of participation ratio, transmission of Silicene,2l1 are close.
-Especially that of 2l2 areexactly the same, which is due to the structure symmetry of it.
-The anistropy of the transmission are clearly seen in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair.
-The localization  contributes a lot to ther anisotropy becuase these trends are silimar to their thermal conductivity.
+To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.
+The transmission function can be expressed as
+\begin{equation}
+  \begin{split}
+    \Theta(\omega)= Tr(
+    \mathbf{\widetilde{k}}_{a\alpha}
+    Im(\mathbf{g}_{\alpha\alpha})
+    \mathbf{\widetilde{k}}_{\alpha a}
+    \mathbf{G}_{a b}^*\\
+    \mathbf{\widetilde{k}}_{b\beta}
+    Im(\mathbf{g}_{\beta\beta})
+    \mathbf{\widetilde{k}}_{\beta b}
+    \mathbf{G}_{b a}
+    )
+  \end{split}
+\end{equation}
+where $\mathbf{\widetilde{k}}_{a\alpha}$,$\mathbf{\widetilde{k}}_{\alpha a}$ represents for the interaction between left lead and center region and its transposition,  $\mathbf{\widetilde{k}}_{b\beta}$,$\mathbf{\widetilde{k}}_{\beta b}$ the interaction between center and right lead.
+$\mathbf{g}$ and $\mathbf{G}$ the retarded Green's function of the leads and center rigion.$Tr$ and $Im$ means trace and imaginary function.
+Transmission function represents for the number of channels of a given frenquency.
+The more chanels means larger capability of thermal transportation.
+The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.
+
+FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
+The y-axis value of each panel is not the same so the transmission is given here only to explain the anisotropy of each strcutre.
+The steps in the curves are  characterisic of perfection of the structure.
+Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of Silicene and 2l1 are perfectly stepwise because of the perfect bonding and the absence of disorder.
+
+Similar to the situation of participation ratio, transmission of both directions of Silicene,2l1 are close.Especially that of 2l2 are exactly the same, which is due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair.
+This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity.
+The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this may contribute a lot to the anisotropy of the thermal transportation.
 

### 2017-06-28 src/fc.py

@@ -2,28 +2,22 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-28 11:12:34
+# @Last Modified time: 2017-06-28 00:02:58
 import aces.tools as tl
 from aces.graph import fig, pl
 import numpy as np
 from aces.f import capacity
 from aces.algorithm.kpoints import filter_along_direction as fad
 from ase import io
+from aces.io.phonopy.fc import readfc2, readfc3
 text_style = dict(
     horizontalalignment='left',
     verticalalignment='center',
     fontsize=12,
     fontdict={'family': 'serif'})
 vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
-f = open('cv.txt', 'w')
 with fig('cv.eps'):
     fi, axes = pl.subplots(figsize=(10, 7))
-    N = len(vs)
-    ind = np.arange(N)  # the x locations for the groups
-    width = 0.35       # the width of the bars
-
-    cv1 = []
-    cv2 = []
     for i, v in enumerate(vs):
         print(v)
         ax = axes
@@ -31,34 +25,10 @@ with fig('cv.eps'):
             v = "2lhex"
         if v == "2lr":
             v = "2lrt3"
-        file = v + "/0/secondorder/groupv/mesh.yaml"
-        data = tl.parseyaml(file)
-        freqs = []
-        qpoints = []
-        for phonon in data['phonon']:
-            qp = phonon['q-position']
-            for band in phonon['band']:
-                frequency = band['frequency']
-                gv = np.array(band['group_velocity'])
-                freqs.append(frequency)
-                qpoints.append(qp)
-        freqs = np.array(freqs)
-        qpoints = np.array(qpoints)
-        dth = np.pi / 10
-        phi = 0.0
-        fil = fad(qpoints, phi, dth)
+        file = v + "/0/secondorder/FORCE_CONSTANTS"
+        fc2 = readfc2(file)
         atoms = io.read(v + "/0/secondorder/POSCAR")
-        V = np.linalg.norm(atoms.cell[0]) * np.linalg.norm(atoms.cell[1]) * (
-            atoms.positions[:, 2].max() - atoms.positions[:, 2].min())
[…]

### 2017-06-28 src/pr_direction.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 16:26:09
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 21:59:58
+# @Last Modified time: 2017-06-28 16:11:57
 
 from aces.graph import fig, setLegend, pl
 from aces.algorithm.kpoints import filter_along_direction as fad
@@ -37,7 +37,7 @@ with fig('pr_direction.eps'):
                     phi = np.pi / 2.0
                 fil = fad(y, phi, dth)
                 q = y[fil][:, [3, 4]]
-                x, y = binmeanx(q, [0, 4.5], .5)
+                x, y = binmeanx(q, [0, 4.9], .5)
                 mfc = [colors[0], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
                 ax.plot(x, y, ls=ls,

### 2017-06-28 latex/paper.tex
Update paper.tex

@@
 The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering.
-Considering three-phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons.
+Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical.
+So this process is called Umpack process( U process).
+And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $q''=q+-q'$), which is called Normal process (N process) or momentum conservation process.
+If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance.
+The phonon scattering rate could be obtained by Fermi-golden rule
+
+\begin{equation}
+\end{equation}
+
+considering only the relaxation time approxmition(RTA).
+We then use iterative method to consider in cross influence of the phonon exitatioin, witch alway give lager lifetime compare to RTA and more close to the real value.
+
+the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+The values are averaged for frequency bins to reduce complexity.
 The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.

### 2017-06-28 latex/paper.tex
Update paper.tex

@@
 considering only the relaxation time approxmition(RTA).
-We then use iterative method to consider in cross influence of the phonon exitatioin, witch alway give lager lifetime compare to RTA and more close to the real value.
+We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
 
@@
 The result is also consist with the trends of thermal conductivity.
+The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity.
+The relation between acoustic phonon lifetime and frequency could be expressed as $\tau\=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
+The coefficient k for both direction are displayed in Table.3.
+The degree of divergence exhibit large anisotropy for the structures.
+However the difference of lifetime is pretty small when frequency is relatively high.
+So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.
 
@@
 
-The anisotroy of phonon lifetime is due to the anisotropy of anharmonic effect. The Gruneisen parameters which represent the degree of anharmonic effect is also shown in FIG.\ref{fig:gruneisen}.
+The anisotropy of phonon lifetime is due to the anisotropy of anharmonic effect. To quatitily check the anharmonic effect we calculate the Gruneisen parameters with
+
+\begin{equation}
+
+\end{equation}
+
+where V is the volumn of the unicell and $\omega$ is the phonon frequency.
+The shift of $\omega$ with V is due to the divirience from paraodic potential which reprensents for the harmonic situation.
+When the potenial is harmonic , all the Gruneisen parameters will vanish.
+The Gruneisen parameters of all the structures are shown in FIG.\ref{fig:gruneisen}.
 The larger the anharmonic effect the smaller the scattering lifetime of the phonons.
+The most anharmonic phonons exist in the low frequency region and consist with previous result of phonon lifetime.
+The large difference between zigzag value and armchair could explain the anisotropy of phonon scattering.
+
+To obtain a clear connection between  the surface characteristic we also statistic the force constants of different position of the structures.
 

### 2017-08-12 src/tc_freq.py
添加tc_freq,调整单位的顺序，修改了pre的图

@@ -1,0 +1,60 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-16 18:34:55
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-08-11 11:01:28
+
+
+from aces.graph import fig, setLegend, pl
+import numpy as np
+from aces.algorithm.kpoints import filter_along_direction as fad
+from aces.io.shengbte import get_qpoints_full as gqf, get_tau, get_omega
+from aces.f import binmeanx
+markers = ['^', 's', "8"]
+colors = "k,r,b,g,purple".split(',')
+import matplotlib
+matplotlib.rcParams['ytick.minor.width'] = 1.5
+matplotlib.rcParams['ytick.minor.size'] = 3
+with fig('tc_freq.eps'):
+    fi, axes = pl.subplots(3, 3, sharex=True, sharey=False, figsize=(10, 10))
+    for j in range(3):
+        if j == 0:
+            vs = "2l1,2l2,2lhex".split(',')
+        if j == 1:
+            vs = "3l1,3l2,4l1".split(',')
+        if j == 2:
+            vs = "5l1,6l1,Silicene".split(',')
+        for i, v in enumerate(vs):
+            for s in ['z', 'a']:
+                ax = axes[j, i]
+                dir = "%s/0/SHENG" % v
+                if v == "2l1":
+                    dir = "2l1/0/sheng.1"
+                kappa = np.loadtxt(
+                    dir + '/T300K/BTE.cumulative_kappaVsOmega_tensor')
+                df = kappa[2, 0] - kappa[0, 0]
+                p = np.arange(len(kappa) - 2)
+                if s == "z":
+                    ax.plot(
+                        kappa[p, 0],
+                        (kappa[p + 2, 1] - kappa[p, 1]) / df,
+                        label=v + s)
+                else:
+                    ax.plot(
+                        kappa[p, 0],
+                        (kappa[p + 2, 5] - kappa[p, 5]) / df,
+                        label=v + s)
+
+                ax.set_xlim([0, 20.55])
+                ax.set_ylim([0, None])
+                ax.set_yticks([])
+                setLegend(ax, fontsize=10)
+    fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
+    fi.text(
+        0.05,
+        0.5,
+        'Thermal Conductivity (W/mK)',
+        va='center',
[…]

### 2017-10-23 latex/paper.tex
test latexdiff

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-06-28 17:35:13
+% @Last Modified time: 2017-10-23 17:41:29
 \documentclass[%
@@
 \title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
-\author{Yang Zhou${}^{1,2}$}
-\author{Chao-Yu Chen${}^{3}$}
-\author{Zhi-Xin Guo${}^{3}$}
+\author{Yang Zhou${}^{1,3}$}
+\author{Chao-Yu Chen${}^{2}$}
+\author{Zhi-Xin Guo${}^{2}$}
 \email{zxguo08@hotmail.com}
-\author{Shi-You Chen}
-\author{Hong-Jun Xiang}
-\author{Xin-Gao Gong${}^{1,2}$}
+\author{Shi-You Chen${}^{1}$}
+\author{Hong-Jun Xiang${}^{1}$}
+\author{Xin-Gao Gong${}^{1,3}$}
 \email{xggong@fudan.edu.cn}
@@
   ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
-  ${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
-  ${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
+  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
+  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
 }
@@
 
-With the development of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials.
+With the development1 of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials.
 The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size.
-For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li,Yu2014}.
+For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}.
 Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}.
@@
 We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons.
-Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical.
+Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
 So this process is called Umpack process( U process).
-And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $q''=q+-q'$), which is called Normal process (N process) or momentum conservation process.
+And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
 If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance.
-The phonon scattering rate could be obtained by Fermi-golden rule
-
-\begin{equation}
-\end{equation}
-
-considering only the relaxation time approxmition(RTA).
+The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014}.considering only the relaxation time approxmition(RTA).
 We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
 
-the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
 The values are averaged for frequency bins to reduce complexity.
@@
 The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity.
-The relation between acoustic phonon lifetime and frequency could be expressed as $\tau\=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
+The relation between acoustic phonon lifetime and frequency could be expressed as $\tau=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
 The coefficient k for both direction are displayed in Table.3.
@@
 \begin{equation}
-
+  \gamma_{k \sigma}=- \frac{V}{\omega_{k \sigma}} \frac{\partial \omega_{k \sigma}}{\partial V}
 \end{equation}
 
-where V is the volumn of the unicell and $\omega$ is the phonon frequency.
-The shift of $\omega$ with V is due to the divirience from paraodic potential which reprensents for the harmonic situation.
+where V is the volumn of the unicell and $\omega_{k \sigma}$ is the phonon frequency.
+The shift of $\omega_{k \sigma}$ with V is due to the divirience from paraodic potential which reprensents for the harmonic situation.
 When the potenial is harmonic , all the Gruneisen parameters will vanish.

### 2017-10-23 latex/paper-last.tex
test latexdiff

--- 2017-10-23 latex/paper.tex
@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-10-23 17:41:29
+% @Last Modified time: 2017-08-08 13:47:15
 \documentclass[%
@@
 
-With the development1 of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials.
+With the development of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials.
 The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size.

### 2017-10-23 latex/run_diff.py

@@ -1,0 +1,14 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-21 01:41:49
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-10-23 17:53:02
+import os
+os.chdir("bin")
+os.system("cp ../*.tex .")
+os.system('latexdiff paper.tex paper-last.tex>diff.tex')
+os.system('latex diff.tex')
+os.system('bibtex diff')
+os.system('latex diff.tex')
+os.system('latex diff.tex')
+os.system("dvipdft diff")

### 2017-10-23 latex/paper.tex
按照郭志新的意见修改introduction

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-10-23 17:41:29
+% @Last Modified time: 2017-10-23 21:19:00
 \documentclass[%
@@
 
-With the development1 of the existing silicon based circuit industry, the requirements of its integration and miniaturization make a lot of research work focusing on the application of the new two-dimensional materials.
-The theory and experiments in the last 10 years show that some new two-dimensional materials have many novel and excellent physical properties due to their structure and size.
-For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}.
-Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}.
-Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}.
-However, materials prepared in the practical application is often multilayer structure to a few nanometers.
-Previous studies have focused on the weak Van der Waals interaction (vdW), and there is no surface reconstruction.
+Many theorical experiment result has shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them potential in the application of thermalelectric field where the thermalelectric figure of merit $ZT=\frac{S^2 \sigma T}{\kappa}$ could be optimized by the reduced thermal condutvitiy.
+For example
+the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
+And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicon nanowires.At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
+Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications.
+However, the study on the properties of multilayer silicon thermal transport is still very rare.
+
+The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction.
 There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure.
@@
 In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicon, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.
+The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.
 
-Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
+Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases.
+For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}.
+Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}.
+Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}.
+In the case of silicon, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}.
+And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction.
+This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.
+
+In this work we use multilayer silicon as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
 And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon.
@@
 In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.
-
-At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
-Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications.
-However, the study on the properties of multilayer silicon thermal transport is still very rare, To this end, based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.
+Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.
 

### 2017-10-23 latex/run_diff.py
成功实现diff

@@ -2,11 +2,19 @@
 # @Author: YangZhou
 # @Date:   2017-06-21 01:41:49
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-10-23 17:53:02
+# @Last Modified time: 2017-10-23 22:03:37
 import os
+import re
 os.chdir("bin")
 os.system("cp ../*.tex .")
-os.system('latexdiff paper.tex paper-last.tex>diff.tex')
+os.system('latexdiff paper-last.tex paper.tex >diff.tex')
+f = open('diff.tex', encoding="utf-8")
+s = f.read()
+s = re.sub(r'({[^}]*)\n\n([^}]*})', r'\1\2', s)
+f.close()
+f = open('diff.tex', 'w', encoding="utf-8")
+f.write(s)
+f.close()
 os.system('latex diff.tex')
 os.system('bibtex diff')
 os.system('latex diff.tex')

### 2017-10-29 latex/paper.tex
修改文章

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-10-23 21:19:00
+% @Last Modified time: 2017-10-29 21:07:47
 \documentclass[%
@@
 
-In this paper, based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007}, we study the thermal conductivity of multilayer silicon structure by using the non-equilibrium temperature gradient method.
+In this paper, we study the thermal conductivity of multilayer silicon structure by using the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
 Because of the abundant silicon structure model, the phase reconstruction has attracted much attention.
-In order to well simulate the structures of different phase by MD, the latest Mod potential is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.
+In order to well simulate the structures of different phase by BTE, the latest Mod potential based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007} is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.
 Firstly, we use conjugate gradient method to optimize these structures.
@@
 
-\begin{table*}
-  \caption{\label{tab:table1}
-    Symmetry of the structures, binding energy $E_c(eV/Si)$ and structure features}
-  \begin{ruledtabular}
-    \begin{tabular}{cccccccc}
-      Name
-           & Minimal period
-           & Symmetry
-           & $E_c$ in Guo
-           & $E_c$ in MD
-           & Buckling Feature                                                                       \\
-      \hline
-      2l1  & $1 \times 1$             & Cmme    & 5.000 & 4.145 & Smooth                            \\
-      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
-      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
-      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
-      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
-      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
-      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
-      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
-      2l2  & $\sqrt{2}\times\sqrt{2}$ & C12/m1  & 4.991 & 4.204 & Large buckling and symmetric      \\
-      2l3  & $2 \times 2$             & C12/m1  & 5.063 & 4.257 & Large buckling and tilt symmetric \\
-      2lh  & $2 \times 2$             & P1      & 5.073 & 4.216 & Large buckling                    \\
-      2lr3 & $\sqrt{3}\times\sqrt{3}$ & P1      & -     & 4.225 & Small buckling and symmetric      \\
-      3l1  & $2 \times 1$             & P121/m1 & 5.138 & 4.337 & -                                 \\
-      3l2  & $2 \times 1$             & P1      & 5.135 & 4.298 & -                                 \\
-      4l1  & $2 \times 1$             & P1      & 5.225 & 4.368 & -                                 \\
-    \end{tabular}
-  \end{ruledtabular}
-
-\end{table*}
-
 From TABLE.\ref{tab:table1}, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure.
@@
 5 kinds of silicon structures of armchair and zigzag were selected to study.
-The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:2l_length}.
+The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:tc_length_sheng}.
 the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh.
@@
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/2l_length}
-  \caption{\label{fig:2l_length} (color online) The thermal conductivity dependence on length for five types of bilayer silicon.
-The scatters are the results of MD simulations while the lines are fitted with Eq.\ref{eq_nemd}.
+  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
+  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for five types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
 The letter z/a in the legend mean the transport direction is zigzag/armchair.}
@@
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/vl_length}
-  \caption{\label{fig:vl_length}(color online) The dependence on length of thermal conductivity for silicon with variable layers.}
+  \includegraphics[width=0.48\textwidth]{images/tc_freq}
+  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
 \end{figure}
@@
 \begin{table*}
-  \caption{\label{tab:table2}
+  \caption{\label{tab:table1}
     The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
   \begin{ruledtabular}
-    \begin{tabular}{cccccccccccc}
-            & $\kappa_{z,\infty}$
-            & $\kappa_{a,\infty}$
-            & $\chi$
-            & $Cv_{z}$
-            & $Cv_{a}$
-            &
+    \begin{tabular}{ccccccc}
+          & Minimal period
           & $\kappa_{z,\infty}$
@@
       \hline
-      2l1   & 11.6                & 6.5  & 43.9\% & 165.8 & 166.7 & 2l2      & 1.5  & 1.2  & 20.0\% & 38.44 & 38.44 \\
-      2l3   & 5.0                 & 9.7  & 48.5\% & 23.38 & 23.38 & 2lr3     & 8.2  & 3.5  & 57.3\% & 10.15 & 10.15 \\
-      2lh   & 2.0                 & 2.5  & 20.0\% & 22.42 & 22.42 & 3l1      & 11.5 & 2.9  & 74.8\% & 52.22 & 52.46 \\
-      3l2   & 10.2                & 5.2  & 49.0\% & 55.56 & 55.84 & 4l1      & 10.2 & 3.4  & 66.7\% & 37.71 & 37.89 \\
-      5l1   & 11.7                & 5.7  & 51.3\% & 29.17 & 29.32 & 6l1      & 10.3 & 7.8  & 24.3\% & 23.73 & 23.86 \\
-      8l1   & 13.2                & 14.9 & 11.4\% & 17.26 & 17.36 & 10l1     & 13.3 & 13.5 & 1.5\%  & -     & -     \\
-      Si111 & 33.6                & 34.7 & 3.2\%  & -     & -     & Silicene & 11.4 & 11.6 & 1.7\%  & 606.4 & 613.4 \\
+      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
+      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
+      2lh & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
+      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
+      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
+      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
+      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
+      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
     \end{tabular}
@@
 However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
-
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/bands}
-  \caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points.
-(a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
-\end{figure}
 
@@
 The relation between the group velocity of both direction are contrast with that of the thermal conductivity, which indicate that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects.
-
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/pr_direction}
-  \caption{\label{fig:pr_direction} (color online) The participation ratio.}
-\end{figure}
 
@@
 
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/gruneisen}
-  \caption{\label{fig:gruneisen} (color online)Gruneisen parameters.}
-\end{figure}
-
 The anisotropy of phonon lifetime is due to the anisotropy of anharmonic effect. To quatitily check the anharmonic effect we calculate the Gruneisen parameters with

### 2017-10-29 src/bands_phonopy.py

@@ -1,0 +1,65 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-15 16:27:39
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-10-28 11:59:02
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+vs = np.array('2l1,2l2,3l1,4l1,6l1,10l1'.split(',')).reshape([2, 3])
+ch = 'abcdef'
+text_style = dict(
+    horizontalalignment='left',
+    verticalalignment='center',
+    fontsize=14,
+    fontdict={'family': 'serif'})
+import matplotlib
+matplotlib.rcParams['xtick.major.width'] = 0
+with fig('bands_phonopy.eps'):
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 7))
+    for i in range(2):
+        for j in range(3):
+            label = ch[i * 3 + j] + ")"
+            v = vs[i, j]
+            file = "multisi_phonon/" + v
+            y = np.loadtxt(file, skiprows=2)
+            k = y[:, 3]
+            fq = y[:, 4:]
+            m = fq.shape[1]
+            # for mi in range(m):
+            G1 = 0.707107
+            X = 1.20711
+            Y = 1.91421
+            G2 = 2.41421
+            LX = X - G1
+            LY = G2 - Y
+            L = LX + LY
+            fil = (k > G1 - 0.02) * (k < X + 0.02)  # G->X
+            axes[i, j].plot(
+                X - k[fil][::-1], fq[fil][::-1], color='k', alpha=0.9)
+            fil = (k > Y - 0.02) * (k < G2 + 0.02)  # Y->G
+            axes[i, j].plot(
+                G2 - k[fil][::-1] + LX, fq[fil][::-1], color='k', alpha=0.9)
+            axes[i, j].text(
+                .05, .95, label, transform=axes[i, j].transAxes, **text_style)
+            axes[i, j].set_xticks([])
+            # axes[i,j].set_xlim([0,2.41421])
+            # axes[i,j].set_xlim([0,L])
+            axes[i, j].set_ylim([0, 19])
+            # t=(0+0.1,0.707107,1.20711,1.91421,2.41421-0.1);
+            # labels=("K",r"$\Gamma$","X","Y",r"$\Gamma$")
[…]

### 2017-10-29 src/gruneisen.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-26 21:53:59
+# @Last Modified time: 2017-10-29 18:20:33
 
 
 from aces.graph import fig, setLegend, pl
@@ -16,14 +16,12 @@ import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('gruneisen.eps'):
-    fi, axes = pl.subplots(3, 3, sharex=True, sharey=True, figsize=(10, 10))
-    for j in range(3):
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 6))
+    for j in range(2):
         if j == 0:
-            vs = "2l1,2l2,2lhex".split(',')
+            vs = "2l1,2lhex,3l1".split(',')
         if j == 1:
-            vs = "3l1,3l2,4l1".split(',')
-        if j == 2:
-            vs = "5l1,6l1,Silicene".split(',')
+            vs = "4l1,5l1,Silicene".split(',')
         for i, v in enumerate(vs):
             for s in ['z', 'a']:
 
@@ -46,18 +44,18 @@ with fig('gruneisen.eps'):
                     omega_full[fil].flatten(),
                     gru_full[fil].flatten()]
                 q = np.nan_to_num(q)
-                x, y = binmeanx(q, [0, 4.49], 0.5)
+                x, y = binmeanx(q, [0, 20.49], 1.5)
                 mfc = [colors[i], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
 
-                ax.semilogy(x, np.abs(y), ls=ls,
-                            marker=markers[i],
-                            markersize=9,
-                            markeredgecolor=colors[i],
-                            markerfacecolor=mfc,
-                            color=colors[i],
-                            label=v + s)
-                ax.set_xlim([0, 4.9])
+                ax.plot(x, np.abs(y), ls=ls,
+                        marker=markers[i],
+                        markersize=9,
+                        markeredgecolor=colors[i],
+                        markerfacecolor=mfc,
+                        color=colors[i],
+                        label=v + s)
+                ax.set_xlim([0, 20.49])
                 setLegend(ax, fontsize=10)
[…]

### 2017-10-29 src/gv.py

@@ -2,37 +2,43 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-26 21:44:53
+# @Last Modified time: 2017-10-29 11:14:58
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
 import numpy as np
 from aces.f import binmeanx
+from aces.io.shengbte import get_w_final, get_qpoints, get_omega, get_tau, get_v
 text_style = dict(
     horizontalalignment='left',
     verticalalignment='center',
     fontsize=12,
     fontdict={'family': 'serif'})
-vs = '2l1,2l2,2l3,2lh,2lr,3l1,3l2,4l1,5l1,6l1,8l1,Silicene'.split(',')
+vs = '2l1,2lh,3l1,4l1,5l1,6l1'.split(',')
 with fig('gv.eps'):
-    fi, axes = pl.subplots(2, 6, sharex=True, sharey=True, figsize=(10, 7))
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 7))
     for i, v in enumerate(vs):
         print(v)
-        ax = axes[i // 6, i % 6]
+        ax = axes[i // 3, i % 3]
         if v == "2lh":
             v = "2lhex"
         if v == "2lr":
             v = "2lrt3"
-        file = v + "/0/secondorder/groupv/mesh.yaml"
-        data = tl.parseyaml(file)
-        freqs = []
-        gvs = []
-        for phonon in data['phonon']:
-            qp = phonon['q-position']
-            for band in phonon['band']:
-                frequency = band['frequency']
-                gv = np.array(band['group_velocity'])
-                freqs.append(frequency)
-                gvs.append(gv)
+        dir = "%s/0/SHENG" % v
+        # file = v + "/0/secondorder/groupv/mesh.yaml"
+        # data = tl.parseyaml(file)
+        # freqs = []
+        # gvs = []
+        # for phonon in data['phonon']:
+        #     qp = phonon['q-position']
+        #     for band in phonon['band']:
+        #         frequency = band['frequency']
+        #         gv = np.array(band['group_velocity'])
+        #         freqs.append(frequency)
+        #         gvs.append(gv)
+        omega = get_omega(dir)
+        cv = get_v(dir)
[…]

### 2017-10-29 src/pr_direction.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 16:26:09
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-28 16:11:57
+# @Last Modified time: 2017-10-28 16:07:45
 
 from aces.graph import fig, setLegend, pl
 from aces.algorithm.kpoints import filter_along_direction as fad
@@ -10,16 +10,16 @@ import numpy as np
 from aces.f import binmeanx
 text_style = dict(horizontalalignment='left', verticalalignment='center',
                   fontsize=12, fontdict={'family': 'serif'})
-vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+vs = '2l1  2lh  3l1   4l1  5l1  6l1'.split()
 markers = ['^', 's', "8"]
 colors = "k,r,b,g,purple".split(',')
 with fig('pr_direction.eps'):
 
     fi, axes = pl.subplots(
-        3, 4, sharex=True, sharey=True, figsize=(10, 10))
+        2, 3, sharex=True, sharey=True, figsize=(10, 6))
     print(vs)
-    for j in range(3):
-        vv = np.array(vs).reshape([3, 4])[j]
+    for j in range(2):
+        vv = np.array(vs).reshape([2, 3])[j]
         for i, v in enumerate(vv):
             for s in ['z', 'a']:
                 ax = axes[j, i]
@@ -37,7 +37,7 @@ with fig('pr_direction.eps'):
                     phi = np.pi / 2.0
                 fil = fad(y, phi, dth)
                 q = y[fil][:, [3, 4]]
-                x, y = binmeanx(q, [0, 4.9], .5)
+                x, y = binmeanx(q, [0, 20.9], 1.5)
                 mfc = [colors[0], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
                 ax.plot(x, y, ls=ls,
@@ -46,7 +46,7 @@ with fig('pr_direction.eps'):
                         markeredgecolor=colors[0],
                         markerfacecolor=mfc,
                         color=colors[0], label=v + s)
-                ax.set_xlim([0, 4.9])
+                ax.set_xlim([0, 20.9])
                 ax.set_ylim([0, 1.2])
                 setLegend(ax, fontsize=10)
     fi.text(0.5, 0.04, 'Phonon Frequency(THz)', ha='center')

### 2017-10-29 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 21:24:07
+# @Last Modified time: 2017-10-29 18:25:16
 
 
 from aces.graph import fig, setLegend, pl
@@ -16,14 +16,12 @@ import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('tau.eps'):
-    fi, axes = pl.subplots(3, 3, sharex=True, sharey=True, figsize=(10, 10))
-    for j in range(3):
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 6))
+    for j in range(2):
         if j == 0:
-            vs = "2l1,2l2,2lhex".split(',')
+            vs = "2l1,2lhex,3l1".split(',')
         if j == 1:
-            vs = "3l1,3l2,4l1".split(',')
-        if j == 2:
-            vs = "5l1,6l1,Silicene".split(',')
+            vs = "4l1,5l1,6l1".split(',')
         for i, v in enumerate(vs):
             for s in ['z', 'a']:
                 ax = axes[j, i]
@@ -47,7 +45,7 @@ with fig('tau.eps'):
                     tau_full[fil].flatten()]
                 q = np.nan_to_num(q)
 
-                x, y = binmeanx(q, [0.0, 5.0], dx=0.5)
+                x, y = binmeanx(q, [0.0, 20.0], dx=1.5)
                 mfc = [colors[i], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
                 ax.semilogy(
@@ -60,8 +58,8 @@ with fig('tau.eps'):
                     markerfacecolor=mfc,
                     color=colors[i],
                     label=v + s)
-                ax.set_xlim([0, 4.55])
-                ax.set_ylim([1e-0, 1e3])
+                ax.set_xlim([0, 20.55])
+                ax.set_ylim([1e-1, 2e2])
                 setLegend(ax, fontsize=10)
     fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
     fi.text(

### 2017-10-29 src/tc_freq.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-08-11 11:01:28
+# @Last Modified time: 2017-10-28 15:40:24
 
 
 from aces.graph import fig, setLegend, pl
@@ -16,14 +16,12 @@ import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('tc_freq.eps'):
-    fi, axes = pl.subplots(3, 3, sharex=True, sharey=False, figsize=(10, 10))
-    for j in range(3):
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 6))
+    for j in range(2):
         if j == 0:
-            vs = "2l1,2l2,2lhex".split(',')
+            vs = "2l1,2lhex,3l1".split(',')
         if j == 1:
-            vs = "3l1,3l2,4l1".split(',')
-        if j == 2:
-            vs = "5l1,6l1,Silicene".split(',')
+            vs = "4l1,5l1,6l1".split(',')
         for i, v in enumerate(vs):
             for s in ['z', 'a']:
                 ax = axes[j, i]
@@ -34,20 +32,32 @@ with fig('tc_freq.eps'):
                     dir + '/T300K/BTE.cumulative_kappaVsOmega_tensor')
                 df = kappa[2, 0] - kappa[0, 0]
                 p = np.arange(len(kappa) - 2)
+                mfc = [colors[0], 'w'][s == 'a']
+                ls = ['-', '-.'][s == 'a']
                 if s == "z":
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 1] - kappa[p, 1]) / df,
-                        label=v + s)
+                        label=v + s, ls=ls,
+                        marker=markers[0],
+                        markersize=9,
+                        markeredgecolor=colors[0],
+                        markerfacecolor=mfc,
+                        color=colors[0])
                 else:
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 5] - kappa[p, 5]) / df,
-                        label=v + s)
+                        label=v + s, ls=ls,
+                        marker=markers[0],
+                        markersize=9,
+                        markeredgecolor=colors[0],
+                        markerfacecolor=mfc,
[…]

### 2017-10-29 src/tc_length_sheng.py

@@ -1,0 +1,146 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-14 22:16:16
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-10-29 19:10:10
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+from ase import io
+
+
+def ff(p, x):
+    return p[0] * (1.0 - np.exp(-x / p[1]))
+    # return 1.0/(p[1]/x+1/p[0])-p[2]
+    # return p[0]*p[1]**x
+kas = []
+with fig('tc_length_sheng.eps', figsize=(7, 8)):
+    markers = ['s', '8', '^', 'D', '>']
+    colors = "k,r,b,purple,g".split(',')
+    vs = '2l1,2l2,2lhex'.split(',')
+    text_style = dict(horizontalalignment='left', verticalalignment='center',
+                      fontsize=14, fontdict={'family': 'serif'})
+    fi, axes = pl.subplots(2, 1, sharex=True, figsize=(7, 8))
+    ax1 = axes[0]
+    for s in ['z', 'a']:
+        for i, v in enumerate(vs):
+            dir = "%s/0/SHENG" % v
+            if v == "2l1":
+                dir = "2l1/0/sheng.1"
+            kappa = np.loadtxt(
+                dir + '/T300K/BTE.cumulative_kappa_tensor')[::3]
+            m = markers[i]
+            c = colors[i]
+
+            l = kappa[:, 0]
+            atoms = io.read(v + "/0/secondorder/POSCAR")
+            if v == 'Silicene':
+                nlayer = 1
+            else:
+                nlayer = int(v.split('l')[0])
+            ss = np.linalg.norm(atoms.cell[2]) / (
+                3.34 * nlayer)
+
+            z = kappa[:, 1] * ss
+            a = kappa[:, 5] * ss
+            if s == 'z':
+                opts = dict(
+                    markeredgecolor='w',
+                    marker=m,
+                    color=c,
+                    markersize=8 + 2,
+                    ls='.')
+                o1 = "-"
+                ka = z
+            else:
+                opts = dict(
+                    markeredgecolor=c,
+                    marker=m,
+                    color='w',
+                    markersize=8,
+                    ls='.')
+                o1 = "--"
+                ka = a
[…]

### 2017-10-29 src/transmission.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   1970-01-01 08:00:00
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-23 21:23:56
+# @Last Modified time: 2017-10-28 15:56:36
 from aces.tools import *
 from ase import io
 from aces.graph import fig, setLegend, pl, fit
@@ -12,9 +12,9 @@ matplotlib.rcParams['ytick.major.width'] = 1
 import numpy as np
 text_style = dict(horizontalalignment='left', verticalalignment='center',
                   fontsize=12, fontdict={'family': 'serif'})
-vs = '2l1  2l2  2l3  2lh  2lr3  3l1  3l2  4l1  5l1  6l1  8l1  Silicene'.split()
+vs = '2l1   2lh   3l1    4l1  5l1  6l1 '.split()
 with fig('transmission.eps'):
-    fi, axes = pl.subplots(6, 2, sharex=True, sharey=False, figsize=(10, 7))
+    fi, axes = pl.subplots(3, 2, sharex=True, sharey=False, figsize=(10, 7))
     for i, v in enumerate(vs):
         ax = axes[i // 2, i % 2]
         file = "negf/" + v + "/transmission.txt"

### 2017-11-01 latex/paper.tex
调整structure

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-10-29 21:07:47
+% @Last Modified time: 2017-11-01 09:13:48
 \documentclass[%
@@
 
-In this paper, we study the thermal conductivity of multilayer silicon structure by using the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
-Because of the abundant silicon structure model, the phase reconstruction has attracted much attention.
-In order to well simulate the structures of different phase by BTE, the latest Mod potential based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007} is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.
-Firstly, we use conjugate gradient method to optimize these structures.
-All structures are shown in FIG.\ref{fig:structures}.
+The thermal conductivity of multilayer silicon structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
+In order to well simulate the structures of different phase by BTE, the latest Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
+It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA).
+However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants.
+For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.
+
+All structures are shown in FIG.\ref{fig:structures}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc.
+) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
+TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicon.
 
@@
   \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicon.
-Within which (a) to (e) are top view and side view of bilayer structures.
-(f) to (g) are side view of trilayer structures and (h) is that of four-layers.
+Within which  are top view and side view of the studied structures.
 The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface.
 All the atoms on the bottom surface are labeled as blue.
-The blacks represent those that are inside the structure.
-The top view of the cells is shown in the last.}
+The greens represent those that are inside the structure.
+The orientation of top view of the cells is labeled as arrows.}
 \end{figure}
 
-For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc.
-) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
-TABLE.\ref{tab:table1} lists the structure name, the minimum repeat cell periodicity, the binding energies, the first principle binding energies and the structural properties of the multilayer silicon.
-The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
-It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA).
-However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants.
-For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.
+Firstly, we use conjugate gradient method to optimize these structures.  According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
 
-From TABLE.\ref{tab:table1}, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure.
-The simulation is doing by velocity Verlet integral algorithm with the timestep to be $1 fs$.
-The length of the system in the x direction is $10 - 100nm$, the transverse direction y is in periodic boundary condition with its simulated width to be 5 nm, and free boundary condition is applied in z direction.
-At the same time the outermost two ends of the x direction are fixed, close to witch a 3nm with Nose-Hoover bath is applied.
-The left and right ends of the temperature control at $310K$ and $290K$.
-The simulation is carried out by NVT for $0.4ns$, then control the temperature gradient for $10 ns$, and finally we statistics the data of the last $10ns$.
-By Fourier's law, the relationship between thermal conductivity and heat flux is
+The thermal conductivity tensor could be calculated with
 
 \begin{equation}
-  \kappa = \frac{ J_x}{ \nabla T \cdot S} \label{eq_nemd}
+  \kappa^{\alpha\beta} = \sum_{k \sigma}{c_{k \sigma}v^{\alpha}_{k \sigma}v^{\beta}_{k \sigma}\tau_{k \sigma}} \label{eq:kappasum}
 \end{equation}
 
-where $\kappa$ stands for thermal conductivity, $J_x$ , $\nabla T=(T_L-T_R)/L_x$ is the average heat flux and temperature gradient along x direction respectively.
-$T_L$, $T_R$ and $L_x$ means the temperature of the two ends and the sample length between the heat baths.
-$S=W \cdot nd$ is the total cross area, where W,n,d is the size in the y direction, the layer number and the thickness of each layer.
-According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
+Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime.
+The heat capacity  could be computed with Eq.
+\ref{eq:cv} .
+
+\begin{equation}
+  c_{k \sigma}=\frac{\hbar \omega_{k \sigma} }{V} \frac{\partial f(\omega_{k \sigma},T)}{\partial T} \label{eq:cv}
+\end{equation}
+
+Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
+
+The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs.
+Both second- and third-order FCs are extracted from finite displacement method realized in Phonopy\cite{Togo2008} and Thridorder respectively.
+Both second-order and third-order  FCs are calculated with $3 \times 3 \times 1$ supercell with a $15\times 15 \times 3$ Monkhorst-Pack q-point mesh.
+The phonon group velocity  and transmision function are calculated with  with second order force constants.
+The interaction range of third-order FCs is truncated up to 4th neighbor.
+Iteration method is used instead of relaxation time approximision (RTA) to avoid underestimate of thermal concutivity.
 
@@
 
-We firstly investigate the effect of surface reconstruction on thermal conductivity.
-5 kinds of silicon structures of armchair and zigzag were selected to study.
-The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:tc_length_sheng}.
-the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh.
+Surface reconstruction affects quite a lot on the intensity and anisotropy of thermal conductivity.
+The relationship between the thermal conductivity  and the length of three kinds of bilayer silicon along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a).
+The thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh.
 In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic.
@@
   \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
-  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for five types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
+  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
 The letter z/a in the legend mean the transport direction is zigzag/armchair.}
@@
 
-The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}.
+The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table1}.
 It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure).
@@
 However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
-
-In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures.
-The $10 \times  10  \times  1$ multilayer structure is chosen.
-The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
-According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport.
-There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction.
-FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2.
-The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy.
-Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction.
-Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease.
-At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length.
-The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair.
-With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged.
-On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number.
-Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.
-
-The thermal conductivity tensor could be calculated with
-
-\begin{equation}
-  \kappa^{\alpha\beta} = \sum_{k \sigma}{c_{k \sigma}v^{\alpha}_{k \sigma}v^{\beta}_{k \sigma}\tau_{k \sigma}} \label{eq:kappasum}
-\end{equation}
-
-Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime.
-The anisotropy could derive from these factors and it's worth finding the most important ones.
-
-Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ , calculate each of their heat capacity with
-
-\begin{equation}
-  c_{k \sigma}=\frac{\hbar \omega_{k \sigma} }{V} \frac{\partial f(\omega_{k \sigma},T)}{\partial T}
-\end{equation}
-
-Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
+Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ ,
 The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$.
-The average heat capacity of the structures are shown in Table.\ref{tab:table2} .
+The average heat capacity of the structures are shown in Table.\ref{tab:table1} .
 Large difference could be found between the $Cv$ of the structures.
@@
   \includegraphics[width=0.48\textwidth]{images/gv}{}
-  \caption{\label{fig:gv} (color online)Group Velocity.}
+  \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
 \end{figure}
@@
 
-The different localization situation  along each direction determines the anisotroy of group velocity  along that direction.
-To qualitatively measure the physical mechanism of phonon localization we carried out a vibrational eigenmode analysis.
-Mode localization can be quantitatively characterized by the phonon participation ratio $P_{k\sigma}$  \cite{Allen1999}for each eigen-mode $k\sigma$ as
-
-\begin{equation}
-  P_{k\sigma}= \frac{1}{N \sum_{i}
-    {(\sum_\alpha{\epsilon^{i\alpha}_{k\sigma}
-        \epsilon^{*i\alpha}_{k\sigma}})^2}}
-\end{equation}
-
-where N is the atom number and $\epsilon^{i\alpha}_{k\sigma}$ is the eigenvector component of mode $k\sigma$ for the i-th atom and $\alpha$ direction.
-The value of participation ratio is between 0 and 1 which measures the fraction of atoms participating a given phonon mode.
-If the mode is localized then its trends with N is O(1/N) while delocalized modes with O(1).
+In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures.
+The $10 \times  10  \times  1$ multilayer structure is chosen.
+The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
+According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport.
+There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction.
+FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2.
+The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conductive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy.
+Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction.
+Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease.
+At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length.
+The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair.
+With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged.
+On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number.
+Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.
 

### 2017-11-06 latex/paper.tex
编译后清理bin目录，防止误编辑bin目录中的tex

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-01 09:13:48
+% @Last Modified time: 2017-11-06 16:09:59
 \documentclass[%
@@
 \begin{abstract}
-  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon.
-It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction.
+  By means of Boltzmann Transporation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene.
+It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in interlayer direction.
 Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.

### 2017-11-06 latex/run.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-21 01:41:49
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-26 18:34:07
+# @Last Modified time: 2017-11-06 17:11:43
 import os
 if not os.path.exists("bin/"):
     os.mkdir("bin")
@@ -17,3 +17,4 @@ os.system('bibtex paper')
 os.system('latex paper.tex')
 os.system('latex paper.tex')
 os.system("dvipdft paper")
+os.system("rm *.tex")

### 2017-11-15 latex/paper.tex
完成compuational detail

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-06 16:09:59
+% @Last Modified time: 2017-11-16 01:01:44
 \documentclass[%
@@
 \begin{abstract}
-  By means of Boltzmann Transporation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene.
+  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene.
 It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in interlayer direction.
@@
 The thermal conductivity of multilayer silicon structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
-In order to well simulate the structures of different phase by BTE, the latest Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
+In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
 It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA).
@@
 
-All structures are shown in FIG.\ref{fig:structures}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc.
+The model silicene structures are shown in FIG.\ref{fig:structures} which are picked from recent work of Guo et al\cite{Guo2015Structural}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc.
 ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
@@
 
-Firstly, we use conjugate gradient method to optimize these structures.  According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
+Before calculating thermal transportation properties , the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .
+Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation.
+The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\Angstrom$ which make  forces acurrate enough.
+As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
 
@@
 
-The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs.
-Both second- and third-order FCs are extracted from finite displacement method realized in Phonopy\cite{Togo2008} and Thridorder respectively.
-Both second-order and third-order  FCs are calculated with $3 \times 3 \times 1$ supercell with a $15\times 15 \times 3$ Monkhorst-Pack q-point mesh.
-The phonon group velocity  and transmision function are calculated with  with second order force constants.
-The interaction range of third-order FCs is truncated up to 4th neighbor.
-Iteration method is used instead of relaxation time approximision (RTA) to avoid underestimate of thermal concutivity.
+The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs and the detail formulas are refered to the work of  Wu Li\cite{Li2014}.
+To avoid underestimate of thermal concutivity,Iteration method is used instead of relaxation time approximision (RTA) .A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence of the summation as well as for further statistical analysics of them.
 

### 2017-11-20 latex/paper.tex
修改分析与结果

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-16 01:01:44
+% @Last Modified time: 2017-11-20 00:54:19
 \documentclass[%
@@
 \author{Yang Zhou${}^{1,3}$}
-\author{Chao-Yu Chen${}^{2}$}
 \author{Zhi-Xin Guo${}^{2}$}
@@
   By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene.
-It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in interlayer direction.
-Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.
-This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
+It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction.
+Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.
+This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
   \begin{description}
     \item[Keywords]
-          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
+          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
   \end{description}
@@
 the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
-And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicon nanowires.At present, research of thermal transport properties based on the silicon nano structure mainly includes silicon nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicon thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
-Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicon multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications.
-However, the study on the properties of multilayer silicon thermal transport is still very rare.
+And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicene nanowires.At present, research of thermal transport properties based on the silicene nano structure mainly includes silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicene thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
+Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicene multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications.
+However, the study on the properties of multilayer silicene thermal transport is still very rare.
 
@@
 The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce.
-Recently, it has been found that monolayer and multilayer silicon material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}.
+Recently, it has been found that monolayer and multilayer silicene material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}.
 The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers.
-In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicon, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.
+In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.
 The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.
@@
 Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}.
-In the case of silicon, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}.
+In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}.
 And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction.
@@
 
-In this work we use multilayer silicon as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
-And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon.
-The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension.
-In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.
-Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicon structure.
+In this work we use multilayer silicene as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.silicene  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
+And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicene.
+The study of multilayer silicene is also helpful to understand the physical evolution of matter from low dimension to high dimension.
+In addition, the preparation process of silicene nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.
+Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicene structure.
 
@@
 
-The thermal conductivity of multilayer silicon structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
-In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants.
+The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
+In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants.
 It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA).
@@
 ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
-TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicon.
+TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicene.
 
@@
   \includegraphics[width=0.48\textwidth]{images/structures}
-  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicon.
+  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene.
 Within which  are top view and side view of the studied structures.
@@
 Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation.
-The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\Angstrom$ which make  forces acurrate enough.
+The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\angstrom$ which make  forces acurrate enough.
 As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
@@
 
-Surface reconstruction affects quite a lot on the intensity and anisotropy of thermal conductivity.
-The relationship between the thermal conductivity  and the length of three kinds of bilayer silicon along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a).
-The thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh.
-In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic.
-In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials.
-And the edges of the two directions are similar in shape, leading to small difference of heat transport.
+Surface reconstruction is found to have substantial influence on the intensity and anisotropy of thermal conductivity.
+The relationship between the thermal conductivity  and the length of three kinds of bilayer silicene along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a).
+The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions.
+The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2lhex structure are around $5W/mK$.
+2l2 and 2lhex structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$.
+The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.
+The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicene.
+The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
+Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.
 
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
-  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
-The letter z/a in the legend mean the transport direction is zigzag/armchair.}
-\end{figure}
-
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tc_freq}
-  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
-\end{figure}
-
-When the length of the silicon is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious.
+The thermal conductivity converged with cutoff MFP very quickly in the curve of 2l2 while a little slower in the others.
+Besides, the cutoff MFP of 2l1 structure exhibits much difference in the two directions  which maybe due to the diffence of scattering intensity caused by the surface conditions.When the length of the silicene is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious.
 When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious.
@@
 Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials.
-Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicon
+Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicene
 \begin{equation}
@@
 
-where $\kappa_\infty$ is the fitted full scattering thermal conductance.
-$L_c$ is the transition length from the ballistic transportation to the scattering transportation.
+where $\kappa_\infty$ is the fitted full scattering thermal conductivity. $L_c$ is the transition length from the ballistic transportation to the scattering transportation.
+
+\begin{figure}[b]
+  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
+  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
+b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
+The letter z/a in the legend mean the transport direction is zigzag/armchair.}
+\end{figure}
+
+With the increase of layer number the anisotropy decreases for layer number larger than three.
+Here we study mainly on multilayer silicene structure with 3-8 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.
+From TABLE.\ref{tab:table1}, for the stuctures with more than three layers,the thermal conductivity of the multilayer silicene with zigzag type is higher than that of armchair.
+$\kappa_z$ decreases while $\kappa_a$ increases.
+The reason is that the zigzag direction of the multilayer silicene surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}).
+Compared with the bulk silicene structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow.
+While along the armchair direction, the fluctuation of multilayer silicene surface is very large, the same is its obvious affection on heat flow.
+This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicene.
+It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase.
 The value $ \chi=|\kappa_{z,\infty}-\kappa_{a,\infty} |/max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) \times 100 \%$ is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
 And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions.
+The magnitude of the anisotropy $\chi$ is also shown in TABLE.\ref{tab:table1},which  decreases obviously for these structures which is expected.
+The case of three layers is exceptional whose values are much larger than the structures with those with larger layer number and possesses a smaller anisotropy.
+This could be understood by the direct interaction beteen the top and bottom sides , and also the absence of hexatomic ring in the side view compared with 4l1 structure.A deeper analysis of this of it could be found in work of Guo \cite{Guo2015Structural}.
 
-The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table1}.
-It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure).
-In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%.
-The smallest is 2l2 and 2lh (20\%).
-The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon.
-The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.
+On the other hand, the size effect of the thermal conductivity anisotropy is obvious.
+As shown in FIG.\ref{fig:tc_length_sheng}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious.
+When the length is about 100nm, the anisotropy difference becomes very small.
+This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicene structures along different directions.
+However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
 
@@
 
-The influence of thickness change on the thermal transport properties was then investigated.
-Here we study mainly on multilayer silicon structure with 3-10 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.
-In order to compare, we also calculated the thermal conductivity of Si on its (111) surface and the thermal conductivity of the monolayer.
-The magnitude of the anisotropy is also shown in TABLE.\ref{tab:table2}.
-From the FIG.\ref{fig:vl_length}(a), in the case of the medium thickness of the 3 - 6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair.
-And with the increase of the number of layers, the anisotropy decreases gradually.
-The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}).
-Compared with the bulk silicon structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow.
-While along the armchair direction, the fluctuation of multilayer silicon surface is very large, the same is its obvious affection on heat flow.
-This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicon.
-In order to predict the relationship between the thermal conductivity and the thickness, we calculated the thermal conductivity of the 8-10 layers silicene with the $2 \times 1$ surface reconstruction.
-In order to compare, the thermal conductivity of the bulk Si (111) surface with no surface reconstruction (9 layers) and the thermal conductivity of the monolayer were calculated.
-As shown in TABLE.\ref{tab:table2}, with the increase of thickness, the anisotropy decreases gradually.
-When the thickness is up to 10 layers, the anisotropy of the thermal transport of multilayer silicon can be neglected (only about 1.5\%), which is consistent with the results of bulk silicon and single silicon.
-On the other hand, as shown in FIG.\ref{fig:vl_length}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious.
-When the length is about 100nm, the anisotropy difference becomes very small, and the size effect of the thermal conductivity anisotropy is obvious.
-This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicon structures along different directions.
-However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
-Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ ,
+For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons.
+The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2lhex have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction.
+For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction.
+Besides, the curves show much similarity for 4l1,5l1 and 6l1, suggesting a common mechanism of the anisotropy of them.
+
+To have inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.\ref{eq:kappasum}.
+
+Heat capacity has large influence between the structures but has no contribution to anisotropy.
+We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq.
+\ref{eq:cv}.
 The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$.
@@
 Large difference could be found between the $Cv$ of the structures.
-The lowest value is $10.15 kJ/m^3/K$ of 2lr while the highest value of Silicene could reach $606.4 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.
-There's no obvious trends when the layer increases but Silicene and 2l1 have pretty large value than the others and this has some relation to their low thickness.
-Almost no difference could be found in the value along zigzag direction and armchair direction, even if $\omega_{k \sigma}$ has large deviation between the direction as shown in Fig.\ref{fig:bands}.
+The lowest value is $17.26 kJ/m^3/K$ of 8l1 while the highest value of 2l1 could reach $166.7 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.
+Almost no difference could be found in the value along zigzag direction and armchair direction.
 This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high.
 That means when considering only acoustic phonons the heat capacity is close to constant.
+
+\begin{figure}[b]
+  \includegraphics[width=0.48\textwidth]{images/tc_freq}
+  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
+\end{figure}
+
+\begin{figure}[b]
+  \includegraphics[width=0.48\textwidth]{images/tau}
+  \caption{\label{fig:tau} (color online)Lifetime of phonons considering three-phonon scattering for all the structures. }
+\end{figure}
+
+The phonon lifetime
+The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures.
+We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons.
+Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
+So this process is called Umpack process( U process).
+And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
+If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance.
+The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014}.considering only the relaxation time approxmition(RTA).
+We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
+
+The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
+The values are averaged for frequency bins to reduce complexity.
+The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.
+The result is also consist with the trends of thermal conductivity.
+The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity.
+The relation between acoustic phonon lifetime and frequency could be expressed as $\tau=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
+The coefficient k for both direction are displayed in Table.3.
+The degree of divergence exhibit large anisotropy for the structures.
+However the difference of lifetime is pretty small when frequency is relatively high.
+So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.
 
@@
 The relation between the group velocity of both direction are contrast with that of the thermal conductivity, which indicate that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects.
-
-In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures.
-The $10 \times  10  \times  1$ multilayer structure is chosen.
-The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction.
-According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport.
-There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction.
-FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2.
-The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conductive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy.
-Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction.
-Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease.
-At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length.
-The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair.
-With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged.
-On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number.
-Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.
-
-The anisotropy of phonon participation ratio has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures.
-In previous work we have proven that phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}.
-Fig.\ref{fig:pr_direction} shows average phonon participation ratio for each eigenmode $k\sigma$ in various structures.
-The participation ratio of similar frequency has large difference and we select the phonons along zigzag direction and  average their participation ratio to obtain the solid black curve in Fig.\ref{fig:pr_direction} while the same is done to obtain the dash red curve for armchair direction.
-All the phonons of Silicene , 2l1 and some low frequency phonons of 2l2 exibit delocalized nature,suggesting that every phonon has been participated by all the atoms, which is due to the perfect bonding of them without dangling bonds.
-Different surface situation affects the localization a a lot.
-2l3 and 2lr3 exhibit large localization and anisotropy even for very low phonons, this is due to their unique surface where the buckling atoms form parallel lines, between them existing large distance,see Fig.\ref{fig:structures}.
-With the increasement of thickness, low frequency region remain delocalized while the participation ratio of intermediate frequency  decreases.
-For 6l1 the average participation ratio could drop down to around 0.4, and that of 8l1 even to 0.3.
-But the absolute number of atoms that participate in the mode $P_{k\sigma} \cdot N$ does not decrease and the number of transmission chanels in fact increase so thermal conductivity increase.
 
@@
 
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tau}
-  \caption{\label{fig:tau} (color online)Lifetime.}
-\end{figure}
-
-The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering.
-We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons.
-Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
-So this process is called Umpack process( U process).
-And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
-If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance.
-The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014}.considering only the relaxation time approxmition(RTA).
-We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
-
-The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
-The values are averaged for frequency bins to reduce complexity.
-The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.
-The result is also consist with the trends of thermal conductivity.
-The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity.
-The relation between acoustic phonon lifetime and frequency could be expressed as $\tau=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
-The coefficient k for both direction are displayed in Table.3.
-The degree of divergence exhibit large anisotropy for the structures.
-However the difference of lifetime is pretty small when frequency is relatively high.
-So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.
-
-The anisotropy of phonon lifetime is due to the anisotropy of anharmonic effect. To quatitily check the anharmonic effect we calculate the Gruneisen parameters with
-
-\begin{equation}
-  \gamma_{k \sigma}=- \frac{V}{\omega_{k \sigma}} \frac{\partial \omega_{k \sigma}}{\partial V}
-\end{equation}
-
-where V is the volumn of the unicell and $\omega_{k \sigma}$ is the phonon frequency.
-The shift of $\omega_{k \sigma}$ with V is due to the divirience from paraodic potential which reprensents for the harmonic situation.
-When the potenial is harmonic , all the Gruneisen parameters will vanish.
-The Gruneisen parameters of all the structures are shown in FIG.\ref{fig:gruneisen}.
-The larger the anharmonic effect the smaller the scattering lifetime of the phonons.
-The most anharmonic phonons exist in the low frequency region and consist with previous result of phonon lifetime.
-The large difference between zigzag value and armchair could explain the anisotropy of phonon scattering.
-
 To obtain a clear connection between  the surface characteristic we also statistic the force constants of different position of the structures.
@@
 
-By means of non-equilibrium molecular dynamics simulation, we found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction.
-Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure), and can be as low as 1.2 W/mK (2l2 structure) and the anisotropy can be as high as 57.3\%.
+By means of non-equilibrium molecular dynamics simulation, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction.
+Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 11.6 W/mK (2l1 structure), and can be as low as 1.2 W/mK (2l2 structure) and the anisotropy can be as high as 57.3\%.
 The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-The ultra-low thermal conductivity indicates that the bilayer silicon has good thermoelectric properties.
-In the 3-6 layer multilayer silicon with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.
+The ultra-low thermal conductivity indicates that the bilayer silicene has good thermoelectric properties.
+In the 3-6 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.
 With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased.
-The thermal conductivity anisotropy of the multilayer silicon with 10 layers is very small, which is consistent with the bulk Si and monolayer silicene.
-This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
+The thermal conductivity anisotropy of the multilayer silicene with 10 layers is very small, which is consistent with the bulk Si and monolayer silicene.
+This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
 

### 2017-11-20 latex/paper.tex
修改结果与分析与结论

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-20 00:54:19
+% @Last Modified time: 2017-11-20 20:47:21
 \documentclass[%
@@
 It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction.
-Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure.
+Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction.
+Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.
 This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
@@
 Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime.
-The heat capacity  could be computed with Eq.
-\ref{eq:cv} .
+The heat capacity  could be computed with Eq.(\ref{eq:cv}) .
 
@@
 \begin{equation}
-  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}})
+  \kappa = \kappa_\infty (1-e^{-\frac{L}{L_c}}) \label{eq:eq_nemd}
 \end{equation}
@@
   \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
-b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}.
+b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq_nemd}).
 The letter z/a in the legend mean the transport direction is zigzag/armchair.}
@@
 
-To have inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.\ref{eq:kappasum}.
+To have a deeper inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
 
 Heat capacity has large influence between the structures but has no contribution to anisotropy.
-We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq.
-\ref{eq:cv}.
+We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq.(\ref{eq:cv}).
 The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$.
@@
 Almost no difference could be found in the value along zigzag direction and armchair direction.
-This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high.
-That means when considering only acoustic phonons the heat capacity is close to constant.
+This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.
 
@@
 
-The phonon lifetime
-The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures.
-We only considering three-phonon scattering,which consist of two types of scattering process, one of them is two phonons vanish and one phonon created and the other type is one phonon transform to two phonons.
-Both of them are possible to have result phonons with q point outside Brioulls boundry, and it must be fold back to Briulls zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
+The phonon lifetimes are the main factor of anisotropy in two layer structures while they are less essential in that of structures with more than three layers.
+When calutating phonon lifetimes, only three-phonon scattering process are considered,which consists of two types of scattering processes, within one of which  two phonons vanish and one phonon be created and the other type is one phonon transform to two phonons.
+Both of them are possible to have result phonons with q point outside Brillouin boundry, which must be fold back to Brillouin zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
 So this process is called Umpack process( U process).
-And of cause there exist the situation that none of the three q points outside the Brioulls boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
-If there's no U process the thermal conductivity could be as large as possible, so this process give the dominent contribution to thermal resistance.
-The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014}.considering only the relaxation time approxmition(RTA).
+And of cause there exist  situation that none of the three q points outside the Brillouin boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
+If there's no U process the thermal conductivity could be as large as possible, so this process gives the dominent contribution to thermal resistance.
+The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014} considering only the relaxation time approxmition(RTA).
 We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
-
 The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
 The values are averaged for frequency bins to reduce complexity.
-The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation.
-The result is also consist with the trends of thermal conductivity.
-The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity.
-The relation between acoustic phonon lifetime and frequency could be expressed as $\tau=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures.
-The coefficient k for both direction are displayed in Table.3.
-The degree of divergence exhibit large anisotropy for the structures.
-However the difference of lifetime is pretty small when frequency is relatively high.
-So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.
+The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2lh has reverse relation.
+However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.
 
@@
 
-The anisotropy of phonon velocity has little contribution for the anisotropy of the thermal conductivity.
+While the anisotropy lifetime in two layer structures affects more than that of group velocity, group velocity contributes most of anisotropy in multilayer structures with layers more than three.
 FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures.
-The group velocity  along the two directions of  2 layers silicene ( include silicene) are exactly the same except for that of 2lr3 structure whose low frequency group velocities are highly anisotropic.
-Group velocity for the others are all highly anisotropic and it's obvious that the group velocity of armchair direction are all large than that of zigzag.
-The relation between the group velocity of both direction are contrast with that of the thermal conductivity, which indicate that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects.
+The group velocity  along the two directions of  2 layers silicene ( include silicene) are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic.
+Group velocity for the others exhibits similar curve and are all highly anisotropic both in low and high frequency range.
+The group velocity of zigzag direction are all large than that of zigzag.
+These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in two layer silicene but the reverse for the structures thicker.
 
@@
 
-To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.
-The transmission function can be expressed as
+Not only group velocity,but also phonon transmission clearly show that  localization of ballistic contribution from long wave phonons dominant the anisotropy of the structures with layers more than three.To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.The transmission function can be expressed as
 \begin{equation}
@@
 The more chanels means larger capability of thermal transportation.
-The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.
-
-FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
-The y-axis value of each panel is not the same so the transmission is given here only to explain the anisotropy of each strcutre.
+The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
+The y-axis value of each panel is scaled for a more convinient comparison of transmission in the tow directions.
 The steps in the curves are  characterisic of perfection of the structure.
-Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of Silicene and 2l1 are perfectly stepwise because of the perfect bonding and the absence of disorder.
-
-Similar to the situation of participation ratio, transmission of both directions of Silicene,2l1 are close.Especially that of 2l2 are exactly the same, which is due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair.
+Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of  2l1 is perfectly stepwise because of the perfect bonding and the absence of disorder.Transmission of both directions of 2l1 ,2l2(not show here) and 2lh are close,especially that of 2l2 are exactly the same due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure such as 3l1,4l1,5l1 and 6l1 where transmissioin is larger in zigzag direction than in armchair.
 This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity.
-The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this may contribute a lot to the anisotropy of the thermal transportation.
+The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this contributes a lot to the anisotropy of the thermal transportation.
 
@@
 
-By means of non-equilibrium molecular dynamics simulation, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction.
-Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 11.6 W/mK (2l1 structure), and can be as low as 1.2 W/mK (2l2 structure) and the anisotropy can be as high as 57.3\%.
+By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction.
+Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2lh structure) and the anisotropy can be as high as 41.1\%.
 The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-The ultra-low thermal conductivity indicates that the bilayer silicene has good thermoelectric properties.
-In the 3-6 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.
-With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased.
-The thermal conductivity anisotropy of the multilayer silicene with 10 layers is very small, which is consistent with the bulk Si and monolayer silicene.
+The ultra-low thermal conductivity indicates that the bilayer silicene 2lh has good thermoelectric properties.
+In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.
+With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased.
+The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function.
 This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.

### 2017-11-21 latex/paper.tex
添加各向异性随长度的变化

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-20 20:47:21
+% @Last Modified time: 2017-11-20 22:20:51
 \documentclass[%
@@
 Many theorical experiment result has shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them potential in the application of thermalelectric field where the thermalelectric figure of merit $ZT=\frac{S^2 \sigma T}{\kappa}$ could be optimized by the reduced thermal condutvitiy.
-For example
-the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
+For example the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
 And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicene nanowires.At present, research of thermal transport properties based on the silicene nano structure mainly includes silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicene thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
@@
 
-Before calculating thermal transportation properties , the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .
+Before calculating thermal transportation properties, the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .
 Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation.
@@
   \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
-b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq_nemd}).
+b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}).
 The letter z/a in the legend mean the transport direction is zigzag/armchair.}
+\end{figure}
+
+\begin{figure}[b]
+  \includegraphics[width=0.48\textwidth]{images/chi}{}
+  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
 \end{figure}
@@
 It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase.
-The value $ \chi=|\kappa_{z,\infty}-\kappa_{a,\infty} |/max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) \times 100 \%$ is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
+The value
+\begin{equation}
+  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
+\end{equation}
+
+is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
 And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions.
@@
 
-On the other hand, the size effect of the thermal conductivity anisotropy is obvious.
-As shown in FIG.\ref{fig:tc_length_sheng}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious.
-When the length is about 100nm, the anisotropy difference becomes very small.
-This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicene structures along different directions.
-However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
+On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others.
+As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$).
+When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic.
+This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process.
+However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents.
+The anisotropy in 2lhex is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.
 
@@
 
-To obtain a clear connection between  the surface characteristic we also statistic the force constants of different position of the structures.
-
 \section{CONCLUSIONS}

### 2017-11-21 src/chi.py

@@ -1,0 +1,63 @@
+# -*- coding: utf-8 -*-
+# @Author: YangZhou
+# @Date:   2017-06-14 22:16:16
+# @Last Modified by:   YangZhou
+# @Last Modified time: 2017-11-20 22:08:46
+from aces.tools import *
+from aces.graph import fig, setLegend, pl, fit
+import numpy as np
+
+from ase import io
+
+kas = []
+with fig('chi.eps', figsize=(7, 8)):
+    markers = ['s', '8', '^', 'D', '>']
+    colors = "k,r,b,purple,g,o".split(',')
+    text_style = dict(horizontalalignment='left', verticalalignment='center',
+                      fontsize=14, fontdict={'family': 'serif'})
+    fi, axes = pl.subplots(1, 1, sharex=True, figsize=(7, 4))
+    ax1 = axes
+    ks = []
+    vs = '2l1,2l2,2lhex,3l1,4l1,5l1,6l1,8l1'.split(',')
+    for i, v in enumerate(vs):
+
+        dir = "%s/0/SHENG" % v
+        if v == "2l1":
+            dir = "2l1/0/sheng.1"
+        kappa = np.loadtxt(
+            dir + '/T300K/BTE.cumulative_kappa_tensor')  # [::3]
+        # m = markers[i]
+        # c = colors[i]
+        l = kappa[:, 0]
+        atoms = io.read(v + "/0/secondorder/POSCAR")
+        nlayer = int(v.split('l')[0])
+        ss = np.linalg.norm(atoms.cell[2]) / (
+            3.34 * nlayer)
+
+        z = kappa[:, 1] * ss
+        a = kappa[:, 5] * ss
+        opts = dict(
+            # markeredgecolor='w',
+            # marker=m,
+            # color=c,
+            # markersize=1 + 2,
+            lw=2,
+            ls='-')
+        o1 = "-"
+        ka = np.abs(z - a) / np.max(np.c_[z, a], axis=1)
+        label = v
+        ax1.semilogx(l, ka, label=label, **opts)
+        ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")
+        # ax1.set_ylim([0, 15])
+        ax1.set_xlim([10, 1e5])
+        ax1.set_ylim([0, .8])
+        ax1.set_ylabel("Thermal Conductivity Anisotropy")
+        # ax1.text(-.15, 1, 'b)', transform=ax1.transAxes, **text_style)
[…]

### 2017-11-22 latex/paper.tex
将2lhex全部改为2l3;调整图像，避免label重叠;删除NEGF的部分

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-20 22:20:51
+% @Last Modified time: 2017-11-22 10:59:16
 \documentclass[%
@@
 The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions.
-The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2lhex structure are around $5W/mK$.
-2l2 and 2lhex structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$.
+The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2l3 structure are around $5W/mK$.
+2l2 and 2l3 structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$.
 The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.
@@
 However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents.
-The anisotropy in 2lhex is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.
+The anisotropy in 2l3 is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.
 
@@
       2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
-      2lh & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
+      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
       3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
@@
 For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons.
-The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2lhex have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction.
+The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2l3 have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction.
 For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction.
@@
 The values are averaged for frequency bins to reduce complexity.
-The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2lh has reverse relation.
+The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2l3 has reverse relation.
 However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.
@@
 
-\begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/transmission}
-  \caption{\label{fig:transmission} (color online)The anisotropic transmission function of the structures.
-The structure identifiers are labeled at top-left of each subplot.
-the transmission along zigzag direction is ploted as black curve while that of armchair direction is filled.
-The y range of each subplot is normalized to the max value within the graph.}
-\end{figure}
-
-Not only group velocity,but also phonon transmission clearly show that  localization of ballistic contribution from long wave phonons dominant the anisotropy of the structures with layers more than three.To quatitily study the number of transmission channels we use Non-Equalibrium Green Function (NEGF)\cite{Mingo2003} to calculate the transmission function of the struction along zigzag and armchair direction.The transmission function can be expressed as
-\begin{equation}
-  \begin{split}
-    \Theta(\omega)= Tr(
-    \mathbf{\widetilde{k}}_{a\alpha}
-    Im(\mathbf{g}_{\alpha\alpha})
-    \mathbf{\widetilde{k}}_{\alpha a}
-    \mathbf{G}_{a b}^*\\
-    \mathbf{\widetilde{k}}_{b\beta}
-    Im(\mathbf{g}_{\beta\beta})
-    \mathbf{\widetilde{k}}_{\beta b}
-    \mathbf{G}_{b a}
-    )
-  \end{split}
-\end{equation}
-where $\mathbf{\widetilde{k}}_{a\alpha}$,$\mathbf{\widetilde{k}}_{\alpha a}$ represents for the interaction between left lead and center region and its transposition,  $\mathbf{\widetilde{k}}_{b\beta}$,$\mathbf{\widetilde{k}}_{\beta b}$ the interaction between center and right lead.
-$\mathbf{g}$ and $\mathbf{G}$ the retarded Green's function of the leads and center rigion.$Tr$ and $Im$ means trace and imaginary function.
-Transmission function represents for the number of channels of a given frenquency.
-The more chanels means larger capability of thermal transportation.
-The value is substracted by the cross area of the transportation direction to eliminate the effect of lattice constants.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions.
-The y-axis value of each panel is scaled for a more convinient comparison of transmission in the tow directions.
-The steps in the curves are  characterisic of perfection of the structure.
-Defects like isotope or grain boundary could lead to disapearance of these step.The transmission of  2l1 is perfectly stepwise because of the perfect bonding and the absence of disorder.Transmission of both directions of 2l1 ,2l2(not show here) and 2lh are close,especially that of 2l2 are exactly the same due to the structure symmetry of it.The anistropy of the transmission are clearly found in other structure such as 3l1,4l1,5l1 and 6l1 where transmissioin is larger in zigzag direction than in armchair.
-This trends is quite consist with that of the thermal conducivity so transmission indeed has large effection on the difference of thermal conductivity.
-The transmission along zigzag direction has a large peak at around 5THz in the structure 3l1,3l2,4l1,5l1,6l1,8l1,while along armchair direction the peak vanish and this contributes a lot to the anisotropy of the thermal transportation.
-
 \section{CONCLUSIONS}
@@
 By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction.
-Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2lh structure) and the anisotropy can be as high as 41.1\%.
+Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2l3 structure) and the anisotropy can be as high as 41.1\%.
 The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-The ultra-low thermal conductivity indicates that the bilayer silicene 2lh has good thermoelectric properties.
+The ultra-low thermal conductivity indicates that the bilayer silicene 2l3 has good thermoelectric properties.
 In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.

### 2017-11-22 src/chi.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-20 22:08:46
+# @Last Modified time: 2017-11-22 11:11:27
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -45,6 +45,8 @@ with fig('chi.eps', figsize=(7, 8)):
             ls='-')
         o1 = "-"
         ka = np.abs(z - a) / np.max(np.c_[z, a], axis=1)
+        if v == '2lhex':
+            v = '2l3'
         label = v
         ax1.semilogx(l, ka, label=label, **opts)
         ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")

### 2017-11-22 src/gv.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-10-29 11:14:58
+# @Last Modified time: 2017-11-22 11:43:17
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
 import numpy as np
@@ -44,14 +44,18 @@ with fig('gv.eps'):
         gvs = np.abs(gvs)
         N = 40
         df = 20.0 / N
+        v1 = v
+        if v1 == '2lhex':
+            v1 = '2l3'
         x, y = binmeanx(np.c_[freqs, gvs[:, 0]], [0, 20], df)
-        ax.plot(x, y, color="k", lw=3, label=v + "z")
+        ax.plot(x, y, color="k", lw=3, label=v1 + "z")
         x, y = binmeanx(np.c_[freqs, gvs[:, 1]], [0, 20], df)
-        ax.plot(x, y, color="r", ls="--", lw=3, label=v + "a")
+        ax.plot(x, y, color="r", ls="--", lw=3, label=v1 + "a")
         # ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
         setLegend(ax, ncol=1, fontsize=10)
         # ax.set_yticks([])
-        ax.set_xlim([0, 20.1])
+        ax.set_xlim([0.05, 19.9])
+        ax.set_ylim([0.05, None])
 
     fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
     fi.text(

### 2017-11-22 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-10-29 18:25:16
+# @Last Modified time: 2017-11-22 11:40:24
 
 
 from aces.graph import fig, setLegend, pl
@@ -48,6 +48,9 @@ with fig('tau.eps'):
                 x, y = binmeanx(q, [0.0, 20.0], dx=1.5)
                 mfc = [colors[i], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
+                v1 = v
+                if v1 == '2lhex':
+                    v1 = '2l3'
                 ax.semilogy(
                     x,
                     y,
@@ -57,8 +60,15 @@ with fig('tau.eps'):
                     markeredgecolor=colors[i],
                     markerfacecolor=mfc,
                     color=colors[i],
-                    label=v + s)
-                ax.set_xlim([0, 20.55])
+                    label=v1 + s)
+                ax.axhline(
+                    y=1,
+                    xmin=0,
+                    xmax=20.55,
+                    linewidth=1,
+                    color='k',
+                    ls='--')
+                ax.set_xlim([0.01, 20.55])
                 ax.set_ylim([1e-1, 2e2])
                 setLegend(ax, fontsize=10)
     fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')

### 2017-11-22 src/tc_freq.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-10-28 15:40:24
+# @Last Modified time: 2017-11-22 11:31:23
 
 
 from aces.graph import fig, setLegend, pl
@@ -34,11 +34,14 @@ with fig('tc_freq.eps'):
                 p = np.arange(len(kappa) - 2)
                 mfc = [colors[0], 'w'][s == 'a']
                 ls = ['-', '-.'][s == 'a']
+                v1 = v
+                if v1 == '2lhex':
+                    v1 = '2l3'
                 if s == "z":
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 1] - kappa[p, 1]) / df,
-                        label=v + s, ls=ls,
+                        label=v1 + s, ls=ls,
                         marker=markers[0],
                         markersize=9,
                         markeredgecolor=colors[0],
@@ -48,15 +51,15 @@ with fig('tc_freq.eps'):
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 5] - kappa[p, 5]) / df,
-                        label=v + s, ls=ls,
+                        label=v1 + s, ls=ls,
                         marker=markers[0],
                         markersize=9,
                         markeredgecolor=colors[0],
                         markerfacecolor=mfc,
                         color=colors[0])
 
-                ax.set_xlim([0, 20.55])
-                ax.set_ylim([0, 1])
+                ax.set_xlim([0.01, 20.55])
+                ax.set_ylim([0.01, 1])
                 # ax.set_yticks([])
                 setLegend(ax, fontsize=10)
     fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')

### 2017-11-22 src/tc_length_sheng.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-10-29 19:10:10
+# @Last Modified time: 2017-11-22 11:25:20
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -62,6 +62,8 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
                     ls='.')
                 o1 = "--"
                 ka = a
+            if v == '2lhex':
+                v = '2l3'
             label = v + s
             kas.append(ka[-1])
             ax1.semilogx(l, ka, label=label, **opts)
@@ -70,7 +72,7 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
             ax1.semilogx(xx, ff(p, xx), color=c, ls=o1)
             ax1.set_ylabel("Thermal Conductivity(W/mK)")
             # ax1.set_xticks([])
-            # ax1.set_ylim([0, 11])
+            ax1.set_ylim([-3, 60])
             ax1.text(-.15, 1, 'a)', transform=ax1.transAxes, **text_style)
 
     kas = np.array(kas).reshape([2, -1])
@@ -126,7 +128,7 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
             xx = np.linspace(10, 1e4, 1000)
             ax1.semilogx(xx, ff(p, xx), color=c, ls=o1)
             ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")
-            # ax1.set_ylim([0, 15])
+            ax1.set_ylim([-2, 39])
             ax1.set_xlim([0.5, 1e5])
             ax1.set_ylabel("Thermal Conductivity(W/mK)")
             ax1.text(-.15, 1, 'b)', transform=ax1.transAxes, **text_style)

### 2017-11-22 latex/paper.tex
ntroduction 把第三段签名讨论MoS2 黑磷。。。的删掉，然后与第二段合并作为一段;Computational details 部分，第一段关于Mod potential 与LDA, GGA的比较论述删掉

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-22 10:59:16
+% @Last Modified time: 2017-11-22 12:00:25
 \documentclass[%
@@
 In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.
-The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.
-
-Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases.
-For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}.
-Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}.
-Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}.
+The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases.
 In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}.
@@
 The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
-In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants.
-It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA).
-However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants.
-For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.
+In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.
 
@@
 b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}).
-The letter z/a in the legend mean the transport direction is zigzag/armchair.}
+The letter z/a in the legend mean the transport direction is zigzag/armchair.
+The dots of 2l2a and 2l2z are almost the same so red solid dots are covered.
+}
 \end{figure}
@@
 With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased.
-The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function.
+The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity.
 This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.

### 2017-11-22 latex/paper.tex
强调4层结构的各向异性最大

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-22 12:00:25
+% @Last Modified time: 2017-11-22 14:17:59
 \documentclass[%
@@
 FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures.
-The group velocity  along the two directions of  2 layers silicene ( include silicene) are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic.
-Group velocity for the others exhibits similar curve and are all highly anisotropic both in low and high frequency range.
-The group velocity of zigzag direction are all large than that of zigzag.
-These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in two layer silicene but the reverse for the structures thicker.
+The group velocity  along the two directions of  bilayer silicenes are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic.
+Group velocity for the others exhibits similar curves and are all highly anisotropic both in low and high frequency range.
+The group velocity of zigzag direction are all larger than that of zigzag.These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in bilayer silicene but it's mainly from group velocity difference of the two directions in 3-6 layer silicenes.
+There's not much anisotropy in phonon lifetime in 3,5,6 layer structures but the structure with 4 layers has its anisotropy from both phonon lifetime and group velocity which lead to a largest anisotropy up to 69.98\%
 

### 2017-12-02 latex/run_pre.py
组会20171202pre

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-21 01:41:49
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-06-26 19:27:33
+# @Last Modified time: 2017-12-02 11:28:15
 import os
 if not os.path.exists("bin/"):
     os.mkdir("bin")
@@ -14,8 +14,6 @@ os.system("cp ../ref.bib .")
 os.system("cp ../../src/*.eps images/")
 os.system("cp ../*.tex .")
 os.system('xelatex presentation.tex')
-# os.system('xelatex presentation.tex')
-# os.system('bibtex presentation')
-# os.system('latex ../presentation.tex')
-# os.system('latex ../presentation.tex')
-# os.system("dvipdft presentation")
+os.system('bibtex presentation')
+os.system('xelatex ../presentation.tex')
+os.system("rm *.tex *.aux *.bbl *.blg *.dvi *.log *.bib *.out")

### 2017-12-07 latex/paper.tex
合并郭志新的修改结果

--- 2017-11-22 latex/paper.tex
@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-22 12:00:25
-\documentclass[%
- reprint,
- amsmath,amssymb,
- aps,
- prb,
-]{revtex4-1}
+% @Last Modified time: 2017-11-22 14:17:59
+
+\documentclass[aps,prb,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}
+
 \preprint{APS/123-QED}
+
 \usepackage{graphicx}% Include figure filesxx
 \usepackage{bm}% bold math
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+
+\usepackage{multirow}
+\usepackage{epsfig}
+\usepackage{amssymb}
+
 \newcommand{\angstrom}{\mbox{\normalfont\AA}}
+
 \begin{document}
+
 \title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
 \author{Yang Zhou${}^{1,3}$}
-\author{Zhi-Xin Guo${}^{2}$}
+\author{Zhi-Xin Guo${}^{2,1}$}
 \email{zxguo08@hotmail.com}
@@
 \begin{abstract}
-  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene.
-It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction.
-Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction.
-Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.
-This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
+The silicon materials present complex surface reconstructions, which are usually neglected for the thermal conductivity investigations due to their small specific surface area.
+However, the reconstruction effect can be significant when the material thickness becomes ultra thin, i.
+e., multilayer silicene.
+Here we systematically study the thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.
+We find that the thermal conductivity of multilayer silicene present significant surface-structure dependence.
+The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures.
+We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the flour-layer  $2\times1$ silicene.
+The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
+Finally, we find that both the phonon-lifetime  anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy for the multilayer silicene.
+This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface constructions in the future.
+
   \begin{description}
@@
 
-Many theorical experiment result has shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them potential in the application of thermalelectric field where the thermalelectric figure of merit $ZT=\frac{S^2 \sigma T}{\kappa}$ could be optimized by the reduced thermal condutvitiy.
-For example the experiment of Boukai et.al.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values representing an approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
-And Hochbaum et.al.\cite{Hochbaum2008} proposed a way of enchancing thermalelectric effieciency by control the roughness of silicene nanowires.At present, research of thermal transport properties based on the silicene nano structure mainly includes silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008}, silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014}, substrate supported silicene\cite{Wang2015,Zhang2015a}, silicene thin film and bulk structure\cite{Bodapati2006,Tang2013Thermal,Jeong2012Thermal,Liu2006Thermal,Wang2006Lattice}.
-Due to the quantum size effect in the thickness direction and surface reconstruction effect, silicene multilayer structure is expected to have lower thermal conductivity than the bulk and is more suitable for thermoelectric applications.
-However, the study on the properties of multilayer silicene thermal transport is still very rare.
+Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics.
+For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
+Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires.
+At present, the thermal conductivity of the silicon nanostructures, i.
+e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a} \textbf{Add, J.
+Phys.: Condensed Matter 28, 145003 (2016)} had been well studied.
+However, the thermal conductivity of multilayer silicene is still mysterious.
+The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications.
+Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.
 
-The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction.
-There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure.
-The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce.
-Recently, it has been found that monolayer and multilayer silicene material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}.
-The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers.
-In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials.
-The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases.
-In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}.
-And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction.
-This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.
+The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.
+Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
+The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation\cite{}\textbf{ [add more refs on mutilayer silicene, such as Appl.
+Phys.
+Lett.
+102, 163106 (2013); Appl.
+Phys.
+Lett.
+104, 131904 (2014),Guo2015Structural}.
+Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties ( \textbf{ Ref.
+Appl.
+Phys.
+Lett.
+104, 131904 (2014), Guo2015Structural}.
+Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.
+Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.
 
-In this work we use multilayer silicene as a group of  ideal model systems to explore the effects of layer number and  surface reconstruction charateristics on the intensity and anisotrope of the 2D dimentional materials.silicene  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment.
-And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicene.
-The study of multilayer silicene is also helpful to understand the physical evolution of matter from low dimension to high dimension.
-In addition, the preparation process of silicene nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.
-Based on the first principles calculation of Guo\cite{Guo2015Structural}, we explored the thermal transport properties of the 2 to 10 layer silicene structure.
+In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-10 atomic layers) and surface reconstructions in use of  the BTE method.
+We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).
+This feature shows that the  multilayer silicene is an ideal candidate in the thermoelectrics.
 
@@
 
-The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}.
-In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.
+The thermal conductivity of multilayer silicene structures are studied with the BTE method realized in ShengBTE\cite{Li2014}.
+In order to save the computing expense, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}.
+This potential is able to reconstruct the silicene material elastic constants, the melting point and phase transition.
+The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller binding energy than that predicted by the first principle method.
 
-The model silicene structures are shown in FIG.\ref{fig:structures} which are picked from recent work of Guo et al\cite{Guo2015Structural}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc.
-) and s indicates the type along the length direction with value of a (armchair) or z (zigzag).
-TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicene.
+The atomic models for multilayer silicene are shown in FIG.\ref{fig:structures}, which are adoped from recent work of Guo \emph{et al}\cite{Guo2015Structural}.
+For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" represents layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
+) and "s" indicates the type along the length direction which is a (armchair) or z (zigzag).
+We show in TABLE.\ref{tab:table1} the structure names and  the minimum repeat cell periodicities of the multilayer silicene.
 
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/structures}
+  \includegraphics[angle= 0, width=0.95\linewidth]{structures.eps}
   \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene.
@@
 
-Before calculating thermal transportation properties, the  structures are  optimized with  conjugate gradient (CG) method which guarantee the stability of them .
-Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract second- and third-order force constants (FCs) in which hundreds of  slightly displaced supercells are generated and their forces are calculated with LAMMPS and used to calculate the FCs with  numerical differential calculation.
-The chosen supercells is $3 \times 3 \times 1$ of premitive cells to make the inplane dimension above  $40\angstrom$ which make  forces acurrate enough.
-As for the out-of-plane dimension, according to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.
+Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.
+Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated.
+The obtained forces are calculated and used to calculate the FCs with numerical differential calculation.
+The chosen supercells are $3 \times 3 \times 1$ of premitive cells to make the in-plane dimension above 40 \angstrom, which ensures  the accuracy of calculated forces.
+Following to previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
 
-The thermal conductivity tensor could be calculated with
+The thermal conductivity tensor can be calculated as
 
@@
 
-Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime.
-The heat capacity  could be computed with Eq.(\ref{eq:cv}) .
+where $c_{k \sigma}$ means the heat capacity of phonon mode,  $v_{k \sigma}^{\alpha}$ represents the mode group velocity, and $\tau_{k \sigma}$ is the phonon lifetime.
+The heat capacity is calculated with Eq.(\ref{eq:cv})
 
@@
 
-Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
+where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
 
-The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs and the detail formulas are refered to the work of  Wu Li\cite{Li2014}.
-To avoid underestimate of thermal concutivity,Iteration method is used instead of relaxation time approximision (RTA) .A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence of the summation as well as for further statistical analysics of them.
+The calculations of $c_{k\sigma}$ , $v_{k \sigma}^{\alpha}$, and $\tau_{k\sigma}$ require the second- and third-order force constants (FCs) as inputs, where the detailed formulas are referred to the work of  Li \cite{Li2014}.
+To avoid underestimation of thermal conductivity, iteration method is used instead of relaxation time approximation (RTA).
+A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence on the summation, as well as for their further statistical analytics.
 
@@
 
-Surface reconstruction is found to have substantial influence on the intensity and anisotropy of thermal conductivity.
-The relationship between the thermal conductivity  and the length of three kinds of bilayer silicene along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a).
-The absolute value of the thermal conductivity shows a large gap between these different surface reconstructions.
-The thermal conductivity of 2l1 structure reaches up to $42.1W/mK$ and $57.9W/mK$ in the zigzag and armchair directions respectively , while those of 2l2 structure are about $31.1W/mK$ in both direction and those of 2l3 structure are around $5W/mK$.
-2l2 and 2l3 structures both show large anisotropy while 2l2 does not because 2l2 structure exhibits excellent rotation symmetry of $\frac{\pi}{2}$.
-The thermal conductivity and anisotropy of multilayer silicene is shown in TABLE.\ref{tab:table1}.
-The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicene.
-The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.
+We first show that the surface reconstruction has substantial influence on thermal conductivity of the multilayer silicene. 
+FIG.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three bilayer silicene structures. 
+As one can see, thermal conductivity converges with cutoff phonon mean free path (MFP) very quickly in of 2l2  structure, while a little slower in the others.
+Moreover, the cutoff MFPs of 2l1 structure are very different in the armchair and zigzag directions.
+These features can be attributed to the different scattering intensity caused by the surface reconstructions.
+It is known that the ballistic phonon transport is dominating  when a material length the is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when a material length is larger than the MFP.
+An empirical formula had been proposed by John A.
+Thomas\cite{Thomas2010}  to characterize the thermal conductivity of the phonon transport from ballistic to diffuse region, and accurately estimate thermal conductivity of the infinite long nanomaterials
 
-The thermal conductivity converged with cutoff MFP very quickly in the curve of 2l2 while a little slower in the others.
-Besides, the cutoff MFP of 2l1 structure exhibits much difference in the two directions  which maybe due to the diffence of scattering intensity caused by the surface conditions.When the length of the silicene is smaller than the mean free path of the phonon, the ballistic transport properties of the phonon are obvious.
-When the length is larger than the mean free path of the phonon, the phonon scattering transport characteristics are obvious.
-The empirical formula of the John A.
-Thomas\cite{Thomas2010} can be used to characterize the thermal conductivity of the phonon transport from ballistic to scattering region, at the same time accurately obtaining thermal conductivity of the infinite long nano materials.
-Using this formula, we obtain the thermal conductivity of infinitely long multilayer silicene
 \begin{equation}
@@
 
-where $\kappa_\infty$ is the fitted full scattering thermal conductivity. $L_c$ is the transition length from the ballistic transportation to the scattering transportation.
+where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation.
+Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by this  formula.
+The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK in zigzag (armchair) direction, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, confirming the significant influence of surface reconstruction on thermal conductivity.
+
+The surface reconstruction also induces the thermal conductivity anisotropy, which can be estimated using 
+\begin{equation}
+  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
+\end{equation}
+where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction. 
+It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.
+The ultra low and perticularly high anisotropy of thermal conductivity of bilayer silicene indicate its great potential applications in the thermoelectrics.
 
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
+ \includegraphics[angle= 0, width=0.9\linewidth]{tc_length_sheng.eps}
   \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
@@
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/chi}{}
+  \includegraphics[angle= 0, width=0.9\linewidth]{chi.eps}{}
   \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
@@
 
-With the increase of layer number the anisotropy decreases for layer number larger than three.
-Here we study mainly on multilayer silicene structure with 3-8 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction.
-From TABLE.\ref{tab:table1}, for the stuctures with more than three layers,the thermal conductivity of the multilayer silicene with zigzag type is higher than that of armchair.
-$\kappa_z$ decreases while $\kappa_a$ increases.
-The reason is that the zigzag direction of the multilayer silicene surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}).
-Compared with the bulk silicene structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow.
-While along the armchair direction, the fluctuation of multilayer silicene surface is very large, the same is its obvious affection on heat flow.
-This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicene.
-It's expected that when the layer number reaches infinity the value of them collapse because we finally obtain the bulk phase.
-The value
-\begin{equation}
-  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
-\end{equation}
+We then discuss the thickness dependence of the thermal conductivity anisotropy.
+Here we mainly focus on the multilayer silicene with 3-8 atomic layers, whose surface presents the typical $2 \times 1$ Si(111) reconstruction.
+A common feature is that the thermal conductivity in the zigzag direction ($\kappa_z$) is obviously  higher than that  in armchair ($\kappa_a$) direction, which induces anisotropy larger than 55\%.
+The reason is that the zigzag direction of surface is composed of smooth zigzag atomic chains (as shown in FIG.\ref{fig:structures}), which are favorable for the heat transport.
+Whereas,  there are large geometry fluctuations in the armchair direction of the surface, which are unfavorable for the heat transport.
+With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on  thermal conductivity anisotropy.
+The negative  effect  is attributed to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing.
+%This feature partially explains why the thermal conductivity  is almost isotropic in bulk Si, which usually has complex surface reconstructions. 
+One exception is for the trilayer silicene, which has the largest thermal conductivity  but the smallest  anisotropy, compared to the thicker  $2\times1$ structures.
+This could be understood by the direct interaction between the top and bottom layers, as well as the absence of ideal honeycomb ring under the surface layers, which is different from the thicker $2\times 1$ structures\cite{Guo2015Structural}.
 
-is used to measure the thermal conductivity difference in different directions, where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
-And is $ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) $ the maximum value of thermal conductivity in the two directions.
-The magnitude of the anisotropy $\chi$ is also shown in TABLE.\ref{tab:table1},which  decreases obviously for these structures which is expected.
-The case of three layers is exceptional whose values are much larger than the structures with those with larger layer number and possesses a smaller anisotropy.
-This could be understood by the direct interaction beteen the top and bottom sides , and also the absence of hexatomic ring in the side view compared with 4l1 structure.A deeper analysis of this of it could be found in work of Guo \cite{Guo2015Structural}.
-
-On the other hand, the size effect of the thermal conductivity anisotropy is obvious in 2l1 but not in the others.
-As shown in FIG.\ref{fig:chi}, thermal conductivity in 2l1 is almost isotropic  in the case of short length (10 - 1000 $\angstrom$).
-When the length is above 1000  $\angstrom$), thermal conductivity become inceasingly anisotropic.
-This is essentially due to the difference acoustic branch along different directions whose mean free path are rather large, which is caused by phonon scattering of umklapp process.
-However, for 3-8 layer structures, thermal conductivity is highly even in the short free path region which indicates anistropy in both low and high frequency range and this could  be verified in the following contents.
-The anisotropy in 2l3 is somelike the mixture of both mechanism but has also a pretty large contribution from long path phonons.
+We also investigated the size effect on the thermal conductivity anisotropy.
+As shown in FIG.\ref{fig:chi}, thermal conductivity of  2l1 bilayer silicene is almost isotropic  with length being 10-1000 \angstrom, and it becomes increasingly anisotropic with the length increasing  above 1000  \angstrom.
+This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.
+As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly attributed to the optical phonons.
+On the other hand, the thermal conductivity anisotropy of 2l3 silicene can be owning to both acoustic and  optical phonons in different directions.
 
@@
   \caption{\label{tab:table1}
-    The thermal conductivity and anisotropic ratio of different multi-layer silicene.Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.}
+    The thermal conductivity and anisotropic ratio of different multi-layer silicene.
+Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.
+$Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively.
+}
   \begin{ruledtabular}
@@
 
-For the structures of two layers the anisotropy mainly comes from low frequency phonons while that of layer number more than fore are contributed from high frequency phonons.
-The frequency distribution of thermal conductivity is shown in Fig.\ref{fig:tc_freq} and it's obvious that both 2l1 and 2l3 have much larger value in the low frequency part of armchair direction and they are the only two structures with thermal conductivity of armchair direction larger than that of zigzag direction.
-For the other structures except 3l1, the low frequency region exhibits little anisotropy while the high frequency thermal condcutivity of zigzag contribution is larger than that of armchair direction.
-Besides, the curves show much similarity for 4l1,5l1 and 6l1, suggesting a common mechanism of the anisotropy of them.
+To explore the origin of anisotropy, we have calculated the frequency distribution of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
+It is found that the  anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i.
+e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that of zigzag direction.
+Whereas, for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivity in armchair and zigzag directions is nearly the same in the low-frequency region, and the anisotropy is mainly  attributed to the high-frequency (5-20 THz) phonons.
+In addition, the anisotropy of the 3l1 structure is resulted by the  phonons with frequency in range of 10-20 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
 
-To have a deeper inside into the origin of anisotropy for all the structures it's helpful to study all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
-
-Heat capacity has large influence between the structures but has no contribution to anisotropy.
-We select all the phonons along  $\Gamma\rightarrow X$ and along $\Gamma \rightarrow Y$ and cacluate their heat capacity with Eq.(\ref{eq:cv}).
-The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$.
-The average heat capacity of the structures are shown in Table.\ref{tab:table1} .
-Large difference could be found between the $Cv$ of the structures.
-The lowest value is $17.26 kJ/m^3/K$ of 8l1 while the highest value of 2l1 could reach $166.7 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity.
-Almost no difference could be found in the value along zigzag direction and armchair direction.
-This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.
+To have a deep inside into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
+We selected all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in BZ, and calculated their heat capacity with Eq.(\ref{eq:cv}).
+The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively.
+As one can see, $Cv_z$ and $Cv_a$  strongly depend on the reconstruction-structure and thicknes of multilayer silicene, but their difference in the same structure is very small.
+This result shows that the thermal conductivity anisotropy is insensitive to the heat capacity.
+%This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.
 
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tc_freq}
+  \includegraphics[width=0.9\linewidth]{tc_freq.eps}
   \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
@@
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/tau}
-  \caption{\label{fig:tau} (color online)Lifetime of phonons considering three-phonon scattering for all the structures. }
+  \includegraphics[width=0.9\linewidth]{tau.eps}
+  \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
 \end{figure}
 
-The phonon lifetimes are the main factor of anisotropy in two layer structures while they are less essential in that of structures with more than three layers.
-When calutating phonon lifetimes, only three-phonon scattering process are considered,which consists of two types of scattering processes, within one of which  two phonons vanish and one phonon be created and the other type is one phonon transform to two phonons.
-Both of them are possible to have result phonons with q point outside Brillouin boundry, which must be fold back to Brillouin zone to make the result physcical( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}+\mathbf{G}$).
-So this process is called Umpack process( U process).
-And of cause there exist  situation that none of the three q points outside the Brillouin boundry, and the summation of the momentum conserves ( $\mathbf{q''}=\mathbf{q} \pm \mathbf{q'}$), which is called Normal process (N process) or momentum conservation process.
-If there's no U process the thermal conductivity could be as large as possible, so this process gives the dominent contribution to thermal resistance.
-The phonon scattering rate could be obtained by Fermi-golden rule\cite{Li2014} considering only the relaxation time approxmition(RTA).
-We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.
-The phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}.
-The values are averaged for frequency bins to reduce complexity.
-The lifetime of 3l1,4l1,5l1,6l1 along zigzag direction is larger than armchair direction while that of 2l1,2l3 has reverse relation.
-However the anitropy of lifetime  is quite obvious in two layers structures , where lifetime of armchair direction is larger almost through all the frequency, while there's not much anisotropy in multilayer structures expcet in the 4THz-7THz range of 4l1 structure.
+We then explore the contributions from the phonon lifetimes for the anisotropy.
+We considered the three-phonon scattering process, where the phonon scattering rate could be obtained by the Fermi-golden rule\cite{Li2014} considering only the relaxation time approximation (RTA).
+The the iterative method was then used to include the cross influence of the phonon excitation, witch usually gives lager but more accurate lifetimes than the RTA.
+The frequency dependence of phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.
+It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity.
+Moreover, the lifetime in armchair direction is obviously larger than that in zigzag direction in the low-frequency region.
+This feature inidcates that the anisotropy in bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
+On the other hand, the phonon lifetimes exhibit different frequency distributions in the thicker silicene, i.
+e.,  $2\times1$ structure with 3-6 Si layers, which cover both the low and high frequency regions with lifetimes  larger than 1 ps.
+This is explains the high frequency phonons contribute significantly to the thermal conductivity in these structures (Fig.
+4).
+Except for the 4l1 structure, the lifetime distributions in zigzag and armchair directions are very similar for these  $2\times1$ structures, showing the tiny effect of phonon lifetimes on the anisotropy.
 
 \begin{figure}[b]
-  \includegraphics[width=0.48\textwidth]{images/gv}{}
+  \includegraphics[width=0.9\linewidth]{gv.eps}{}
   \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
@@
 
-While the anisotropy lifetime in two layer structures affects more than that of group velocity, group velocity contributes most of anisotropy in multilayer structures with layers more than three.
-FIG.\ref{fig:gv} showes the group velocity along both zigzag and armchair direction for all the structures.
-The group velocity  along the two directions of  2 layers silicene ( include silicene) are basicly the same except for the frequency range of 12THz - 15THz in 2l1 structure whose  group velocities are highly anisotropic.
-Group velocity for the others exhibits similar curve and are all highly anisotropic both in low and high frequency range.
-The group velocity of zigzag direction are all large than that of zigzag.
-These results  show that the main effect of anistropy is not from group velocity but the scatter rate origin from anharmonic effects in two layer silicene but the reverse for the structures thicker.
+To further explore the origin of thermal conductivity anisotropy in multilayer  silicene, we have calculated the frequency dependence of phonon group velocities.
+As shown in Fig.
+6,  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
+As for the $2\times 1$ silicene with thickness more than layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region.
+Combined with the fact that the lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the anisotropy of $2\times 1$ silicene structures.
+It should be noted that the anisotropy of 4l1 structure is from contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
 
 \section{CONCLUSIONS}
-
-By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction.
-Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2l3 structure) and the anisotropy can be as high as 41.1\%.
-The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction.
-The ultra-low thermal conductivity indicates that the bilayer silicene 2l3 has good thermoelectric properties.
-In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive.
-With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased.
-The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity.
-This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
+By means of Boltzmann Transporation Equation methods, we have investigated thermal conductivity of multilayer silicene with various surface structures and thickness.
+We found that the surface reconstruction has significant effect on thermal conductivity.
+The smooth surface is favorable for heat conduction, while the rough surface greatly suppresses the heat conduction.
+Both ultra low (3.3 W/mK) and relatively high (57.9 W/mK) thermal conductivities have been obtained on bilayer silicene with different surface structures, which also induce large anisotropy of 41\% and 27\%, respectively.
+We also found that the $2 \times 1$  surface reconstruction induces the unusual large thermal conductivity anisotropy of 70\%  in the quadlayer silicene.
+Moreover, we found that increasing silicene thickness, which has an effect of weakening the surface contribution to the thermal transport,  reduces the anisotropy.
+Finally, we clarify that the anisotropy of phonon lifetimes and phonon group velocities is the mainly contributes to   the thermal conductivity anisotropy for the bilayer and thicker $2\times 1$ silicene structures, respectively.
+Our results indicate that silicene structures with thickness of 2-4 layers present the most  exotic physical  properties, which may be a common feature for the 2D materials with strong interlayer interactions.
+This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials in the future.
 

### 2017-12-07 latex/paper.tex
添加郭志新提出的refrence

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-11-22 14:17:59
+% @Last Modified time: 2017-12-07 14:28:22
 
@@
 At present, the thermal conductivity of the silicon nanostructures, i.
-e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a} \textbf{Add, J.
-Phys.: Condensed Matter 28, 145003 (2016)} had been well studied.
+e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied.
 However, the thermal conductivity of multilayer silicene is still mysterious.
@@
 Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
-The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation\cite{}\textbf{ [add more refs on mutilayer silicene, such as Appl.
-Phys.
-Lett.
-102, 163106 (2013); Appl.
-Phys.
-Lett.
-104, 131904 (2014),Guo2015Structural}.
-Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties ( \textbf{ Ref.
-Appl.
-Phys.
-Lett.
-104, 131904 (2014), Guo2015Structural}.
+The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation
+\cite{Fu2014,Padova2016,Guo2015Structural}.
+Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}.
 Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.

### 2017-12-13 latex/paper.tex
按照郭志新的意见修改

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-12-07 14:28:22
+% @Last Modified time: 2017-12-13 15:17:11
 
@@
 The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures.
-We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the flour-layer  $2\times1$ silicene.
+We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the four-layer  $2\times1$ silicene.
 The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
@@
 The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications.
-Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.
+Since the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.
 
@@
 Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
-The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation
-\cite{Fu2014,Padova2016,Guo2015Structural}.
+The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
 Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}.
 Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.
-Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.
+Both experiments and theory suggests surface reconstruction in 2D materials may induce large anisotropy, for example, BP and phosphorene exhibit distinct orthogonal electrical and thermal transport anisotropies arising from their puckered structure \cite{Zhang2015,Peng2015}.
+While the anisotropic electrical properties influence the device performance, the anisotropic thermal transport properties are closely relevant to the thermomechanical reliability of functional devices fabricated from these materials.
+In particular, alternative flexible substrate and active layer materials with increased thermal conductivity are needed to prevent thermomechanical failures that have become an important challenge in flexible devices based on 2D materials\cite{Akinwande2014,Sadeghi2016}.
+Without doult, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  could promote the applications of covalently bonded 2D materials in the thermoelectrics.
 
-In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-10 atomic layers) and surface reconstructions in use of  the BTE method.
+In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-8 atomic layers) and surface reconstructions in use of  the BTE method.
 We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).
@@
 \begin{figure}[b]
-  \includegraphics[angle= 0, width=0.95\linewidth]{structures.eps}
+  \includegraphics[angle= 0, width=0.95\linewidth]{images/structures.eps}
   \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene.
@@
 The greens represent those that are inside the structure.
-The orientation of top view of the cells is labeled as arrows.}
+The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.}
 \end{figure}
@@
 Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.
-Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated.
+Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated.
 The obtained forces are calculated and used to calculate the FCs with numerical differential calculation.
@@
 \begin{figure}[b]
-  \includegraphics[angle= 0, width=0.9\linewidth]{tc_length_sheng.eps}
+  \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
   \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
@@
 \begin{figure}[b]
-  \includegraphics[angle= 0, width=0.9\linewidth]{chi.eps}{}
+  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
   \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
@@
 \begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{tc_freq.eps}
+  \includegraphics[width=0.9\linewidth]{images/tc_freq.eps}
   \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
@@
 \begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{tau.eps}
+  \includegraphics[width=0.9\linewidth]{images/tau.eps}
   \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
@@
 This is explains the high frequency phonons contribute significantly to the thermal conductivity in these structures (Fig.
-4).
+\ref{fig:tc_freq}).
 Except for the 4l1 structure, the lifetime distributions in zigzag and armchair directions are very similar for these  $2\times1$ structures, showing the tiny effect of phonon lifetimes on the anisotropy.
@@
 \begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{gv.eps}{}
+  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
   \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
@@
 As shown in Fig.
-6,  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
+\ref{fig:gv},  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
 As for the $2\times 1$ silicene with thickness more than layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region.
@@
 
-\quad \\
-\section{ACKNOWLEGEMENTS}
+\section{ACKNOWLEDGEMENTS}
 This paper was partially supported by the National Natural Science Foundation of China, the Special Funds for Major State Basic Research, the Foundation for the Author of National Excellent Doctoral Dissertation of China, the Program for Professor of Special Appointment at Shanghai Institutions of Higher Learning, and the Research Program of Shanghai Municipality and the Ministry of Education.

### 2017-12-13 src/chi.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-22 11:11:27
+# @Last Modified time: 2017-12-07 14:42:03
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -12,7 +12,8 @@ from ase import io
 kas = []
 with fig('chi.eps', figsize=(7, 8)):
     markers = ['s', '8', '^', 'D', '>']
-    colors = "k,r,b,purple,g,o".split(',')
+    colors = "firebrick,r,b,k,g,hotpink,orange,r".split(
+        ',')
     text_style = dict(horizontalalignment='left', verticalalignment='center',
                       fontsize=14, fontdict={'family': 'serif'})
     fi, axes = pl.subplots(1, 1, sharex=True, figsize=(7, 4))
@@ -27,7 +28,7 @@ with fig('chi.eps', figsize=(7, 8)):
         kappa = np.loadtxt(
             dir + '/T300K/BTE.cumulative_kappa_tensor')  # [::3]
         # m = markers[i]
-        # c = colors[i]
+        c = colors[i]
         l = kappa[:, 0]
         atoms = io.read(v + "/0/secondorder/POSCAR")
         nlayer = int(v.split('l')[0])
@@ -39,12 +40,12 @@ with fig('chi.eps', figsize=(7, 8)):
         opts = dict(
             # markeredgecolor='w',
             # marker=m,
-            # color=c,
+            color=c,
             # markersize=1 + 2,
             lw=2,
             ls='-')
         o1 = "-"
-        ka = np.abs(z - a) / np.max(np.c_[z, a], axis=1)
+        ka = np.abs(z - a) / np.max(np.c_[z, a], axis=1) * 100
         if v == '2lhex':
             v = '2l3'
         label = v
@@ -52,8 +53,8 @@ with fig('chi.eps', figsize=(7, 8)):
         ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")
         # ax1.set_ylim([0, 15])
         ax1.set_xlim([10, 1e5])
-        ax1.set_ylim([0, .8])
-        ax1.set_ylabel("Thermal Conductivity Anisotropy")
+        ax1.set_ylim([0, .8 * 100])
[…]

### 2017-12-16 latex/paper.tex
merge guo's modification at 20171216

@@
 \begin{abstract}
-  The silicon materials present complex surface reconstructions, which are usually neglected for the thermal conductivity investigations due to their small specific surface area.
-However, the reconstruction effect can be significant when the material thickness becomes ultra thin, i.
+  The silicon materials present complex surface reconstructions, which are usually neglected for thermal conductivity investigations due to their small specific surface area.
+However, the reconstruction effect can be significant when a material's thickness becomes ultra thin, i.
 e., multilayer silicene.
-Here we systematically study the thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.
-We find that the thermal conductivity of multilayer silicene present significant surface-structure dependence.
-The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures.
-We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the four-layer  $2\times1$ silicene.
-The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
-  Finally, we find that both the phonon-lifetime  anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy for the multilayer silicene.
-  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface constructions in the future.
+Here we systematically study thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.
+We find that their thermal conductivity strongly depends on the surface structures.
+Thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK with different surface structures.
+Also, the $2\times1$ surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  in a four-layer silicene.
+We also find that the anisotropy decreases with silicene thickness increasing, owing to the significant reduction of thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
+ Finally, we find that both the phonon-lifetime anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy of multilayer silicene.
+These findings could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface reconstructions in the future.
 
@@
 
-Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics.
-For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range.
-Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires.
-At present, the thermal conductivity of the silicon nanostructures, i.
-e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied.
-However, the thermal conductivity of multilayer silicene is still mysterious.
-The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications.
-Since the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.
+Many theoretical and experimental results showed that the quantum confinement and surface effects can remarkably reduce the thermal conductivity of nanomaterials while remaining their electronic conductivity at high level, which make them great potential applications in the thermoelectrics[Adv.
+Mater.
+2007, 19, 1043–1053; Int.
+Mater.
+Rev.
+48, 45 (2003)].
+For example,  Boukai \emph{et al}.\cite{Boukai2008} found that by varying the nanowire size and impurity doping levels,  approximately 100-fold improvement of  ZT over bulk Si can be achieved in a broad temperature range.
+Also, Hochbaum \emph{et al}.\cite{Hochbaum2008}  proposed a way of increasing ZT via controlling the roughness of silicene nanowires.
+As far as we know,  thermal conductivity of silicon nanostructures, i.
+e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied, while it is still mysterious for multilayer silicene.
+The combined effects of quantum size and surface reconstruction in multilayer silicene are expected to induce exotic thermal transport properties different from either monolayer silicene or bulk Si,  which may make it suitable for the thermoelectric applications.
+Since thermal conductivity of monolayer silicene and bulk Si had been well explored, the investigation on multilayer silicene is helpful for understanding thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.
 
-The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.
-Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
-The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
-Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}.
-Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.
-Both experiments and theory suggests surface reconstruction in 2D materials may induce large anisotropy, for example, BP and phosphorene exhibit distinct orthogonal electrical and thermal transport anisotropies arising from their puckered structure \cite{Zhang2015,Peng2015}.
-While the anisotropic electrical properties influence the device performance, the anisotropic thermal transport properties are closely relevant to the thermomechanical reliability of functional devices fabricated from these materials.
-In particular, alternative flexible substrate and active layer materials with increased thermal conductivity are needed to prevent thermomechanical failures that have become an important challenge in flexible devices based on 2D materials\cite{Akinwande2014,Sadeghi2016}.
-Without doult, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  could promote the applications of covalently bonded 2D materials in the thermoelectrics.
+The existing researches on thermal conductivity of  2D materials  mainly focus on the ones with weak van der Waals (vdW) interlayer interactions where  no surface reconstruction appears.
+The multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015} are such kind of 2D materials which had been well studied.
+Whereas, the thermal conductivity of 2D materials with strong interlayer interactions is barely explored so far.
+The multilayer silicene, which has been both theoretically predicted and experimentally synthesized, can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
+Previous studies showed that mutilayer silicene exhibits special surface reconstructions which induce the intriguing electronic property\cite{Fu2014,Guo2015Structural}.
+Naturally, one also expects the surface reconstruction to play a key role in its thermal transport property.
 
-In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-8 atomic layers) and surface reconstructions in use of  the BTE method.
-We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).
-This feature shows that the  multilayer silicene is an ideal candidate in the thermoelectrics.
+On the other hand, both experimental and theoretical studies showed that surface reconstruction in 2D materials can induce large anisotropy.
+For example, black phosphorus and phosphorene exhibit distinct thermal transport anisotropy owning to their puckered structures\cite{Zhang2015,Peng2015}.
+The thermal transport anisotropy is closely relevant to the thermomechanical reliability of functional devices in nanoelectronics.
+In particular, alternative flexible substrate and active layer materials with increased thermal conductivity are  desirable  to prevent thermomechanical failures which have become a big challenge in flexible devices based on 2D materials\cite{Akinwande2014,Sadeghi2016}.
+Revealing the surface reconstruction effect on thermal conductivity anisotropy of mutilayer silicene could stimulate the studies of covalently bonded 2D materials for the potential applications in the nanoelectronics.
+
+In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various surface reconstructions and thicknesses  (2-8 atomic layers) in use of  the BTE method.
+We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce either ultra-low thermal conductivity ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).
+This feature shows that multilayer silicene can be ideal candidates in thermoelectrics and nanoelectronics.
 
@@
 The thermal conductivity of multilayer silicene structures are studied with the BTE method realized in ShengBTE\cite{Li2014}.
-In order to save the computing expense, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}.
-This potential is able to reconstruct the silicene material elastic constants, the melting point and phase transition.
-The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller binding energy than that predicted by the first principle method.
+In order to save the computing expense, the latest classical Mod potential\cite{Parks2007} implemented on the large scale parallel  molecular dynamics software package (LAMMPS) is chosen\cite{Kumagai2007Development}.
+This potential is able to reconstruct the elastic constant, melting point and phase transition of silicon materials.
+The potential parameters have been constructed for different type of silicene structures by fitting its bond angles to give accurate melting point and elastic constants, and for bulk Si with experimental equilibrium bond lengths which leads to smaller binding energy than that predicted by the first-principles calculations.
 
-The atomic models for multilayer silicene are shown in FIG.\ref{fig:structures}, which are adoped from recent work of Guo \emph{et al}\cite{Guo2015Structural}.
-For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" represents layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
-) and "s" indicates the type along the length direction which is a (armchair) or z (zigzag).
-We show in TABLE.\ref{tab:table1} the structure names and  the minimum repeat cell periodicities of the multilayer silicene.
+The atomic structures of multilayer silicene that were predicted to be stable by Guo \emph{et al}\cite{Guo2015Structural} are shown in Fig.\ref{fig:structures}.
+For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
+) and "s"="a" or "z", corresponds to the silicene adge along the length direction, i.
+e.,  "a" for armchair) and "z" for zigzag.
+We also show in TABLE.\ref{tab:table1} the structure names and  minimum repeat cell periodicities of these multilayer silicene.
 
@@
   \includegraphics[angle= 0, width=0.95\linewidth]{images/structures.eps}
-  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene.
-Within which  are top view and side view of the studied structures.
-The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface.
-All the atoms on the bottom surface are labeled as blue.
-The greens represent those that are inside the structure.
+  \caption{\label{fig:structures}  (color online)  Top view and side views of typical structures of multilayer silicene.
+The buckling Si atoms on the top layer are labeled as yellow balls, and the red balls represent the remaining Si atoms on the top layer.
+All the Si atoms on the bottom layer are labeled as the blue balls.
+The green balls represent Si atoms in the middle layers.
 The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.}
@@
 
-Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.
-Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated.
-The obtained forces are calculated and used to calculate the FCs with numerical differential calculation.
-The chosen supercells are $3 \times 3 \times 1$ of premitive cells to make the in-plane dimension above 40 \angstrom, which ensures  the accuracy of calculated forces.
-Following to previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
+Before the thermal conductivity calculation, silicene structures are fully optimized using the conjugate gradient method.
+Then the finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder (\textbf{Is it a software??)} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated.
+The obtained forces are calculated and used to calculate the FCs with the numerical differential calculation.
+The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces.
+Following the previous studies \textbf{[Is there references for this??]}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
 
 The thermal conductivity tensor can be calculated as
-
 \begin{equation}
@@
 \end{equation}
-
 where $c_{k \sigma}$ means the heat capacity of phonon mode,  $v_{k \sigma}^{\alpha}$ represents the mode group velocity, and $\tau_{k \sigma}$ is the phonon lifetime.
-The heat capacity is calculated with Eq.(\ref{eq:cv})
-
+The heat capacity is calculated as
 \begin{equation}
@@
 \end{equation}
+where $ f(\omega,T)=1/[exp(\frac{\hbar \omega}{k_b T})-1]$ is the Bose-Einstein distribution function.
 
-where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.
-
-The calculations of $c_{k\sigma}$ , $v_{k \sigma}^{\alpha}$, and $\tau_{k\sigma}$ require the second- and third-order force constants (FCs) as inputs, where the detailed formulas are referred to the work of  Li \cite{Li2014}.
-To avoid underestimation of thermal conductivity, iteration method is used instead of relaxation time approximation (RTA).
-A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is used to obtain enough phonons for the convergence on the summation, as well as for their further statistical analytics.
+The calculations of $c_{k\sigma}$ , $v_{k \sigma}^{\alpha}$, and $\tau_{k\sigma}$ require the second- and third-order FCs as inputs, where the detailed formulas are referred to the work of  Li \cite{Li2014}.
+To avoid underestimation of thermal conductivity, the iteration method is used instead of the relaxation time approximation (RTA).
+A $45\times 45 \times 1$ Monkhorst-Pack q-point mesh is adopted for the convergence on the summation.
 
@@
 
-We first show that the surface reconstruction has substantial influence on thermal conductivity of the multilayer silicene.
-FIG.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three bilayer silicene structures.
-As one can see, thermal conductivity converges with cutoff phonon mean free path (MFP) very quickly in of 2l2  structure, while a little slower in the others.
-Moreover, the cutoff MFPs of 2l1 structure are very different in the armchair and zigzag directions.
+We first show that the surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
+Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three bilayer silicene structures.
+It is seen that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2l2 structure, while it is a bit slowly in 2l1 and 2l3 structures.
+Also, the cutoff MFPs of 2l1 structure are distinct in the armchair and zigzag directions.
 These features can be attributed to the different scattering intensity caused by the surface reconstructions.
-It is known that the ballistic phonon transport is dominating  when a material length the is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when a material length is larger than the MFP.
-An empirical formula had been proposed by John A.
-Thomas\cite{Thomas2010}  to characterize the thermal conductivity of the phonon transport from ballistic to diffuse region, and accurately estimate thermal conductivity of the infinite long nanomaterials
-
+It is known that the ballistic phonon transport is dominating when a material length is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when the length is larger than the MFP.
+An empirical formula had been proposed by John A. Thomas\cite{Thomas2010}  to characterize the thermal conductivity from ballistic to diffuse phonon-transport region, which is
 \begin{equation}
@@
 \end{equation}
+where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation.
+Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by such formula.
+The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, respectively,  showing the significant influence of surface reconstruction on thermal conductivity.
 
-where $\kappa_\infty$ is the fitted full scattering thermal conductivity, $L_c$ is the transition length from the ballistic transportation to the diffuse transportation.
-Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by this  formula.
-The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK in zigzag (armchair) direction, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, confirming the significant influence of surface reconstruction on thermal conductivity.
-
-The surface reconstruction also induces the thermal conductivity anisotropy, which can be estimated using
+The surface reconstruction also induces thermal conductivity anisotropy, which can be evaluated using 
 \begin{equation}
-  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
+  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max‚Å°(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
 \end{equation}
-where $ \kappa_{z,\infty} (\kappa_{a,\infty})$ stands for the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
+with $ \kappa_{z,\infty} (\kappa_{a,\infty})$ being the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
 It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.
-The ultra low and perticularly high anisotropy of thermal conductivity of bilayer silicene indicate its great potential applications in the thermoelectrics.
+The ultra low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanooelectrics.
 
@@
   \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
-  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene.
-b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}).
-The letter z/a in the legend mean the transport direction is zigzag/armchair.
+  \caption{\label{fig:tc_length_sheng} (color online) a) The length dependence of thermal conductivity of three bilayer silicene structures.
+b) The thickness dependence of thermal conductivity of silicene with $2\times 1$ reconstruction.
+The dots are the results from BTE calculations, and the lines are the fitted results using Eq.(\ref{eq:eq_nemd}).
+The letter z/a in the legend means that the transport direction is zigzag/armchair.
 The dots of 2l2a and 2l2z are almost the same so red solid dots are covered.
@@
   \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
-  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
+  \caption{\label{fig:chi} (color online) The silicene length dependence of thermal conductivity anisotropy $\chi$.}
 \end{figure}
 
-We then discuss the thickness dependence of the thermal conductivity anisotropy.
-Here we mainly focus on the multilayer silicene with 3-8 atomic layers, whose surface presents the typical $2 \times 1$ Si(111) reconstruction.
-A common feature is that the thermal conductivity in the zigzag direction ($\kappa_z$) is obviously  higher than that  in armchair ($\kappa_a$) direction, which induces anisotropy larger than 55\%.
-The reason is that the zigzag direction of surface is composed of smooth zigzag atomic chains (as shown in FIG.\ref{fig:structures}), which are favorable for the heat transport.
-Whereas,  there are large geometry fluctuations in the armchair direction of the surface, which are unfavorable for the heat transport.
-With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on  thermal conductivity anisotropy.
-The negative  effect  is attributed to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing.
+We then discuss the thickness dependence of thermal conductivity anisotropy in multilayer silicene.
+Here we mainly focus on the structures of 3-8 Si layers in thickness, whose surface present the typical $2 \times 1$ Si(111) reconstruction.
+A common feature is that the thermal conductivity in the zigzag direction ($\kappa_z$) is obviously higher than that  in the armchair ($\kappa_a$) direction, which induces anisotropy larger than 55\%.
+The reason is that the surface in zigzag direction is composed of smooth zigzag atomic chains (as shown in Fig.\ref{fig:structures}), which are favorable for the heat transport.
+Whereas,  there are large geometry fluctuations in its the armchair direction, which are unfavorable for the heat transport.
+With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on the thermal conductivity anisotropy, which  is owing to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing.
 %This feature partially explains why the thermal conductivity  is almost isotropic in bulk Si, which usually has complex surface reconstructions. 
-One exception is for the trilayer silicene, which has the largest thermal conductivity  but the smallest  anisotropy, compared to the thicker  $2\times1$ structures.
-This could be understood by the direct interaction between the top and bottom layers, as well as the absence of ideal honeycomb ring under the surface layers, which is different from the thicker $2\times 1$ structures\cite{Guo2015Structural}.
+One exception is for the trilayer silicene, which has the largest thermal conductivity but the smallest  anisotropy compared to the thicker  $2\times1$ silicene structures.
+This could be understood by the direct interaction between the top and bottom layers, as well as the absence of ideal honeycomb ring under the surface layers  for the thermal transport, which is different from the thicker ones\cite{Guo2015Structural}.
 
-We also investigated the size effect on the thermal conductivity anisotropy.
-As shown in FIG.\ref{fig:chi}, thermal conductivity of  2l1 bilayer silicene is almost isotropic  with length being 10-1000 \angstrom, and it becomes increasingly anisotropic with the length increasing  above 1000  \angstrom.
+We have also investigated the size effect on the thermal conductivity anisotropy.
+As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2l1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom.
 This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.
-As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly attributed to the optical phonons.
+As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly induced by the optical phonons.
 On the other hand, the thermal conductivity anisotropy of 2l3 silicene can be owning to both acoustic and  optical phonons in different directions.
@@
   \caption{\label{tab:table1}
-    The thermal conductivity and anisotropic ratio of different multi-layer silicene.
-Along with the average heat capacity ($kJ/m^3/K$) of zigzag direction and armchair direction.
-$Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively.
-}
+ The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }
   \begin{ruledtabular}
@@
 
-To explore the origin of anisotropy, we have calculated the frequency distribution of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
+To explore the origin of thermal conductivity anisotropy, we have calculated the phonon frequency distributions of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
 It is found that the anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i.
-e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that of zigzag direction.
-Whereas, for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivity in armchair and zigzag directions is nearly the same in the low-frequency region, and the anisotropy is mainly  attributed to the high-frequency (5-20 THz) phonons.
-In addition, the anisotropy of the 3l1 structure is resulted by the  phonons with frequency in range of 10-20 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
+e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
+Whereas, as for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
+In addition, the anisotropy of the 3l1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
 
 To have a deep inside into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
-We selected all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in BZ, and calculated their heat capacity with Eq.(\ref{eq:cv}).
-The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in  zigzag and armchair directions, respectively.
-As one can see, $Cv_z$ and $Cv_a$  strongly depend on the reconstruction-structure and thicknes of multilayer silicene, but their difference in the same structure is very small.
-This result shows that the thermal conductivity anisotropy is insensitive to the heat capacity.
+We select all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in Brillouin zone, and calculated their heat capacity with Eq.(\ref{eq:cv}).
+The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in the zigzag and armchair directions, respectively.
+As one can see, although $Cv_z$ and $Cv_a$  strongly depend on the reconstructed structure and thickness of multilayer silicene, their difference in the same structure is very small.
+This feature shows that the thermal conductivity anisotropy is insensitive to the heat capacity.
 %This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.
@@
   \includegraphics[width=0.9\linewidth]{images/tc_freq.eps}
-  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
+  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity of multilayer silicene versus phonon frequency. }
 \end{figure}
@@
   \includegraphics[width=0.9\linewidth]{images/tau.eps}
-  \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
+  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process. }
 \end{figure}
 
-We then explore the contributions from the phonon lifetimes for the anisotropy.
-We considered the three-phonon scattering process, where the phonon scattering rate could be obtained by the Fermi-golden rule\cite{Li2014} considering only the relaxation time approximation (RTA).
-The the iterative method was then used to include the cross influence of the phonon excitation, witch usually gives lager but more accurate lifetimes than the RTA.
-The frequency dependence of phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.
+We then explore the contributions from the phonon lifetimes for the thermal conductivity anisotropy.
+We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA).
+The iterative method was then adopted to include the cross influence of the phonon excitation, since it usually gives lager but more accurate lifetimes than the RTA.
+The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.
 It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity.
-Moreover, the lifetime in armchair direction is obviously larger than that in zigzag direction in the low-frequency region.
-This feature inidcates that the anisotropy in bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
-On the other hand, the phonon lifetimes exhibit different frequency distributions in the thicker silicene, i.
-e.,  $2\times1$ structure with 3-6 Si layers, which cover both the low and high frequency regions with lifetimes  larger than 1 ps.
-This is explains the high frequency phonons contribute significantly to the thermal conductivity in these structures (Fig.
+Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region.
+This feature indicates that the thermal conductivity anisotropy of bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
+On the other hand, the phonon lifetimes exhibit a different frequency distribution for the thicker silicene, i.
+e.,  $2\times1$ structures with 3-6 Si layer in thickness, where the phonon lifetimes larger than 1 ps cover both the low and high frequency regions.
+This explains why the high frequency phonons contribute significantly to the thermal conductivity in the thicker silicene (Fig.
 \ref{fig:tc_freq}).
-Except for the 4l1 structure, the lifetime distributions in zigzag and armchair directions are very similar for these  $2\times1$ structures, showing the tiny effect of phonon lifetimes on the anisotropy.
+However, except for the 4l1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.
 
@@
   \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
-  \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
+  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz.}
 \end{figure}
 
-To further explore the origin of thermal conductivity anisotropy in multilayer  silicene, we have calculated the frequency dependence of phonon group velocities.
+To further explore the origin of thermal conductivity anisotropy in multilayer silicene, we have calculated the frequency dependence of phonon group velocities in armchair and zigzag directions.
 As shown in Fig.
-\ref{fig:gv},  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
-As for the $2\times 1$ silicene with thickness more than layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region.
-Combined with the fact that the lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the anisotropy of $2\times 1$ silicene structures.
-It should be noted that the anisotropy of 4l1 structure is from contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
+\ref{fig:gv},  the group-velocity difference in the two directions is very small in the low-frequency region for the bilayer silicene.
+This result confirms that the thermal conductivity anisotropy mainly comes from the different phonon scatterings in the armchair and zigzag directions,  which induce different phonon lifetimes.
+As for the $2\times 1$ silicene with thickness more than three Si layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region.
+Considering that the phonon-lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the thermal conductivity anisotropy of $2\times 1$ multilayer silicene.
+It should be noted that the anisotropy of 4l1 structure is from the contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
 
 \section{CONCLUSIONS}
-By means of Boltzmann Transporation Equation methods, we have investigated thermal conductivity of multilayer silicene with various surface structures and thickness.
-We found that the surface reconstruction has significant effect on thermal conductivity.
+By means of Boltzmann Transporation Equation methods, we have investigated the thermal conductivity of multilayer silicene with various surface structures and thicknesses.
+We have found that the surface reconstruction has significant effect on the thermal conductivity of multilayer silicene.
 The smooth surface is favorable for heat conduction, while the rough surface greatly suppresses the heat conduction.
 Both ultra low (3.3 W/mK) and relatively high (57.9 W/mK) thermal conductivities have been obtained on bilayer silicene with different surface structures, which also induce large anisotropy of 41\% and 27\%, respectively.
-We also found that the $2 \times 1$  surface reconstruction induces the unusual large thermal conductivity anisotropy of 70\%  in the quadlayer silicene.
-Moreover, we found that increasing silicene thickness, which has an effect of weakening the surface contribution to the thermal transport,  reduces the anisotropy.
-Finally, we clarify that the anisotropy of phonon lifetimes and phonon group velocities is the mainly contributes to   the thermal conductivity anisotropy for the bilayer and thicker $2\times 1$ silicene structures, respectively.
-Our results indicate that silicene structures with thickness of 2-4 layers present the most  exotic physical  properties, which may be a common feature for the 2D materials with strong interlayer interactions.
-This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials in the future.
+We have also found that the $2 \times 1$ surface reconstruction induces the unusual large thermal conductivity anisotropy of 70\%  in the four-layer silicene.
+Moreover, we have found that increasing silicene thickness, which has an effect of weakening the surface contribution to the thermal transport,  reduces the thermal conductivity anisotropy.
+Finally, we have clarified that the anisotropy from phonon lifetimes and phonon-group velocities contributes most to the thermal conductivity anisotropy to the bilayer and thicker $2\times 1$ silicene structures, respectively.
+Our results indicate that multilayer silicene with thickness of 2-4 layers present the most exotic physical properties, which may be a common feature for the 2D materials with strong interlayer interactions.
+This work is expected to helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials in the future.
 

### 2017-12-17 latex/paper.tex
modify 20171217

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-12-13 15:17:11
+% @Last Modified time: 2017-12-17 21:06:23
 
@@
   The silicon materials present complex surface reconstructions, which are usually neglected for thermal conductivity investigations due to their small specific surface area.
-However, the reconstruction effect can be significant when a material's thickness becomes ultra thin, i.
+However, the reconstruction effect can be significant when a material's thickness becomes ultra-thin, i.
 e., multilayer silicene.
@@
 
-Many theoretical and experimental results showed that the quantum confinement and surface effects can remarkably reduce the thermal conductivity of nanomaterials while remaining their electronic conductivity at high level, which make them great potential applications in the thermoelectrics[Adv.
-Mater.
-2007, 19, 1043–1053; Int.
-Mater.
-Rev.
-48, 45 (2003)].
-For example,  Boukai \emph{et al}.\cite{Boukai2008} found that by varying the nanowire size and impurity doping levels,  approximately 100-fold improvement of  ZT over bulk Si can be achieved in a broad temperature range.
+Many theoretical and experimental results showed that the quantum confinement and surface effects can remarkably reduce the thermal conductivity of nanomaterials while maintaining their electronic conductivity at high level, which make them great potential applications in the thermoelectric\cite{Dresselhaus2007,Chen2013}.
+For example,  Boukai \emph{et al}.\cite{Boukai2008} found that by altering the nanowire size and impurity doping levels,  approximately 100-fold improvement of  ZT over bulk Si can be achieved in a broad temperature range.
 Also, Hochbaum \emph{et al}.\cite{Hochbaum2008}  proposed a way of increasing ZT via controlling the roughness of silicene nanowires.
@@
 The existing researches on thermal conductivity of 2D materials mainly focus on the ones with weak van der Waals (vdW) interlayer interactions where no surface reconstruction appears.
-The multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015} are such kind of 2D materials which had been well studied.
+The multilayer graphene\cite{Lindsay2011, Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015} are such kind of 2D materials which had been well studied.
 Whereas, the thermal conductivity of 2D materials with strong interlayer interactions is barely explored so far.
 The multilayer silicene, which has been both theoretically predicted and experimentally synthesized, can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
-Previous studies showed that mutilayer silicene exhibits special surface reconstructions which induce the intriguing electronic property\cite{Fu2014,Guo2015Structural}.
+Previous studies showed that multilayer silicene exhibits special surface reconstructions which induce  intriguing electronic property\cite{Fu2014,Guo2015Structural}.
 Naturally, one also expects the surface reconstruction to play a key role in its thermal transport property.
@@
 In particular, alternative flexible substrate and active layer materials with increased thermal conductivity are  desirable  to prevent thermomechanical failures which have become a big challenge in flexible devices based on 2D materials\cite{Akinwande2014,Sadeghi2016}.
-Revealing the surface reconstruction effect on thermal conductivity anisotropy of mutilayer silicene could stimulate the studies of covalently bonded 2D materials for the potential applications in the nanoelectronics.
-
-In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various surface reconstructions and thicknesses  (2-8 atomic layers) in use of  the BTE method.
-We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce either ultra-low thermal conductivity ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).
-This feature shows that multilayer silicene can be ideal candidates in thermoelectrics and nanoelectronics.
+Revealing the surface reconstruction effect on thermal conductivity anisotropy of multilayer silicene could stimulate the studies of covalently bonded 2D materials for the potential applications in the nanoelectronics.
 
@@
 For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
-) and "s"="a" or "z", corresponds to the silicene adge along the length direction, i.
+) and "s"="a" or "z", corresponds to the silicene edge along the length direction, i.
 e.,  "a" for armchair) and "z" for zigzag.
@@
 Before the thermal conductivity calculation, silicene structures are fully optimized using the conjugate gradient method.
-Then the finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder (\textbf{Is it a software??)} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated.
+Then the finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder \cite{Li2014} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated.
 The obtained forces are calculated and used to calculate the FCs with the numerical differential calculation.
 The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces.
-Following the previous studies \textbf{[Is there references for this??]}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
+Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
 
@@
 \begin{equation}
-  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max‚Å°(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
+  \chi=\frac{|\kappa_{z,\infty}-\kappa_{a,\infty} |}{ max⁡(\kappa_{z,\infty}-\kappa_{a,\infty} ) } \times 100 \%  \label{eq:eq_chi}
 \end{equation}
@@
 It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.
-The ultra low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanooelectrics.
+The ultra-low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanoelectronics.
 
@@
 With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on the thermal conductivity anisotropy, which  is owing to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing.
-%This feature partially explains why the thermal conductivity  is almost isotropic in bulk Si, which usually has complex surface reconstructions. 
 One exception is for the trilayer silicene, which has the largest thermal conductivity but the smallest  anisotropy compared to the thicker  $2\times1$ silicene structures.
@@
   \caption{\label{tab:table1}
- The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }
+    The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively.
+}
   \begin{ruledtabular}
@@
 This feature shows that the thermal conductivity anisotropy is insensitive to the heat capacity.
-%This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high, which means when considering only acoustic phonons the heat capacity is close to constant.
 
 \begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{images/tc_freq.eps}
+  \includegraphics[width=1\linewidth]{images/tc_freq.eps}
   \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity of multilayer silicene versus phonon frequency. }
@@
 \begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{images/tau.eps}
+  \includegraphics[width=1\linewidth]{images/tau.eps}
   \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process. }
@@
 
+\begin{figure}[b]
+  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
+  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz.}
+\end{figure}
 We then explore the contributions from the phonon lifetimes for the thermal conductivity anisotropy.
@@
 
-\begin{figure}[b]
-  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
-  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz.}
-\end{figure}
-
 To further explore the origin of thermal conductivity anisotropy in multilayer silicene, we have calculated the frequency dependence of phonon group velocities in armchair and zigzag directions.
@@
 \section{CONCLUSIONS}
-By means of Boltzmann Transporation Equation methods, we have investigated the thermal conductivity of multilayer silicene with various surface structures and thicknesses.
+By means of Boltzmann Transportation Equation methods, we have investigated the thermal conductivity of multilayer silicene with various surface structures and thicknesses.
 We have found that the surface reconstruction has significant effect on the thermal conductivity of multilayer silicene.
 The smooth surface is favorable for heat conduction, while the rough surface greatly suppresses the heat conduction.
-Both ultra low (3.3 W/mK) and relatively high (57.9 W/mK) thermal conductivities have been obtained on bilayer silicene with different surface structures, which also induce large anisotropy of 41\% and 27\%, respectively.
+Both ultra-low (3.3 W/mK) and relatively high (57.9 W/mK) thermal conductivities have been obtained on bilayer silicene with different surface structures, which also induce large anisotropy of 41\% and 27\%, respectively.
 We have also found that the $2 \times 1$ surface reconstruction induces the unusual large thermal conductivity anisotropy of 70\%  in the four-layer silicene.

### 2017-12-17 src/gv.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-22 11:43:17
+# @Last Modified time: 2017-12-16 16:05:05
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
 import numpy as np
@@ -15,7 +15,7 @@ text_style = dict(
     fontdict={'family': 'serif'})
 vs = '2l1,2lh,3l1,4l1,5l1,6l1'.split(',')
 with fig('gv.eps'):
-    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 7))
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(8, 5))
     for i, v in enumerate(vs):
         print(v)
         ax = axes[i // 3, i % 3]
@@ -57,7 +57,7 @@ with fig('gv.eps'):
         ax.set_xlim([0.05, 19.9])
         ax.set_ylim([0.05, None])
 
-    fi.text(0.5, 0.04, 'Frequency (THz)', ha='center')
+    fi.text(0.5, 0.00, 'Phonon Frequency (THz)', ha='center')
     fi.text(
         0.07,
         0.5,

### 2017-12-17 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-22 11:40:24
+# @Last Modified time: 2017-12-16 16:04:01
 
 
 from aces.graph import fig, setLegend, pl
@@ -16,7 +16,7 @@ import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('tau.eps'):
-    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 6))
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(8, 5))
     for j in range(2):
         if j == 0:
             vs = "2l1,2lhex,3l1".split(',')
@@ -68,11 +68,11 @@ with fig('tau.eps'):
                     linewidth=1,
                     color='k',
                     ls='--')
-                ax.set_xlim([0.01, 20.55])
-                ax.set_ylim([1e-1, 2e2])
+                ax.set_xlim([0.01, 19.55])
+                ax.set_ylim([1.1e-1, 2e2])
                 setLegend(ax, fontsize=10)
-    fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
+    fi.text(0.5, 0.00, 'Phonon Frequency (THz)', ha='center')
     fi.text(
-        0.05, 0.5, 'Relaxation Time (ps)', va='center', rotation='vertical')
+        0.03, 0.5, 'Relaxation Time (ps)', va='center', rotation='vertical')
     fi.subplots_adjust(
         left=None, bottom=None, right=None, top=None, wspace=0, hspace=0)

### 2017-12-17 src/tc_freq.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-22 11:31:23
+# @Last Modified time: 2017-12-16 16:03:31
 
 
 from aces.graph import fig, setLegend, pl
@@ -16,7 +16,7 @@ import matplotlib
 matplotlib.rcParams['ytick.minor.width'] = 1.5
 matplotlib.rcParams['ytick.minor.size'] = 3
 with fig('tc_freq.eps'):
-    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(10, 6))
+    fi, axes = pl.subplots(2, 3, sharex=True, sharey=True, figsize=(8, 5))
     for j in range(2):
         if j == 0:
             vs = "2l1,2lhex,3l1".split(',')
@@ -58,16 +58,16 @@ with fig('tc_freq.eps'):
                         markerfacecolor=mfc,
                         color=colors[0])
 
-                ax.set_xlim([0.01, 20.55])
+                ax.set_xlim([0.03, 19.5])
                 ax.set_ylim([0.01, 1])
                 # ax.set_yticks([])
                 setLegend(ax, fontsize=10)
-    fi.text(0.5, 0.04, 'Phonon Frequency (THz)', ha='center')
+    fi.text(0.5, 0.00, 'Phonon Frequency (THz)', ha='center', fontsize=14)
     fi.text(
         0.05,
         0.5,
         'Thermal Conductivity (W/mK)',
         va='center',
-        rotation='vertical')
+        rotation='vertical', fontsize=14)
     fi.subplots_adjust(
         left=None, bottom=None, right=None, top=None, wspace=0, hspace=0)

### 2018-01-09 latex/paper.tex
按龚老师的意见修改

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2017-12-17 21:06:23
+% @Last Modified time: 2018-01-09 16:34:41
 
@@
 
-\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
+\title{Anisotropic in-plane thermal conductivity in multilayer silicene}
 \author{Yang Zhou${}^{1,3}$}
@@
 \begin{abstract}
-  The silicon materials present complex surface reconstructions, which are usually neglected for thermal conductivity investigations due to their small specific surface area.
-However, the reconstruction effect can be significant when a material's thickness becomes ultra-thin, i.
-e., multilayer silicene.
-Here we systematically study thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.
+  We systematically study thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.
 We find that their thermal conductivity strongly depends on the surface structures.
@@
 Also, Hochbaum \emph{et al}.\cite{Hochbaum2008}  proposed a way of increasing ZT via controlling the roughness of silicene nanowires.
-As far as we know,  thermal conductivity of silicon nanostructures, i.
-e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied, while it is still mysterious for multilayer silicene.
 The combined effects of quantum size and surface reconstruction in multilayer silicene are expected to induce exotic thermal transport properties different from either monolayer silicene or bulk Si, which may make it suitable for the thermoelectric applications.
@@
 The multilayer graphene\cite{Lindsay2011, Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015} are such kind of 2D materials which had been well studied.
-Whereas, the thermal conductivity of 2D materials with strong interlayer interactions is barely explored so far.
+Whereas, the thermal conductivity of 2D materials with strong interlayer interactions is poorly understood so far.
 The multilayer silicene, which has been both theoretically predicted and experimentally synthesized, can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
@@
 
-Before the thermal conductivity calculation, silicene structures are fully optimized using the conjugate gradient method.
-Then the finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder \cite{Li2014} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated.
+Silicene structures are fully optimized using the conjugate gradient method.
+The finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder \cite{Li2014} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated.
 The obtained forces are calculated and used to calculate the FCs with the numerical differential calculation.
@@
 \end{equation}
-where $c_{k \sigma}$ means the heat capacity of phonon mode,  $v_{k \sigma}^{\alpha}$ represents the mode group velocity, and $\tau_{k \sigma}$ is the phonon lifetime.
-The heat capacity is calculated as
+where $c_{k \sigma}$ is the heat capacity of phonon mode,  $v_{k \sigma}^{\alpha}$ is the mode group velocity, and $\tau_{k \sigma}$ is the phonon lifetime. The heat capacity is calculated by
 \begin{equation}
@@
 We first show that the surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
-Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three bilayer silicene structures.
-It is seen that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2l2 structure, while it is a bit slowly in 2l1 and 2l3 structures.
+Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three structures of bilayer silicene.
+One can see that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2l2 structure, while it is a bit slowly in 2l1 and 2l3 structures.
 Also, the cutoff MFPs of 2l1 structure are distinct in the armchair and zigzag directions.
 These features can be attributed to the different scattering intensity caused by the surface reconstructions.
-It is known that the ballistic phonon transport is dominating when a material length is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when the length is larger than the MFP.
-An empirical formula had been proposed by John A. Thomas\cite{Thomas2010}  to characterize the thermal conductivity from ballistic to diffuse phonon-transport region, which is
+It is known that the ballistic phonon transport is dominating when the length of the sample is smaller than the MFP,  whereas the diffuse phonon transport is  dominating when the length is larger than the MFP.
+An empirical formula had been proposed by Thomas\cite{Thomas2010}  to characterize the thermal conductivity from ballistic to diffuse phonon-transport region, which is
 \begin{equation}
@@
   \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
-  \caption{\label{fig:tc_length_sheng} (color online) a) The length dependence of thermal conductivity of three bilayer silicene structures.
+  \caption{\label{fig:tc_length_sheng} (color online) a) The size dependence of thermal conductivity of three bilayer silicene structures.
 b) The thickness dependence of thermal conductivity of silicene with $2\times 1$ reconstruction.
@@
 
-We then discuss the thickness dependence of thermal conductivity anisotropy in multilayer silicene.
-Here we mainly focus on the structures of 3-8 Si layers in thickness, whose surface present the typical $2 \times 1$ Si(111) reconstruction.
+Here we discuss the thickness dependence of thermal conductivity anisotropy in multilayer silicene.
+We mainly focus on the structures of 3-8 Si layers in thickness, whose surface present the typical $2 \times 1$ Si(111) reconstruction.
 A common feature is that the thermal conductivity in the zigzag direction ($\kappa_z$) is obviously higher than that  in the armchair ($\kappa_a$) direction, which induces anisotropy larger than 55\%.
 The reason is that the surface in zigzag direction is composed of smooth zigzag atomic chains (as shown in Fig.\ref{fig:structures}), which are favorable for the heat transport.
-Whereas,  there are large geometry fluctuations in its the armchair direction, which are unfavorable for the heat transport.
+Whereas,  there are large geometry fluctuations in the armchair direction, which are unfavorable for the heat transport.
 With the silicene thickness increasing from 4 to 8 atomic layers, the anisotropy monotonically decreases from 70\% to 58\%, showing the negative  effect of thickness on the thermal conductivity anisotropy, which  is owing to the decrease of $\kappa_z$ and increase of $\kappa_a$  with the  thickness increasing.
@@
 
-To have a deep inside into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
+To have a deep insight into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
 We select all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in Brillouin zone, and calculated their heat capacity with Eq.(\ref{eq:cv}).

### 2018-01-09 src/chi.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-12-07 14:42:03
+# @Last Modified time: 2018-01-09 16:54:40
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -50,13 +50,13 @@ with fig('chi.eps', figsize=(7, 8)):
             v = '2l3'
         label = v
         ax1.semilogx(l, ka, label=label, **opts)
-        ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")
+        ax1.set_xlabel("Cutoff Mean Free Path for Phonons (${ \\AA }$)")
         # ax1.set_ylim([0, 15])
         ax1.set_xlim([10, 1e5])
-        ax1.set_ylim([0, .8 * 100])
+        ax1.set_ylim([0, 100])
         ax1.set_ylabel("Thermal Conductivity Anisotropy (%)")
         # ax1.text(-.15, 1, 'b)', transform=ax1.transAxes, **text_style)
-    setLegend(ax1, ncol=2, loc=0, fontsize=8)
+    setLegend(ax1, ncol=4, loc=0, fontsize=12)
     fi.subplots_adjust(
         left=None,
         bottom=None,

### 2018-01-09 src/gv.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-12-16 16:05:05
+# @Last Modified time: 2018-01-09 17:04:18
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
 import numpy as np
@@ -52,7 +52,7 @@ with fig('gv.eps'):
         x, y = binmeanx(np.c_[freqs, gvs[:, 1]], [0, 20], df)
         ax.plot(x, y, color="r", ls="--", lw=3, label=v1 + "a")
         # ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
-        setLegend(ax, ncol=1, fontsize=10)
+        setLegend(ax, ncol=1, fontsize=12)
         # ax.set_yticks([])
         ax.set_xlim([0.05, 19.9])
         ax.set_ylim([0.05, None])

### 2018-01-09 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-12-16 16:04:01
+# @Last Modified time: 2018-01-09 17:04:00
 
 
 from aces.graph import fig, setLegend, pl
@@ -70,7 +70,7 @@ with fig('tau.eps'):
                     ls='--')
                 ax.set_xlim([0.01, 19.55])
                 ax.set_ylim([1.1e-1, 2e2])
-                setLegend(ax, fontsize=10)
+                setLegend(ax, fontsize=12)
     fi.text(0.5, 0.00, 'Phonon Frequency (THz)', ha='center')
     fi.text(
         0.03, 0.5, 'Relaxation Time (ps)', va='center', rotation='vertical')

### 2018-01-09 src/tc_freq.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-12-16 16:03:31
+# @Last Modified time: 2018-01-09 17:02:43
 
 
 from aces.graph import fig, setLegend, pl
@@ -61,7 +61,7 @@ with fig('tc_freq.eps'):
                 ax.set_xlim([0.03, 19.5])
                 ax.set_ylim([0.01, 1])
                 # ax.set_yticks([])
-                setLegend(ax, fontsize=10)
+                setLegend(ax, fontsize=12)
     fi.text(0.5, 0.00, 'Phonon Frequency (THz)', ha='center', fontsize=14)
     fi.text(
         0.05,

### 2018-01-09 src/tc_length_sheng.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-22 11:25:20
+# @Last Modified time: 2018-01-09 17:01:27
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -82,7 +82,7 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
         print(v + "z=" + str(kas[0][i]) + " " + v +
               "a=" + str(kas[1][i]) + " kai=" + str(kai) + "%")
     kas = []
-    setLegend(ax1, ncol=2, loc=0, fontsize=8)
+    setLegend(ax1, ncol=1, loc=0, fontsize=12)
     ax1 = axes[1]
     vs = '3l1,4l1,5l1,6l1,8l1'.split(',')
     for s in ['z', 'a']:
@@ -127,12 +127,13 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
             p = fit(l, ka, [1, 1, 1], ff)
             xx = np.linspace(10, 1e4, 1000)
             ax1.semilogx(xx, ff(p, xx), color=c, ls=o1)
-            ax1.set_xlabel("Cutoff Mean Free Path for Phonons (Angstrom)")
+            ax1.set_xlabel(
+                "Cutoff Mean Free Path for Phonons (${ \\AA }$)")
             ax1.set_ylim([-2, 39])
             ax1.set_xlim([0.5, 1e5])
             ax1.set_ylabel("Thermal Conductivity(W/mK)")
             ax1.text(-.15, 1, 'b)', transform=ax1.transAxes, **text_style)
-    setLegend(ax1, ncol=2, loc=0, fontsize=8)
+    setLegend(ax1, ncol=1, loc=0, fontsize=12)
     kas = np.array(kas).reshape([2, -1])
     for i, v in enumerate(vs):
         kai = np.abs(kas[0][ i] - kas[1][i ]) / \

### 2018-01-10 latex/paper.tex
按龚老师要求修改caption

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2018-01-09 16:34:41
+% @Last Modified time: 2018-01-10 23:52:08
 
@@
 Whereas, the thermal conductivity of 2D materials with strong interlayer interactions is poorly understood so far.
-The multilayer silicene, which has been both theoretically predicted and experimentally synthesized, can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
+The multilayer silicene, which has been both theoretically predicted and experimentally synthesized, can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.The silicon materials present complex surface reconstructions, which are usually neglected for thermal conductivity investigations due to their small specific surface area.
+However, the reconstruction effect can be significant when a material's thickness becomes ultra thin, i.
+e., multilayer silicene.
 Previous studies showed that multilayer silicene exhibits special surface reconstructions which induce  intriguing electronic property\cite{Fu2014,Guo2015Structural}.
@@
 The green balls represent Si atoms in the middle layers.
-The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.}
+The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.
+The structures exihibit obvious and pretty different surface reconsruction.}
 \end{figure}
@@
 The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces.
-Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.
+Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness d because the thickness of two dimensional silicene is hard to restrictly determined, since it's a common constant for all the structures, the conclusion is independent on the absolute value of d, so a experimental value makes sence here.
 
@@
   \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
-  \caption{\label{fig:tc_length_sheng} (color online) a) The size dependence of thermal conductivity of three bilayer silicene structures.
-b) The thickness dependence of thermal conductivity of silicene with $2\times 1$ reconstruction.
+  \caption{\label{fig:tc_length_sheng} (color online) The depencence of cummulative thermal conductivity(TC) on cutoff phonon mean free path for all the structures.
+a) The cummulative TC of bilayer silicene structures.
+b) The cummulative TC of multilayer silicene with $2\times 1$ reconstruction and different layer.
 The dots are the results from BTE calculations, and the lines are the fitted results using Eq.(\ref{eq:eq_nemd}).
@@
 The dots of 2l2a and 2l2z are almost the same so red solid dots are covered.
+With the increase of cutoff mean free path TC converges.
+For bilayer structures TC along armchair direction is larger while for the others TC along zigzag direction is larger.
+With the increase of thickness TC along zigzag decreases while that along armchair increases a little.
 }
@@
   \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
-  \caption{\label{fig:chi} (color online) The silicene length dependence of thermal conductivity anisotropy $\chi$.}
+  \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$.
+$\chi$ of 2l2 structure is exactly zero and is a horizonal line at 0.
+For 2l1, 2l3  structures the anisotropy increase with the cutoff MPF while that of 3l1 decreases.
+The others show indepencece of cutoff MPF.
+For bilayer silicence the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length.
+}
 \end{figure}
@@
   \includegraphics[width=1\linewidth]{images/tc_freq.eps}
-  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity of multilayer silicene versus phonon frequency. }
+  \caption{\label{fig:tc_freq} (color online)  The phonon frequency dependence of converged thermal conductivity of multilayer silicene.
+For bilayer structures TC mainly comes from low frequency phonons while the others have more contribution from high frequency phonons and they have similar curve.
+TC of bilayer structure have larger TC along armchair direction at low frequency and the anisotropy deceases with frequency.
+For the other structures, TC shows little difference along the two direction at low frequency but TC along zigzag direction is higher at high frequency.
+}
 \end{figure}
@@
   \includegraphics[width=1\linewidth]{images/tau.eps}
-  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process. }
+  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.
+The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency.
+Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4l1 structure).
+The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.
+}
 \end{figure}
@@
   \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
-  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz.}
+  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene.
+The histogram bin width is chosen as 1.5 THz.
+The bilayer structures have isotropic group velocities at low frequency region and the contribution from high frequency could be ignored considering the valishment of lifetime at this region.
+The structure of 3-6 layers exhibit anisotropic group velocity which suggests localization of phonons.}
 \end{figure}

### 2018-01-10 latex/paper.tex
为每个段落提取主旨句

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2018-01-10 23:52:08
+% @Last Modified time: 2018-01-11 00:20:31
 
@@
 
-We first show that the surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
+The surface reconstruction has substantial influence on thermal conductivity of multilayer silicene.
 Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three structures of bilayer silicene.
@@
 
-The surface reconstruction also induces thermal conductivity anisotropy, which can be evaluated using
+The surface reconstruction also induces thermal conductivity anisotropy. The anisotropy can be presented by
 \begin{equation}
@@
 
-Here we discuss the thickness dependence of thermal conductivity anisotropy in multilayer silicene.
+The anisotropy of TC decreases with thickness.
 We mainly focus on the structures of 3-8 Si layers in thickness, whose surface present the typical $2 \times 1$ Si(111) reconstruction.
@@
 
-We have also investigated the size effect on the thermal conductivity anisotropy.
+The anisotropy shows size effect in bilayer structure while no size effect of it is found in multilayer structures.
 As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2l1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom.
@@
 
+The magnitude and anisotropy of TC is mainly contributed from low frequency phonons in bilayers structures while that in multilayer structures comes from high frequency phonons.
 To explore the origin of thermal conductivity anisotropy, we have calculated the phonon frequency distributions of thermal conductivity in armchair and zigzag directions  (Fig.\ref{fig:tc_freq}).
@@
 e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
-Whereas, as for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
+Whereas,  for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
 In addition, the anisotropy of the 3l1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
 
+The heat capacity has contribution to mugnitude difference in the structures but is not responsible for the anisotropy.
 To have a deep insight into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
@@
 \end{figure}
-We then explore the contributions from the phonon lifetimes for the thermal conductivity anisotropy.
+
+Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less denpendence on frequency.
 We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA).
@@
 
-To further explore the origin of thermal conductivity anisotropy in multilayer silicene, we have calculated the frequency dependence of phonon group velocities in armchair and zigzag directions.
+Group velocity at low frequency shows no anisotropy in bilayer structures while that of zigzag direction is larger than that of armchair direction in 3-6 layer structures.
 As shown in Fig.

### 2018-01-11 latex/paper.tex
将2l1改为2L1

@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2018-01-11 00:20:31
+% @Last Modified time: 2018-01-11 15:12:52
 
@@
 Fig.\ref{fig:tc_length_sheng}(a) presents the length dependence of thermal conductivity of three structures of bilayer silicene.
-One can see that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2l2 structure, while it is a bit slowly in 2l1 and 2l3 structures.
-Also, the cutoff MFPs of 2l1 structure are distinct in the armchair and zigzag directions.
+One can see that the thermal conductivity converges quickly with cutoff phonon mean free path (MFP) in of 2L2 structure, while it is a bit slowly in 2L1 and 2L3 structures.
+Also, the cutoff MFPs of 2L1 structure are distinct in the armchair and zigzag directions.
 These features can be attributed to the different scattering intensity caused by the surface reconstructions.
@@
 Here we find that the length dependence of thermal conductivity of multilayer silicene can also be well described by such formula.
-The saturated thermal conductivity of 2l1 structure reaches up to 42.1 (57.9) W/mK, while it is  31.1 (31.1) W/mK  for 2l2 structure and  3.3 (5.6)  W/mK for 2l3 structure in zigzag (armchair) direction, respectively,  showing the significant influence of surface reconstruction on thermal conductivity.
+The saturated thermal conductivity of 2L1 structure reaches up to 42.1 (57.9) W/mK, while it is  31.1 (31.1) W/mK  for 2L2 structure and  3.3 (5.6)  W/mK for 2L3 structure in zigzag (armchair) direction, respectively,  showing the significant influence of surface reconstruction on thermal conductivity.
 
@@
 with $ \kappa_{z,\infty} (\kappa_{a,\infty})$ being the full scattering thermal conductivity (infinite thermal conductivity) in the zigzag (armchair) direction.
-It is found that both 2l2 and 2l3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2l2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.
+It is found that both 2L2 and 2L3 structures show large thermal conductivity anisotropy, i.e., 27\% and 41\%, respectively, while 2L2 structure does not exhibits the anisotropy owning to its rotational symmetry over $\pi/2$.
 The ultra-low and particularly high thermal conductivity anisotropy of bilayer silicene indicate its potential applications in the nanoelectronics.
@@
 The letter z/a in the legend means that the transport direction is zigzag/armchair.
-The dots of 2l2a and 2l2z are almost the same so red solid dots are covered.
+The dots of 2L2a and 2L2z are almost the same so red solid dots are covered.
 With the increase of cutoff mean free path TC converges.
@@
   \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$.
-$\chi$ of 2l2 structure is exactly zero and is a horizonal line at 0.
-For 2l1, 2l3  structures the anisotropy increase with the cutoff MPF while that of 3l1 decreases.
+$\chi$ of 2L2 structure is exactly zero and is a horizonal line at 0.
+For 2L1, 2L3  structures the anisotropy increase with the cutoff MPF while that of 3L1 decreases.
 The others show indepencece of cutoff MPF.
@@
 The anisotropy shows size effect in bilayer structure while no size effect of it is found in multilayer structures.
-As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2l1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom.
+As shown in Fig.\ref{fig:chi}, the thermal conductivity of  2L1 bilayer silicene is almost isotropic with length of 10-1000 \angstrom, and it becomes increasingly anisotropic for length  above 1000  \angstrom.
 This is essentially due to the difference of acoustic phonons in different directions,  which have large MFP.
 As for the $2\times1$ structures with 3-8 Si layers in thickness, the high thermal conductivity anisotropy is obtained even when the length is as short as 10 \angstrom, implying that the anisotropy is  mainly induced by the optical phonons.
-On the other hand, the thermal conductivity anisotropy of 2l3 silicene can be owning to both acoustic and  optical phonons in different directions.
+On the other hand, the thermal conductivity anisotropy of 2L3 silicene can be owning to both acoustic and  optical phonons in different directions.
 
@@
       \hline
-      2l1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
-      2l2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
-      2l3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
-      3l1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
-      4l1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
-      5l1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
-      6l1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
-      8l1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
+      2L1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
+      2L2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
+      2L3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
+      3L1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
+      4L1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
+      5L1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
+      6L1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
+      8L1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
     \end{tabular}
@@
 It is found that the anisotropy is mainly attributed to the low-frequency (0-5 THz) phonons for the bilayer silicene, i.
-e., 2l1 and 2l3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
+e., 2L1 and 2L3, where thermal conductivity in armchair direction is obviously larger than that in zigzag direction.
 Whereas,  for the $2\times1$ structures thicker than 3 Si layers, the thermal conductivities in armchair and zigzag directions are nearly the same in the low-frequency region, and the anisotropy is mainly attributed to the high-frequency (5-20 THz) phonons.
-In addition, the anisotropy of the 3l1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
+In addition, the anisotropy of the 3L1 structure is resulted by the phonons with frequency above 10 THz, below which the summation of contributions to thermal conductivity are nearly the same in armchair and zigzag directions.
 
@@
 The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency.
-Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4l1 structure).
+Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4L1 structure).
 The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.
@@
 The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.
-It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity.
+It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2L1, 2L3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity.
 Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region.
@@
 \ref{fig:tc_freq}).
-However, except for the 4l1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.
+However, except for the 4L1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.
 
@@
 As for the $2\times 1$ silicene with thickness more than three Si layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region.
-Considering that the phonon-lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the thermal conductivity anisotropy of $2\times 1$ multilayer silicene.
-It should be noted that the anisotropy of 4l1 structure is from the contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
+Considering that the phonon-lifetime difference contributes little to the anisotropy for 3L1, 5L1, and 6L1 structures, one can conclude that the group velocity difference is the main reason for the thermal conductivity anisotropy of $2\times 1$ multilayer silicene.
+It should be noted that the anisotropy of 4L1 structure is from the contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.
 

### 2018-01-11 src/chi.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2018-01-09 16:54:40
+# @Last Modified time: 2018-01-11 15:18:39
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -49,7 +49,7 @@ with fig('chi.eps', figsize=(7, 8)):
         if v == '2lhex':
             v = '2l3'
         label = v
-        ax1.semilogx(l, ka, label=label, **opts)
+        ax1.semilogx(l, ka, label=label.replace('l', 'L'), **opts)
         ax1.set_xlabel("Cutoff Mean Free Path for Phonons (${ \\AA }$)")
         # ax1.set_ylim([0, 15])
         ax1.set_xlim([10, 1e5])

### 2018-01-11 src/gv.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 14:39:58
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2018-01-09 17:04:18
+# @Last Modified time: 2018-01-11 15:21:38
 import aces.tools as tl
 from aces.graph import fig, setLegend, pl
 import numpy as np
@@ -50,7 +50,17 @@ with fig('gv.eps'):
         x, y = binmeanx(np.c_[freqs, gvs[:, 0]], [0, 20], df)
         ax.plot(x, y, color="k", lw=3, label=v1 + "z")
         x, y = binmeanx(np.c_[freqs, gvs[:, 1]], [0, 20], df)
-        ax.plot(x, y, color="r", ls="--", lw=3, label=v1 + "a")
+        ax.plot(
+            x,
+            y,
+            color="r",
+            ls="--",
+            lw=3,
+            label=(
+                v1 +
+                "a").replace(
+                'l',
+                'L'))
         # ax.text(.02,.8,"("+v+")",transform=ax.transAxes,**text_style)
         setLegend(ax, ncol=1, fontsize=12)
         # ax.set_yticks([])

### 2018-01-11 src/tau.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2018-01-09 17:04:00
+# @Last Modified time: 2018-01-11 15:21:11
 
 
 from aces.graph import fig, setLegend, pl
@@ -60,7 +60,8 @@ with fig('tau.eps'):
                     markeredgecolor=colors[i],
                     markerfacecolor=mfc,
                     color=colors[i],
-                    label=v1 + s)
+                    label=(v1 + s).replace('l', 'L')
+                )
                 ax.axhline(
                     y=1,
                     xmin=0,

### 2018-01-11 src/tc_freq.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-16 18:34:55
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2018-01-09 17:02:43
+# @Last Modified time: 2018-01-11 15:20:32
 
 
 from aces.graph import fig, setLegend, pl
@@ -41,7 +41,7 @@ with fig('tc_freq.eps'):
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 1] - kappa[p, 1]) / df,
-                        label=v1 + s, ls=ls,
+                        label=(v1 + s).replace('l', 'L'), ls=ls,
                         marker=markers[0],
                         markersize=9,
                         markeredgecolor=colors[0],
@@ -51,7 +51,7 @@ with fig('tc_freq.eps'):
                     ax.plot(
                         kappa[p, 0],
                         (kappa[p + 2, 5] - kappa[p, 5]) / df,
-                        label=v1 + s, ls=ls,
+                        label=(v1 + s).replace('l', 'L'), ls=ls,
                         marker=markers[0],
                         markersize=9,
                         markeredgecolor=colors[0],

### 2018-01-11 src/tc_length_sheng.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-14 22:16:16
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2018-01-09 17:01:27
+# @Last Modified time: 2018-01-11 15:16:45
 from aces.tools import *
 from aces.graph import fig, setLegend, pl, fit
 import numpy as np
@@ -66,7 +66,7 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
                 v = '2l3'
             label = v + s
             kas.append(ka[-1])
-            ax1.semilogx(l, ka, label=label, **opts)
+            ax1.semilogx(l, ka, label=label.replace('l', 'L'), **opts)
             p = fit(l, ka, [1, 1, 1], ff)
             xx = np.linspace(10, 1e4, 1000)
             ax1.semilogx(xx, ff(p, xx), color=c, ls=o1)
@@ -123,7 +123,7 @@ with fig('tc_length_sheng.eps', figsize=(7, 8)):
                 ka = a
             label = v + s
             kas.append(ka[-1])
-            ax1.semilogx(l, ka, label=label, **opts)
+            ax1.semilogx(l, ka, label=label.replace('l', 'L'), **opts)
             p = fit(l, ka, [1, 1, 1], ff)
             xx = np.linspace(10, 1e4, 1000)
             ax1.semilogx(xx, ff(p, xx), color=c, ls=o1)

### 2018-01-15 submit/paper.tex
submit to CMS

--- 2018-01-11 latex/paper.tex
@@
 % @Last Modified by:   YangZhou
-% @Last Modified time: 2018-01-11 15:12:52
+% @Last Modified time: 2018-01-15 17:09:48
 
-\documentclass[aps,prb,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}
-
-\preprint{APS/123-QED}
+\documentclass[review]{elsarticle}
 
@@
 \usepackage{amssymb}
-
+\bibliographystyle{elsarticle-num}
 \newcommand{\angstrom}{\mbox{\normalfont\AA}}
@@
 \title{Anisotropic in-plane thermal conductivity in multilayer silicene}
-\author{Yang Zhou${}^{1,3}$}
-\author{Zhi-Xin Guo${}^{2,1}$}
-\email{zxguo08@hotmail.com}
-\author{Shi-You Chen${}^{1}$}
-\author{Hong-Jun Xiang${}^{1}$}
-\author{Xin-Gao Gong${}^{1,3}$}
-\email{xggong@fudan.edu.cn}
-\affiliation{
-  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
-  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
-  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
-}
+\author[1,3]{Yang Zhou}
+\author[2,1]{Zhi-Xin Guo\corref{correspondingauthor1}}
+\author[1]{Shi-You Chen}
+\author[1]{Hong-Jun Xiang}
+\author[1,3]{Xin-Gao Gong\corref{correspondingauthor2}}
+\cortext[correspondingauthor1]{zxguo08@hotmail.com}
+\cortext[correspondingauthor2]{xggong@fudan.edu.cn}
+
+\address[1]{Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China}
+\address[2]{Department of Physics, Xiangtan University, Xiangtan 411105, China}
+\address[3]{Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China}
 \begin{abstract}
@@
 The atomic structures of multilayer silicene that were predicted to be stable by Guo \emph{et al}\cite{Guo2015Structural} are shown in Fig.\ref{fig:structures}.
-For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
+For convenience, we define the names of these structures as "nLxs", where "n" is a pure number, representing the number of layers, "L" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc.
 ) and "s"="a" or "z", corresponds to the silicene edge along the length direction, i.
@@
 The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.
-The structures exihibit obvious and pretty different surface reconsruction.}
+The structures exhibit obvious and pretty different surface reconsruction.}
 \end{figure}
@@
 The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces.
-Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness d because the thickness of two dimensional silicene is hard to restrictly determined, since it's a common constant for all the structures, the conclusion is independent on the absolute value of d, so a experimental value makes sence here.
+Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness d because the thickness of two dimensional silicene is hard to strictly  determined, since it's a common constant for all the structures, the conclusion is independent on the absolute value of d, so a experimental value makes sense here.
 
@@
 For 2L1, 2L3  structures the anisotropy increase with the cutoff MPF while that of 3L1 decreases.
-The others show indepencece of cutoff MPF.
-For bilayer silicence the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length.
+The others show independence of cutoff MPF.
+For bilayer silicene the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length.
 }
@@
 }
-  \begin{ruledtabular}
+
   \begin{tabular}{ccccccc}
@@
   \end{tabular}
-  \end{ruledtabular}
 \end{table*}
@@
 
-The heat capacity has contribution to mugnitude difference in the structures but is not responsible for the anisotropy.
+The heat capacity has contribution to magnitude difference in the structures but is not responsible for the anisotropy.
 To have a deep insight into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
@@
   \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.
-The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency.
-Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4L1 structure).
+The horizonal dash line at 1.0ps is a guidance for the main contribution region of phonon frequency.
+Phonon lifetime doesnt's show obvious anisotropy in both bilayer structure and multilayer structures (except for the abnmornal region of 5-7 THz in 4L1 structure).
 The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.
@@
 The histogram bin width is chosen as 1.5 THz.
-The bilayer structures have isotropic group velocities at low frequency region and the contribution from high frequency could be ignored considering the valishment of lifetime at this region.
+The bilayer structures have isotropic group velocities at low frequency region and the contribution from high frequency could be ignored considering the vanishment of lifetime at this region.
 The structure of 3-6 layers exhibit anisotropic group velocity which suggests localization of phonons.}
@@
 
-Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less denpendence on frequency.
+Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less dependence on frequency.
 We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA).

### 2018-01-15 latex/run.py

@@ -2,7 +2,7 @@
 # @Author: YangZhou
 # @Date:   2017-06-21 01:41:49
 # @Last Modified by:   YangZhou
-# @Last Modified time: 2017-11-06 17:11:43
+# @Last Modified time: 2018-01-15 17:09:52
 import os
 if not os.path.exists("bin/"):
     os.mkdir("bin")
